---
title: "Data_ind_imp_RUVIII_WPCNA"
author: "Omar Johnson"
date: "2023-12-19"
output: html_document
---
# Load Libraries 
```{r Libraries, include=FALSE}

library(EDASeq)
library(RUVSeq)
library(RColorBrewer)
library(edgeR)
library(limma)
library(Biobase)
library(SummarizedExperiment)
library(tidyverse) 
library(ggfortify)
library(cluster)
library(edgeR)
library(limma)
library(Homo.sapiens)
library(BiocParallel)
library(qvalue)
library(pheatmap)
library(clusterProfiler)
library(AnnotationDbi)
library(org.Hs.eg.db)
library(RColorBrewer)
library(variancePartition)
library(DOSE)
library(UpSetR)
library(ggvenn)
library(biomaRt)
library(ggridges)
library(reshape2)
library(BioNERO)
library(WGCNA)
library(impute)
library(dynamicTreeCut)
```


# Read in Data 
```{r Read in data}

# 1. RUVg Corrected data across all 10 samples that has been log2 transformed. It has not yet been quantile normalized. 
 RUVg_Log2_quantnormalized_all10samples <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/DIA_proteins/RUVIII_Imputed/RUVIII_10samples_log2_notquantilenormalized.csv", header = TRUE, row.names = 1)

# Undo log tranformation
RUVg_Log2_quantnormalized_all10samples <- RUVg_Log2_quantnormalized_all10samples^2

 

# 2. Toptable correspondding to the Diff.Abundance test from #1 
toptable_summary <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/DIA_proteins/RUVIII_Imputed/Toptable_summary_RUVIII.csv", header = TRUE, row.names = 1)
toptable_summary %>% head()


# 3. Meta data for all 10 samples in our study. 
Meta <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/DIA_proteins/RUVIII_Imputed/Meta.csv", header = TRUE, row.names = 1)
Meta
```


# WPCNA- shallow cuts initial objects
```{r Create summarized experiment object}

# Create summarized experiment object 
WGCNA_DF <- SummarizedExperiment(assays = as.matrix(RUVg_Log2_quantnormalized_all10samples))
WGCNA_DF
dim(RUVg_Log2_quantnormalized_all10samples) 
exp_filt <- filter_by_variance(WGCNA_DF, n = 4182)
exp_filt %>% assay() %>% head()
Meta
```


# SFT power threshold  
```{r SFT power threshold  }
# Determine the soft power threshold to get scale free shape
sft <- SFT_fit(exp_filt, net_type = "signed", rsquared = 0.8,  cor_method = "pearson")
sft$plot  
```


# Modify workflow to have a simpler network  
```{r  Modify workflow to have a simpler network}
exp2gcn2_EDIT <- function (exp, net_type = "signed", module_merging_threshold = 0.8, 
          SFTpower = NULL, cor_method = "spearman", verbose = FALSE) 
{
  params <- list(net_type = net_type, module_merging_threshold = module_merging_threshold, 
                 SFTpower = SFTpower, cor_method = cor_method)
  norm.exp <- BioNERO:::handleSE(exp)
  if (is.null(SFTpower)) {
    stop("Please, specify the SFT power.")
  }
  if (verbose) {
    message("Calculating adjacency matrix...")
  }
  cor_matrix <- BioNERO:::calculate_cor_adj(cor_method, norm.exp, SFTpower, 
                                  net_type)$cor
  adj_matrix <- BioNERO:::calculate_cor_adj(cor_method, norm.exp, SFTpower, 
                                  net_type)$adj
  gene_ids <- rownames(adj_matrix)
  adj_matrix <- matrix(adj_matrix, nrow = nrow(adj_matrix))
  rownames(adj_matrix) <- gene_ids
  colnames(adj_matrix) <- gene_ids
  if (verbose) {
    message("Calculating topological overlap matrix (TOM)...")
  }
  tomtype <- BioNERO:::get_TOMtype(net_type)
  TOM <- WGCNA::TOMsimilarity(adj_matrix, TOMType = tomtype)
  dissTOM <- 1 - TOM
  geneTree <- hclust(as.dist(dissTOM), method = "average")
  if (verbose) {
    message("Detecting coexpression modules...")
  }
  old.module_labels <- dynamicTreeCut::cutreeDynamicTree(dendro = geneTree, maxTreeHeight = 3 , 
                                                         minModuleSize = 35, deepSplit = FALSE)
  nmod <- length(unique(old.module_labels))
  palette <- rev(WGCNA::standardColors(nmod))
  old.module_colors <- WGCNA::labels2colors(old.module_labels, 
                                            colorSeq = palette)
  if (verbose) {
    message("Calculating module eigengenes (MEs)...")
  }
  old.MElist <- WGCNA::moduleEigengenes(t(norm.exp), colors = old.module_colors, 
                                        softPower = SFTpower)
  old.MEs <- old.MElist$eigengenes
  MEDiss1 <- 1 - cor(old.MEs)
  old.METree <- hclust(as.dist(MEDiss1), method = "average")
  MEDissThreshold <- 1 - module_merging_threshold
  if (verbose) {
    message("Merging similar modules...")
  }
  if (cor_method == "pearson") {
    merge1 <- WGCNA::mergeCloseModules(t(norm.exp), old.module_colors, 
                                       cutHeight = MEDissThreshold, verbose = 0, colorSeq = palette)
  }
  else if (cor_method == "spearman") {
    merge1 <- WGCNA::mergeCloseModules(t(norm.exp), old.module_colors, 
                                       cutHeight = MEDissThreshold, verbose = 0, corOptions = list(use = "p", 
                                                                                                   method = "spearman"), colorSeq = palette)
  }
  else if (cor_method == "biweight") {
    merge1 <- WGCNA::mergeCloseModules(t(norm.exp), old.module_colors, 
                                       cutHeight = MEDissThreshold, verbose = 0, corFnc = bicor, 
                                       colorSeq = palette)
  }
  else {
    stop("Please, specify a correlation method. One of 'spearman', 'pearson' or 'biweight'.")
  }
  new.module_colors <- merge1$colors
  new.MEs <- merge1$newMEs
  new.METree <- hclust(as.dist(1 - cor(new.MEs)), method = "average")
  genes_and_modules <- as.data.frame(cbind(gene_ids, new.module_colors))
  colnames(genes_and_modules) <- c("Genes", "Modules")
  if (verbose) {
    message("Calculating intramodular connectivity...")
  }
  kwithin <- WGCNA::intramodularConnectivity(adj_matrix, new.module_colors)
  result.list <- list(adjacency_matrix = adj_matrix, MEs = new.MEs, 
                      genes_and_modules = genes_and_modules, kIN = kwithin, 
                      correlation_matrix = cor_matrix, params = params, dendro_plot_objects = list(tree = geneTree, 
                                                                                                   unmerged = old.module_colors))
  return(result.list)
}
```


# Generate network with max merge threshold 
```{r Generate network with max merge threshold }
net <- exp2gcn2_EDIT(
  exp_filt, net_type = "signed", module_merging_threshold = 0.99, SFTpower = 20, 
  cor_method = "pearson")


# Dendogram
plot_dendro_and_colors(net )



# Eigengene networks
WGCNA::plotEigengeneNetworks(net$MEs, "", marDendro = c(3, 5, 2, 6), plotHeatmaps = FALSE)

WGCNA::plotEigengeneNetworks(net$MEs, "", marHeatmap = c(3, 4, 2, 2), plotDendrograms = FALSE)

plot_eigengene_network(net)

# Genes per module 
plot_ngenes_per_module(net)
```


# Generate network with desired merge threshold 
```{r Generate network with desired merge threshold}

net <- exp2gcn2_EDIT(
  exp_filt, net_type = "signed", module_merging_threshold = 0.8, SFTpower = 20, 
  cor_method = "pearson")



# Dendogram
plot_dendro_and_colors(net )


# Eigengene networks
WGCNA::plotEigengeneNetworks(net$MEs, "", marDendro = c(3, 5, 2, 6), plotHeatmaps = FALSE)


WGCNA::plotEigengeneNetworks(net$MEs, "", marHeatmap = c(3, 4, 2, 2), plotDendrograms = FALSE)


plot_eigengene_network(net)


# Genes per module 
plot_ngenes_per_module(net)
```


# Define trait and get eigen proteins!!!!! 
```{r Define trat and get eigen proteins }

Meta

WGCNA_DF$trait <- c(1,1,1,1,1,0,0,0,0,0)
names(WGCNA_DF$trait) <- c("S1", "S3", "S5", "S7", "S9", "S2", "S4", "S6", "S8", "S10")


eigenmatrix <- net$MEs %>% as.matrix()
eigenmatrix
```


# Trait-module correlation test 
```{r Trait-module correlation test,  fig.width = 5, fig.height = 8}
correlationResults <- cor(eigenmatrix, WGCNA_DF$trait, method="pearson")

pvalues <- sapply(1:ncol(eigenmatrix), function(column) cor.test(eigenmatrix[,column], WGCNA_DF$trait)$p.value )

WGCNA_DF$trait <- as.matrix(WGCNA_DF$trait)

Modeigen <- as.matrix(net$MEs)


# Trait data frame
trait_data <- data.frame(
  ME = correlationResults %>% rownames(),
  Value = correlationResults[,1],
  PValue = pvalues
)
trait_data$neglogP <- -log(trait_data$PValue)
trait_data




# Plot correlation across modules
ggplot(trait_data, aes(x = ME, y = neglogP, color = Value)) + 
  geom_segment(aes(xend = ME, yend = 0), linetype = "solid") +
  geom_point(size = 10) + 
  scale_color_gradient(
    low = "red", 
    high = "blue", 
    name = "corr",
    limits = c(-1, 1),
    breaks = seq(-1, 1, by = 0.5)
  ) +
  labs(x = "Module", y = "-log(P-value)", title = "Module correlation with DOX treatment") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  geom_hline(yintercept = 2.995732, color = "black", linetype = "dashed") +
  geom_text(aes(x = 0, y = 3.5, label = "P-Val Threshold"), hjust = -0.1, vjust = 1.5)
```


# General wrangling 
```{r General wrangling }
# Get modules that significantly associate with DOX treatment 
Signifigant_modules <-  trait_data[trait_data$PValue < 0.05, ]$ME


# Get your genes/proteins and modules DF 
Gene_mod_DF <- net$genes_and_modules 



# Module data gets merged with toptable
toptable_summary %>% head()


Toptable_Modules <- merge(toptable_summary, 
                          Gene_mod_DF, by.x = "Protein", by.y = "Genes")





# Get the corresponding Gene name IDs
mart <- useMart("ensembl", dataset = "hsapiens_gene_ensembl")


results_Pro_names <- getBM(filters = "uniprotswissprot", 
                           attributes = c("uniprotswissprot", "hgnc_symbol"), 
                           values = toptable_summary$Protein, 
                           mart = mart)


merged_results_Pro_names_AND_Toptable_for_ENZYME <- merge(toptable_summary, results_Pro_names, by.x = "Protein", by.y = "uniprotswissprot")
ENZYME_DF_Toptable <- merged_results_Pro_names_AND_Toptable_for_ENZYME

DE_Enzymes <- ENZYME_DF_Toptable[(ENZYME_DF_Toptable$P.Value < 0.05) & (!is.na(ENZYME_DF_Toptable$ENZYME)), ]$hgnc_symbol

All_Proteins_ENZYMES <- ENZYME_DF_Toptable[(!is.na(ENZYME_DF_Toptable$ENZYME)), ]$hgnc_symbol



# Plotting LogFC in significant modules module 
Significant_modules_NoME <- stringr::str_replace(Signifigant_modules, "^ME", "")

Toptable_Modules_Sig <- Toptable_Modules[Toptable_Modules$Modules %in% Significant_modules_NoME, ]



# n-modules total 
Toptable_Modules$Modules %>% unique() %>% length()

# n-sig modules
Signifigant_modules %>% length()


# Percent sig modules 
(Signifigant_modules %>% length()) / (Toptable_Modules$Modules %>% unique() %>% length())



# Get modules that significantly associate with DOX treatment 
Signifigant_modules <-  trait_data[trait_data$PValue < 0.05, ]$ME


# Get your genes/proteins and modules DF 
Gene_mod_DF <- net$genes_and_modules 


# Subset genes/proteins and modules DF by the significantly correlated modules to DOX 
Sig_Gene_mod_DF <- Gene_mod_DF[Gene_mod_DF$Modules %in% Signifigant_modules, ]


# Module data gets merged with toptable
Toptable_Modules <- merge(toptable_summary, 
                          Gene_mod_DF, by.x = "Protein", by.y = "Genes")

Toptable_Modules %>% head()
Toptable_Modules %>% dim()
```


# Combining diff abundant test with modules 
```{r Ridge}

# LogFC Ridge plot 
ggplot(Toptable_Modules_Sig, aes(x = logFC, y = Modules, fill = Modules)) +
  ggridges::geom_density_ridges(alpha = 0.8) +
  labs(title = "Dox Associated Module LogFC distribution from DE test",
       x = "Log Fold Change",
       y = "Modules") +
  ggridges::theme_ridges() 


# LogFC Ridge plot 
ggplot(Toptable_Modules, aes(x = logFC, y = Modules, fill = Modules)) +
  ggridges::geom_density_ridges(alpha = 0.8) +
  labs(title = "Dox Associated Module LogFC distribution from DE test",
       x = "Log Fold Change",
       y = "Modules") +
  ggridges::theme_ridges() 



# Pval Ridge plot 
ggplot(Toptable_Modules_Sig, aes(x = P.Value, y = Modules, fill = Modules)) +
  ggridges::geom_density_ridges(alpha = 0.8) +
  labs(title = "Module pval distribution from DE test",
       x = "Pval",
       y = "") +
  ggridges::theme_ridges()+
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), limits = c(0, 1))


# Pval Ridge plot 
ggplot(Toptable_Modules, aes(x = P.Value, y = Modules, fill = Modules)) +
  ggridges::geom_density_ridges(alpha = 0.6) +
  labs(title = "Module pval distribution from DE test",
       x = "Pval",
       y = "Modules") +
  ggridges::theme_ridges()+
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), limits = c(0, 1))

```


# DE across modules 
```{r DE across modules}
# Plotting LogFC between DE and non DE proteins 
Toptable_Modules$DE_or_Not <- Toptable_Modules$P.Value < 0.05


# Calculate percentage of DE genes for each module
DE_Mod_result <- Toptable_Modules %>%
  group_by(Modules) %>%
  summarize(
    total_genes = n(),
    DE_genes = sum(P.Value < 0.05),
    percent_DE = (DE_genes / total_genes) * 100
  )

print(DE_Mod_result)


# Plot
ggplot(DE_Mod_result, aes(x = Modules, y = percent_DE)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Module",
    y = "Percentage of DE genes",
    title = "Percentage of DE genes in each module",
    fill = "Module"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


# Compute complementary percentage for non-DE genes
DE_Mod_result$percent_nonDE <- 100 - DE_Mod_result$percent_DE

# Reshape data to long format
long_data <- DE_Mod_result %>% 
  pivot_longer(cols = c(percent_DE, percent_nonDE), 
               names_to = "type", 
               values_to = "percentage")



# Plot stacked bar chart
ggplot(long_data, aes(x = Modules, y = percentage, fill = type)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Module",
    y = "Percentage",
    title = "Percentage of DE and non-DE genes in each module",
    fill = "Type"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = rev(seq(0, 100, by = 10)))

Significant_modules_NoME
```


# GO enrichment acrross dox correlated modules 
```{r GO enrichment, fig.width = 10, fig.height = 15}
hubs <- get_hubs_gcn(WGCNA_DF, net)
ontology_categories <- c("ALL")


# Loop over each module and ontology category
for (module in Significant_modules_NoME) {
  # Extract hub genes for the current module
  module_hubs <- hubs[hubs$Module == module, ]$Gene
  
  # All module proteins
  module_proteins <- Toptable_Modules[(Toptable_Modules$Modules == module), ]$Protein
  
  # Get gene names for the proteins in the module
  module_genes <- ENZYME_DF_Toptable[ENZYME_DF_Toptable$Protein %in% module_proteins, ]$hgnc_symbol
  
  # Define background genes
  background_genes_mod <- ENZYME_DF_Toptable$hgnc_symbol
  
  for (ont in ontology_categories) {
    # GO Enrichment
    go_enrichment <- enrichGO(gene = module_genes,
                              OrgDb = org.Hs.eg.db,
                              keyType = "SYMBOL",
                              universe = background_genes_mod,
                              ont = ont,
                              pvalueCutoff = 1,
                              qvalueCutoff = 1)
    
    # Plotting the results
    # Plotting the results
    p <- barplot(go_enrichment, showCategory = 20) +
      ggtitle(paste("Module:", module, "- Ontology:", ont))
    
    print(p)   
    
  }
}
Significant_modules_NoME
```


# Protein corrrelation plots within modules 
```{r Protein corrrelation plots, fig.width=15, fig.height=15}
# Total number of networks edges 
get_edge_list(net) %>% dim()
Significant_modules_NoME
```


# Network darkturquoise 
```{r Network darkturquoise, fig.width = 10, fig.height = 15}
edges_filtered <- get_edge_list(
  net, module = c("darkturquoise" ), 
  filter = TRUE, method = "min_cor", rcutoff = 0.97,
  check_SFT = TRUE
)

dim(edges_filtered)

plot_gcn(
  edgelist_gcn = edges_filtered, 
  net = net, 
  color_by = "module", 
  hubs = hubs,
  top_n_hubs = 30,
  show_labels = "tophubs"
)
```


# Network midnightblue  
```{r Network midnightblue, fig.width = 10, fig.height = 15}
edges_filtered <- get_edge_list(
  net, module = c( "midnightblue"), 
  filter = TRUE, method = "min_cor", rcutoff = 0.95,
  check_SFT = TRUE
)

dim(edges_filtered)

plot_gcn(
  edgelist_gcn = edges_filtered, 
  net = net, 
  color_by = "module", 
  hubs = hubs,
  top_n_hubs = 30,
  show_labels = "tophubs"
)
```


# Network cyan  
```{r Network cyan, fig.width = 10, fig.height = 15}
edges_filtered <- get_edge_list(
  net, module = c("cyan" ), 
  filter = TRUE, method = "min_cor", rcutoff = 0.98,
  check_SFT = TRUE
)

dim(edges_filtered)

plot_gcn(
  edgelist_gcn = edges_filtered, 
  net = net, 
  color_by = "module", 
  hubs = hubs,
  top_n_hubs = 30,
  show_labels = "tophubs"
)
```


# Network tan  
```{r Network tan, fig.width = 10, fig.height = 15}
edges_filtered <- get_edge_list(
  net, module = c("tan"), 
  filter = TRUE, method = "min_cor", rcutoff = 0.99,
  check_SFT = TRUE
)

dim(edges_filtered)

plot_gcn(
  edgelist_gcn = edges_filtered, 
  net = net, 
  color_by = "module", 
  hubs = hubs,
  top_n_hubs = 30,
  show_labels = "tophubs"
)
```


# Network yellow  
```{r Network yellow, fig.width = 10, fig.height = 15}
edges_filtered <- get_edge_list(
  net, module = c("yellow"), 
  filter = TRUE, method = "min_cor", rcutoff = 0.97,
  check_SFT = TRUE
)

dim(edges_filtered)

plot_gcn(
  edgelist_gcn = edges_filtered, 
  net = net, 
  color_by = "module", 
  hubs = hubs,
  top_n_hubs = 30,
  show_labels = "tophubs"
)
```


# Trait correlation Individual
```{r trait corr ind.}
Drug_trait_results <- trait_data

Meta

WGCNA_DF$trait <- c(1,2,3,3,3,1,2,3,3,3)
names(WGCNA_DF$trait) <- c("S1", "S3", "S5", "S7", "S9", "S2", "S4", "S6", "S8", "S10")


eigenmatrix <- net$MEs %>% as.matrix()
eigenmatrix


correlationResults <- cor(eigenmatrix, WGCNA_DF$trait, method="pearson")

pvalues <- sapply(1:ncol(eigenmatrix), function(column) cor.test(eigenmatrix[,column], WGCNA_DF$trait)$p.value )

WGCNA_DF$trait <- as.matrix(WGCNA_DF$trait)

Modeigen <- as.matrix(net$MEs)


# Trait data frame
trait_data <- data.frame(
  ME = correlationResults %>% rownames(),
  Value = correlationResults[,1],
  PValue = pvalues
)
trait_data$neglogP <- -log(trait_data$PValue)
trait_data



# Plot correlation across modules
ggplot(trait_data, aes(x = ME, y = neglogP, color = Value)) + 
  geom_segment(aes(xend = ME, yend = 0), linetype = "solid") +
  geom_point(size = 10) + 
  scale_color_gradient(
    low = "red", 
    high = "blue", 
    name = "corr",
    limits = c(-1, 1),
    breaks = seq(-1, 1, by = 0.5)
  ) +
  labs(x = "Module", y = "-log(P-value)", title = "Module correlation with DOX treatment") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  geom_hline(yintercept = 2.995732, color = "black", linetype = "dashed") +
  geom_text(aes(x = 0, y = 3.5, label = "P-Val Threshold"), hjust = -0.1, vjust = 1.5)
      
        

# Get modules that significantly associate with DOX treatment 
Signifigant_modules <-  trait_data[trait_data$PValue < 0.05, ]$ME


# Get your genes/proteins and modules DF 
Gene_mod_DF <- net$genes_and_modules 




# Module data gets merged with toptable
toptable_summary %>% head()


Toptable_Modules <- merge(toptable_summary, 
                          Gene_mod_DF, by.x = "Protein", by.y = "Genes")




merged_results_Pro_names_AND_Toptable_for_ENZYME <- merge(toptable_summary, results_Pro_names, by.x = "Protein", by.y = "uniprotswissprot")
ENZYME_DF_Toptable <- merged_results_Pro_names_AND_Toptable_for_ENZYME

DE_Enzymes <- ENZYME_DF_Toptable[(ENZYME_DF_Toptable$P.Value < 0.05) & (!is.na(ENZYME_DF_Toptable$ENZYME)), ]$hgnc_symbol

All_Proteins_ENZYMES <- ENZYME_DF_Toptable[(!is.na(ENZYME_DF_Toptable$ENZYME)), ]$hgnc_symbol



# Plotting LogFC in significant modules module 
Significant_modules_NoME <- stringr::str_replace(Signifigant_modules, "^ME", "")

Toptable_Modules_Sig <- Toptable_Modules[Toptable_Modules$Modules %in% Significant_modules_NoME, ]



# n-modules total 
Toptable_Modules$Modules %>% unique() %>% length()

# n-sig modules
Signifigant_modules %>% length()


# Percent sig modules 
(Signifigant_modules %>% length()) / (Toptable_Modules$Modules %>% unique() %>% length())



# Get modules that significantly associate with DOX treatment 
Signifigant_modules <-  trait_data[trait_data$PValue < 0.05, ]$ME


# Get your genes/proteins and modules DF 
Gene_mod_DF <- net$genes_and_modules 


# Subset genes/proteins and modules DF by the significantly correlated modules to DOX 
Sig_Gene_mod_DF <- Gene_mod_DF[Gene_mod_DF$Modules %in% Signifigant_modules, ]


# Module data gets merged with toptable
Toptable_Modules <- merge(toptable_summary, 
                          Gene_mod_DF, by.x = "Protein", by.y = "Genes")

Toptable_Modules %>% head()
Toptable_Modules %>% dim()




# Loop over each module and ontology category
for (module in Significant_modules_NoME) {
  # Extract hub genes for the current module
  module_hubs <- hubs[hubs$Module == module, ]$Gene
  
  # All module proteins
  module_proteins <- Toptable_Modules[(Toptable_Modules$Modules == module), ]$Protein
  
  # Get gene names for the proteins in the module
  module_genes <- ENZYME_DF_Toptable[ENZYME_DF_Toptable$Protein %in% module_proteins, ]$hgnc_symbol
  
  # Define background genes
  background_genes_mod <- ENZYME_DF_Toptable$hgnc_symbol
  
  for (ont in ontology_categories) {
    # GO Enrichment
    go_enrichment <- enrichGO(gene = module_genes,
                              OrgDb = org.Hs.eg.db,
                              keyType = "SYMBOL",
                              universe = background_genes_mod,
                              ont = ont,
                              pvalueCutoff = 1,
                              qvalueCutoff = 1)
    
    # Plotting the results
    # Plotting the results
    p <- barplot(go_enrichment, showCategory = 10) +
      ggtitle(paste("Module:", module, "- Ontology:", ont))
    
    print(p)   
    
  }
}




Drug_trait_results_sub <- Drug_trait_results[,c(1,2,3)]
colnames(Drug_trait_results_sub) <- c("Module", "cor", "pval")
Drug_trait_results_sub$Trait <- "DOX"
Drug_trait_results_sub


trait_data
Ind_trait_sub <- trait_data[,c(1,2,3)]
colnames(Ind_trait_sub) <- c("Module","cor", "pval")
Ind_trait_sub$Trait <- "IND."

Fulltrait_df <- rbind(Drug_trait_results_sub,Ind_trait_sub)
Fulltrait_df



Fulltrait_df$annotation <- ifelse(Fulltrait_df$pval < 0.05, "*", "")



ggplot(Fulltrait_df, aes(x = Trait, y = Module, fill = cor)) +
  geom_tile() +
  geom_text(aes(label = annotation), color = "black", size = 10) +
  scale_fill_gradient2(
    low = "blue", 
    high = "red", 
    mid = "white", 
    midpoint = 0, 
    name = "Correlation",
    limits = c(-1, 1)  # Set the limits for the color scale
  ) +
  labs(x = "Trait", y = "Module") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```