---
title: "Data_ind_Diffabtrial"
output: html_document
date: "2023-12-13"
---

# Load Libraries 
```{r Libraries, include=FALSE}
library(EDASeq)
library(RUVSeq)
library(RColorBrewer)
library(edgeR)
library(limma)
library(Biobase)
library(SummarizedExperiment)
library(tidyverse) 
library(ggfortify)
library(cluster)
library(edgeR)
library(limma)
library(Homo.sapiens)
library(BiocParallel)
library(qvalue)
library(pheatmap)
library(corrplot)
library(gplots)
library(clusterProfiler)
library(AnnotationDbi)
library(org.Hs.eg.db)
library(RColorBrewer)
library(variancePartition)
library(DOSE)
library(UpSetR)
library(ggvenn)
library(biomaRt)
library(ggridges)
library(reshape2)
library(BioNERO)
library(WGCNA)
library(impute)
library(DESeq2)
library(ruv)
```


# Added funtions 
```{r Added functions}
# 1
remove_rows_with_nas <- function(data_frame) {
  data_frame[rowSums(is.na(data_frame)) < 5, ]
}

# 2
remove_rows_with_nas_var <- function(data_frame, NA_remove) {
  data_frame[rowSums(is.na(data_frame)) < NA_remove, ]
}

# 3
plot_nrow_vs_naremove <- function(data_frame) {
  results <- data.frame(NA_remove = integer(), Rows_Remaining = integer())

  for (i in 1:ncol(data_frame)) {
    filtered_df <- remove_rows_with_nas_var(data_frame, NA_remove = i)
    results <- rbind(results, data.frame(NA_remove = i, Rows_Remaining = nrow(filtered_df)))
  }

  ggplot(results, aes(x = NA_remove, y = Rows_Remaining)) +
    geom_point() +
    geom_line() +
    xlab("Na tolerance threshold") +
    ylab("Number of proteins remaining") +
    theme_minimal()
}
```

# Read in Data 
```{r Read in Data 1}

# Load your data
Protein_DF <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/RNA_Protein_DF/Data_ind_prot_DOX_24hr.csv", header = TRUE)

# Include metadata about samples 
Meta <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/Meta_DIA.csv", header = TRUE)
```

# Wrangle Data Frame 
```{r Wrangle Data Frame 1}
# Save the original 
Full_DF <- Protein_DF 
Full_DF %>% head()
Full_DF %>% dim()

# Subset the columns referring to abundance
Protein_DF_Abundance <- Full_DF[,colnames(Full_DF) %in% c("Protein.Ids", "S1" , "S3" , "S5" , "S7", "S9", "S2", "S4", "S6" , "S8", "S10")] 
Protein_DF_Abundance %>% head()
Protein_DF_Abundance %>% dim()
colnames(Protein_DF_Abundance) <- c("Accession", "S1" , "S3" , "S5" , "S7", "S9", "S2", "S4", "S6" , "S8", "S10")
Protein_DF_Abundance %>% head()
Protein_DF_Abundance %>% dim()

# Check for duplicated rows 
# Identify duplicated values
Protein_DF_Abundance$duplicated_name <- duplicated(Protein_DF_Abundance$Accession)

# This will return a logical vector where TRUE indicates the position of duplicates in the column.
# To see only rows with duplicated values, you can subset the dataframe like this:
duplicated_rows <- Protein_DF_Abundance[Protein_DF_Abundance$duplicated_name == TRUE, ]
print(duplicated_rows) # We have 0 rows with duplicate protein names 

# Make rownames of the data frame accession IDs
rownames(Protein_DF_Abundance) <- Protein_DF_Abundance$Accession

# Change colnames 
colnames(Protein_DF_Abundance)
Protein_DF_Abundance <- Protein_DF_Abundance[, -c(1, 12)]

# Remove non-human peptides 
Protein_DF_Abundance %>% head()
Protein_DF_Abundance %>% dim()


Protein_DF_Abundance <- Protein_DF_Abundance[!rownames(Protein_DF_Abundance) %in% c("Q6ZSR9", "P15252","P25691","P00761"), ]
Protein_DF_Abundance %>% head()
Protein_DF_Abundance %>% dim()

# Assuming column names of Protein_DF match with the rows in Meta
Meta
rownames(Meta) <- Meta$Samples
Meta
colnames(Protein_DF_Abundance) <- Meta$Samples
Protein_DF_Abundance %>% head()
Meta
```

# Remove NA
```{r Wrangle Data Frame 234}
#1.  Find rows with any NA values
rows_with_na <- apply(Protein_DF_Abundance, 1, function(x) any(is.na(x))) %>% which()
 

rows_with_na <- as.numeric(rows_with_na)


# 2. Remove rows with NA values 
Protein_DF_Abundance <- Protein_DF_Abundance[-rows_with_na, ]

# 3. Sanity check 
Protein_DF_Abundance %>% dim()
```

# Log2 transform 
```{r Wrangle Data Frame 90}
log2_norm_counts <- log2(Protein_DF_Abundance)
log2_norm_counts %>% rowMeans() %>% hist(breaks = 100)
```

# Quantile Normalization 
```{r Wrangle Data Frame 55}
normalizedData <- limma::normalizeBetweenArrays(log2_norm_counts[, c(1,2,4,6,7,9)], method = "quantile")
normalizedData %>% rowMeans() %>% hist(breaks = 100)
```

# Linear model - NA proteins  
```{r upcor on 6 samples 2}
#  counts need to be integer values and in a numeric matrix 
counts <- as.matrix(normalizedData) 
counts %>% dim()

# Create a DataFrame for the phenoData
phenoData <- DataFrame(Meta)
phenoData_sub <- phenoData[c(1,2,4,6,7,9), ]


# Create Design Matrix 
# phenoData$Cond <- factor(phenoData$Cond , levels = c("Control", "Dox"))
design <- model.matrix(~ 0 + Cond , phenoData_sub)
design

# rename columns 
colnames(design) <- c('Control', "Dox")


# Fit model
dupcor <- duplicateCorrelation(counts , design, block = phenoData_sub$Ind)
fit <- lmFit(object = counts, design = design, block = phenoData_sub$Ind, correlation = dupcor$consensus)
fit2 <- eBayes(fit)


# Make contrasts
cm <- makeContrasts(
  DoxvNorm = Dox - Control,
  levels = design)


# Model with contrasts
fit2 <- contrasts.fit(fit, cm)
fit2 <- eBayes(fit2 )


# Summarize
results_summary <- decideTests(fit2, adjust.method = "none", p.value = 0.05)
summary(results_summary)






# Toptable summary organized to contain results for all tested proteins   
toptable_summary <- topTable(fit2, coef = "DoxvNorm",number = (nrow(normalizedData)), p.value = 1, adjust.method = "none")
toptable_summary$Protein <- rownames(toptable_summary)
toptable_summary$P.Value %>% hist(breaks = 100)



# PCA of log2-quantile normalized-RUVs values:
prcomp_res <- prcomp(t(normalizedData %>% as.matrix()), center = TRUE)

ggplot2::autoplot(prcomp_res, data = as.data.frame(phenoData_sub), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()


# Volcano plots 
# 1. Create a column to threshold P-values 
toptable_summary <- toptable_summary %>%  mutate(threshold_P = P.Value < 0.05)

# 2. Plot 
ggplot(toptable_summary)+
  geom_point(mapping = aes(x = logFC, y = -log10(P.Value), color = threshold_P))+
  xlab("log2FC")+
  ylab("-log10 nominal p-value")+
  ylim(0, 7.5)+
  xlim(-5, 5)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()


# Other fits 
fit3 <- eBayes(fit2, robust = TRUE, trend = TRUE)


# Summarize
results_summary <- decideTests(fit3, adjust.method = "none", p.value = 0.05)
summary(results_summary)


# Toptable summary organized to contain results for all tested proteins   
toptable_summary <- topTable(fit3, coef = "DoxvNorm",number = (nrow(normalizedData)), p.value = 1, adjust.method = "none")
toptable_summary$Protein <- rownames(toptable_summary)
toptable_summary$P.Value %>% hist(breaks = 100)


# PCA of log2-quantile normalized-RUVs values:
prcomp_res <- prcomp(t(normalizedData %>% as.matrix()), center = TRUE)


ggplot2::autoplot(prcomp_res, data = as.data.frame(phenoData_sub), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()


# Volcano plots 
# 1. Create a column to threshold P-values 
toptable_summary <- toptable_summary %>%  mutate(threshold_P = P.Value < 0.05)


# 2. Plot 
ggplot(toptable_summary)+
  geom_point(mapping = aes(x = logFC, y = -log10(P.Value), color = threshold_P))+
  xlab("log2FC")+
  ylab("-log10 nominal p-value")+
  ylim(0, 7.5)+
  xlim(-5, 5)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()
```


# Wrangle Data Frame for imputed data
```{r Wrangle Data Frame impute}
# Save the original
Full_DF <- Protein_DF
Full_DF %>% head()
Full_DF %>% dim()

# # Subset the columns referring to abundance
Protein_DF_Abundance <- Full_DF[,colnames(Full_DF) %in% c("Protein.Ids", "S1" , "S3" , "S5" , "S7", "S9", "S2", "S4", "S6" , "S8", "S10")]
Protein_DF_Abundance %>% head()
Protein_DF_Abundance %>% dim()
colnames(Protein_DF_Abundance) <- c("Accession", "S1" , "S3" , "S5" , "S7", "S9", "S2", "S4", "S6" , "S8", "S10")
Protein_DF_Abundance %>% head()
Protein_DF_Abundance %>% dim()

# # Check for duplicated rows 
# # Identify duplicated values
Protein_DF_Abundance$duplicated_name <- duplicated(Protein_DF_Abundance$Accession)

# # This will return a logical vector where TRUE indicates the position of duplicates in the column.
# # To see only rows with duplicated values, you can subset the dataframe like this:
duplicated_rows <- Protein_DF_Abundance[Protein_DF_Abundance$duplicated_name == TRUE, ]
print(duplicated_rows) # We have 0 rows with duplicate protein names

# # Make rownames of the data frame accession IDs
rownames(Protein_DF_Abundance) <- Protein_DF_Abundance$Accession

# # Change colnames 
colnames(Protein_DF_Abundance)
Protein_DF_Abundance <- Protein_DF_Abundance[, -c(1, 12)]
Protein_DF_Abundance %>% head()
Protein_DF_Abundance %>% dim()


# Remove non-human peptides 
Protein_DF_Abundance %>% head()
Protein_DF_Abundance %>% dim()


Protein_DF_Abundance <- Protein_DF_Abundance[!rownames(Protein_DF_Abundance) %in% c("Q6ZSR9", "P15252","P25691","P00761"), ]
Protein_DF_Abundance %>% head()
Protein_DF_Abundance %>% dim()




# # Assuming column names of Protein_DF match with the rows in Meta
Meta
rownames(Meta) <- Meta$Samples
Meta
colnames(Protein_DF_Abundance) <- Meta$Samples
Protein_DF_Abundance %>% head()
Meta
```

# Viewing how NA threshold vs remaining proteins  
```{r viewing NA and imp}

# View how NA thresholds affect the amount of proteins remaining to model
# All proteins 
Protein_DF_Abundance %>% nrow()

# Removing proteins with 1 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 1 ) %>% nrow()

# Removing proteins with 2 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 2 ) %>% nrow()

# Removing proteins with 3 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 3 ) %>% nrow()

# Removing proteins with 4 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 4 ) %>% nrow()

# Removing proteins with 5 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 5 ) %>% nrow()

# Removing proteins with 6 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 6 ) %>% nrow()

# Removing proteins with 7 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 7 ) %>% nrow()

# Removing proteins with 8 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 8 ) %>% nrow()

# View in graph 
plot_nrow_vs_naremove(Protein_DF_Abundance)
```

# NA removal and imputing with knn
```{r knn impute NA}
# View original abundances 
Protein_DF_Abundance %>% head()
Protein_DF_Abundance[,1] %>% hist(breaks = 100)
Protein_DF_Abundance[,2] %>% hist(breaks = 100)
Protein_DF_Abundance[,3] %>% hist(breaks = 100)
Protein_DF_Abundance[,4] %>% hist(breaks = 100)
Protein_DF_Abundance[,5] %>% hist(breaks = 100)
Protein_DF_Abundance[,6] %>% hist(breaks = 100)
Protein_DF_Abundance[,7] %>% hist(breaks = 100)
Protein_DF_Abundance[,8] %>% hist(breaks = 100)
Protein_DF_Abundance[,9] %>% hist(breaks = 100)
Protein_DF_Abundance[,10] %>% hist(breaks = 100)


# Remove non - human peptides 
Protein_DF_Abundance <- Protein_DF_Abundance[!rownames(Protein_DF_Abundance) %in% c("Q6ZSR9", "P15252","P25691","P00761"), ]
Protein_DF_Abundance %>% head()
Protein_DF_Abundance %>% dim()



# View abundances after removing proteins with 5 or more (50%) NA 
Protein_DF_Abundance_imp <- remove_rows_with_nas(Protein_DF_Abundance)
Protein_DF_Abundance_imp %>% dim()
Protein_DF_Abundance_imp[,1] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,2] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,3] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,4] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,5] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,6] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,7] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,8] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,9] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,10] %>% hist(breaks = 100)
Protein_DF_Abundance_imp %>% dim()

Protein_DF_Abundance_imp_2 <- impute.knn(as.matrix(Protein_DF_Abundance_imp), k = 10, rowmax = 0.4)$data
Protein_DF_Abundance_imp_2 %>% dim()
Protein_DF_Abundance_imp_2[,1] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,2] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,3] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,4] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,5] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,6] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,7] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,8] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,9] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,10] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2 %>% dim()
```

# Log2 transform for imputed data
```{r Wrangle Data Frame 3}
log2_norm_counts <- log2(Protein_DF_Abundance_imp_2)
log2_norm_counts %>% rowMeans() %>% hist(breaks = 100)
log2_norm_counts[,1] %>% hist(breaks = 100) 
log2_norm_counts[,2] %>% hist(breaks = 100)
log2_norm_counts[,3] %>% hist(breaks = 100)
log2_norm_counts[,4] %>% hist(breaks = 100)
log2_norm_counts[,5] %>% hist(breaks = 100)
log2_norm_counts[,6] %>% hist(breaks = 100)
log2_norm_counts[,7] %>% hist(breaks = 100)
log2_norm_counts[,8] %>% hist(breaks = 100)
log2_norm_counts[,9] %>% hist(breaks = 100)
log2_norm_counts[,10] %>% hist(breaks = 100)
log2_norm_counts %>% dim()
```

# Quantile Normalization for imputed data
```{r Wrangle Data Frame 4}
normalizedData <- limma::normalizeBetweenArrays(log2_norm_counts[, c(1,2,4,6,7,9)], method = "quantile")
normalizedData %>% rowMeans() %>% hist(breaks = 100)
normalizedData[,1] %>% hist(breaks = 100) 
normalizedData[,2] %>% hist(breaks = 100)
normalizedData[,3] %>% hist(breaks = 100)
normalizedData[,4] %>% hist(breaks = 100)
normalizedData[,5] %>% hist(breaks = 100)
normalizedData[,6] %>% hist(breaks = 100)
normalizedData %>% dim()
```

# View distribution of imputed NA values for all samples  
```{r  Imputed value distribution}
na_positions <- is.na(Protein_DF_Abundance_imp)

imputed_dataframe <- normalizedData

imputed_values <- imputed_dataframe[na_positions] %>% na.omit()

hist(imputed_values, breaks = 50, main = "Histogram of Imputed Values", xlab = "Value")

# Histogram of original data (with NA values removed)
hist(log2(Protein_DF_Abundance_imp) %>% rowMeans(na.rm = TRUE), xlim = range(log2(Protein_DF_Abundance_imp) %>% rowMeans(), na.rm = TRUE), breaks = 50, main = "Histogram with Imputed & Non-imputed Values", xlab = "Value")

# Histogram of imputed values
hist(imputed_values, breaks = 50, add = TRUE, col = "red")
```



# RUV III
```{r RUVIII}
Protein_DF_Abundance_imp_2 %>% head()
Protein_DF_Abundance_imp_2 %>% dim()

# Convert to DGEList object 
dge <- DGEList(counts = as.matrix(Protein_DF_Abundance_imp_2))
dge %>% dim()

# PCA imputed data frame abundance BEFORE RUVIII
prcomp_res <- prcomp(t(Protein_DF_Abundance_imp_2 %>% as.matrix()), center = TRUE, scale. = TRUE)
ggplot2::autoplot(prcomp_res, data = as.data.frame(Meta), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()


# correlation matrix 
Prot_cor_matrix <- cor(Protein_DF_Abundance_imp_2 %>% as.matrix())

# Heatmap 1. 
pheatmap(Prot_cor_matrix, 
         color = colorRampPalette(c("blue", "white", "red"))(200),
         display_numbers = TRUE)

# Adjust column names 
rownames(Prot_cor_matrix) <- Meta$Cond_Ind
colnames(Prot_cor_matrix) <- Meta$Cond_Ind

# Heatmap 2. 
pheatmap(mat = Prot_cor_matrix, 
         color = colorRampPalette(c("blue", "white", "red"))(200),
         display_numbers = TRUE
            )








# Moving on to find the low variance genes across samples 
# for the RUVIII normalization.

# Calculate variability 
cv <- rowSds(dge$counts, useNames = TRUE)/rowMeans(dge$counts)

# Identify the 10% least variable proteins
num_controls <- ceiling(0.05 * nrow(dge$counts))
control_proteins <- names(sort(cv, decreasing = FALSE))[1:num_controls]
control_proteins %>% length()

# Create an index vector
control_proteins_index <- match(control_proteins, rownames(Protein_DF_Abundance_imp_2))
control_proteins_index %>% length()

# Design matrix from metadata
Meta
Model_mat <- replicate.matrix(a = Meta[,c(4)])
Model_mat

Test <- RUVIII(Y = t(Protein_DF_Abundance_imp_2 %>% log2()), M = Model_mat, ctl =control_proteins_index , k = 1, return.info = TRUE)


New_Y <- Test$newY %>% t() 
New_Y[(New_Y %>% rowMeans()) < 0, ]


# PCA of RUVIII normalized abundance values:
prcomp_res <- prcomp(t(New_Y %>% as.matrix()), center = TRUE, scale. = TRUE)
ggplot2::autoplot(prcomp_res, data = as.data.frame(Meta), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()

# correlation matrix 
Prot_cor_matrix <- cor(New_Y %>% as.matrix())

# Heatmap 1. 
pheatmap(Prot_cor_matrix, 
         color = colorRampPalette(c("blue", "white", "red"))(200),
         display_numbers = TRUE)

# Adjust column names 
rownames(Prot_cor_matrix) <- Meta$Cond_Ind
colnames(Prot_cor_matrix) <- Meta$Cond_Ind

# Heatmap 2. 
pheatmap(mat = Prot_cor_matrix, 
         color = colorRampPalette(c("blue", "white", "red"))(200),
         display_numbers = TRUE
            )


New_Y %>% head()
New_Y %>% dim()
New_Y %>% rowMeans() %>% hist(breaks = 100)
New_Y %>% na.omit() %>% dim()
New_Y[,1] %>% hist(breaks = 100)
New_Y[,2] %>% hist(breaks = 100)
New_Y[,3] %>% hist(breaks = 100)
New_Y[,4] %>% hist(breaks = 100)
New_Y[,5] %>% hist(breaks = 100)
New_Y[,6] %>% hist(breaks = 100)
New_Y[,7] %>% hist(breaks = 100)
New_Y[,8] %>% hist(breaks = 100)
New_Y[,9] %>% hist(breaks = 100)
New_Y[,10] %>% hist(breaks = 100)


Meta_sub<-Meta[c(1,2,4,6,7,9),]
counts_RUV_log2_sub <- New_Y[,c(1,2,4,6,7,9)]
counts_RUV_log2_sub %>% head()
counts_RUV_log2_sub %>% dim()
counts_RUV_log2_sub[,1] %>% hist(breaks = 100)
counts_RUV_log2_sub[,2] %>% hist(breaks = 100)
counts_RUV_log2_sub[,3] %>% hist(breaks = 100)
counts_RUV_log2_sub[,4] %>% hist(breaks = 100)
counts_RUV_log2_sub[,5] %>% hist(breaks = 100)
counts_RUV_log2_sub[,6] %>% hist(breaks = 100)
# PCA of RUVIII normalized abundance values:
prcomp_res <- prcomp(t(counts_RUV_log2_sub %>% as.matrix()), center = TRUE, scale. = TRUE)
ggplot2::autoplot(prcomp_res, data = as.data.frame(Meta_sub), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()

# correlation matrix 
Prot_cor_matrix <- cor(counts_RUV_log2_sub %>% as.matrix())

# Heatmap 1. 
pheatmap(Prot_cor_matrix, 
         color = colorRampPalette(c("blue", "white", "red"))(200),
         display_numbers = TRUE)

# Adjust column names 
rownames(Prot_cor_matrix) <- Meta_sub$Cond_Ind
colnames(Prot_cor_matrix) <- Meta_sub$Cond_Ind

# Heatmap 2. 
pheatmap(mat = Prot_cor_matrix, 
         color = colorRampPalette(c("blue", "white", "red"))(200),
         display_numbers = TRUE
            )





counts_RUV_log2_sub_quantnorm <- limma::normalizeBetweenArrays(counts_RUV_log2_sub, method = "quantile")
counts_RUV_log2_sub_quantnorm %>% head()
counts_RUV_log2_sub_quantnorm %>% dim()
Meta_sub
# 1.
counts_RUV_log2_sub_quantnorm[,1] %>% hist(main = "B_77_Dox", breaks = 50)
# 2.
counts_RUV_log2_sub_quantnorm[,2] %>% hist(main = "C_87_Dox", breaks = 50)
# 3.
counts_RUV_log2_sub_quantnorm[,3] %>% hist(main = "A_48_Dox", breaks = 50)
# 4.
counts_RUV_log2_sub_quantnorm[,4] %>% hist(main = "B_77_Control", breaks = 50)
# 5.
counts_RUV_log2_sub_quantnorm[,5] %>% hist(main = "C_87_Control", breaks = 50)
# 6.
counts_RUV_log2_sub_quantnorm[,6] %>% hist(main = "A_48_Control", breaks = 50)

# PCA of RUVIII normalized abundance values:
prcomp_res <- prcomp(t(counts_RUV_log2_sub_quantnorm %>% as.matrix()), center = TRUE, scale. = TRUE)
ggplot2::autoplot(prcomp_res, data = as.data.frame(Meta_sub), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()

# correlation matrix 
Prot_cor_matrix <- cor(counts_RUV_log2_sub_quantnorm %>% as.matrix())

# Heatmap 1. 
pheatmap(Prot_cor_matrix, 
         color = colorRampPalette(c("blue", "white", "red"))(200),
         display_numbers = TRUE)

# Adjust column names 
rownames(Prot_cor_matrix) <- Meta_sub$Cond_Ind
colnames(Prot_cor_matrix) <- Meta_sub$Cond_Ind

# Heatmap 2. 
pheatmap(mat = Prot_cor_matrix, 
         color = colorRampPalette(c("blue", "white", "red"))(200),
         display_numbers = TRUE
            )













# Moving on to the actual linear model 
# Create a DataFrame for the phenoData
phenoData_RUVIII <- DataFrame(Meta)
phenoData_RUVIII <- Meta[c(1,2,4,6,7,9), ]



# View changes 
phenoData_RUVIII



# Create Design Matrix 
# phenoData$Cond <- factor(phenoData$Cond , levels = c("Control", "Dox"))
design <- model.matrix(~ 0 + Cond, data = phenoData_RUVIII)
design


# rename columns 
colnames(design) <- c('Control', "Dox")


# Get model counts 
Model_counts <- counts_RUV_log2_sub_quantnorm


# Fit model
dupcor <- duplicateCorrelation(Model_counts, design = design, block = phenoData_RUVIII$Ind)

fit <- lmFit(object = as.matrix(Model_counts), block = phenoData_RUVIII$Ind, design = design, correlation = dupcor$consensus.correlation)

fit2 <- eBayes(fit)


# Make contrasts
cm <- makeContrasts(
  DoxvNorm = Dox - Control,
  levels = design)


# Model with contrasts
fit2 <- contrasts.fit(fit, cm)
fit2 <- eBayes(fit2, robust = TRUE, trend = TRUE)


# Summarize
results_summary <- decideTests(fit2, adjust.method = "none", p.value = 0.05)
summary(results_summary)



# Toptable summary organized   
toptable_summary_DoxvNorm <- topTable(fit2, coef = "DoxvNorm",number = (nrow(Model_counts)), p.value = 1, adjust.method = "none")
toptable_summary_DoxvNorm$Protein <- rownames(toptable_summary_DoxvNorm)
toptable_summary_DoxvNorm$P.Value %>% hist(breaks = 100)
abline(v = c(0.01,0.025, 0.05, 0.1), col = "red" )

toptable_summary_DoxvNorm %>% head()
toptable_summary_DoxvNorm %>% dim()

# Volcano plots 
# 1. Create a column to threshold P-values 
toptable_summary_DoxvNorm <- toptable_summary_DoxvNorm %>%  mutate(threshold_P = P.Value < 0.05)


# 2. Plot 
ggplot(toptable_summary_DoxvNorm)+
  geom_point(mapping = aes(x = logFC, y = -log10(P.Value), color = threshold_P))+
  xlab("log2FC")+
  ylab("-log10 nominal p-value")+
  ylim(0, 7)+
  xlim(-6, 6)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()


# Make top_proteins your toptable summary 
top_proteins <- toptable_summary_DoxvNorm[1:5, ] %>% rownames()

# Loop through each of the top proteins within the Model_counts
for (i in top_proteins) {
  # Create a boxplot for each protein
  boxplot(Model_counts[i, ] ~ Meta_sub$Cond, 
          main = i, 
          xlab = "Condition", 
          ylab = "log2-RUVIII-Quantnorm Abundance", 
          col = c("lightblue", "red2"),
          las = 2)  # las = 2 makes the axis labels perpendicular to the axis


}


# Comparing to a different cutoff
top_proteins <- toptable_summary_DoxvNorm[(toptable_summary_DoxvNorm$P.Value < 0.05) & (toptable_summary_DoxvNorm$P.Value > 0.0495),] %>% rownames()

# Loop through each of the top proteins within the Model_counts
for (i in top_proteins) {
  # Create a boxplot for each protein
  boxplot(Model_counts[i, ] ~ Meta_sub$Cond, 
          main = i, 
          xlab = "Condition", 
          ylab = "log2-RUVIII-Quantnorm Abundance", 
          col = c("lightblue", "red2"),
          las = 2)  # las = 2 makes the axis labels perpendicular to the axis


}

```