---
title: "Differentially_abundant_proteins_imputed"
output: html_document
date: "2023-12-06"
---
# Load Libraries 
```{r Libraries, include=FALSE}

library(EDASeq)
library(RUVSeq)
library(RColorBrewer)
library(edgeR)
library(limma)
library(Biobase)
library(SummarizedExperiment)
library(tidyverse) 
library(ggfortify)
library(cluster)
library(edgeR)
library(limma)
library(Homo.sapiens)
library(BiocParallel)
library(qvalue)
library(pheatmap)
library(clusterProfiler)
library(AnnotationDbi)
library(org.Hs.eg.db)
library(RColorBrewer)
library(variancePartition)
library(DOSE)
library(UpSetR)
library(ggvenn)
library(biomaRt)
library(ggridges)
library(reshape2)
library(BioNERO)
library(WGCNA)
library(impute)
```

# Added funtions 
```{r Added functions}
remove_rows_with_nas <- function(data_frame) {
  data_frame[rowSums(is.na(data_frame)) < 5, ]
}
```
# Steps  
```{r Steps to take}
#* 1. Take Abundance values/counts 
#* 2. Remove NA values from Abundance values 
#* 3. Apply log2 transform to Abundance values 
#* 4. Quantile normalize abundance values 
#* 5. RUVs applied to account for technical variation 
#* 6. Use Limma to model differential protein abundaance 
```


# Read in Data 
```{r Read in Data}

# Load your data
Protein_DF <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/Abundance.csv", header = TRUE)

# Include metadata about samples 
Meta <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/Meta.csv", header = TRUE)
```


# Wrangle Data Frame 
```{r Wrangle Data Frame}
# Save the original 
Full_DF <- Protein_DF 


# Subset the columns referring to abundance
Protein_DF_Abundance <- Protein_DF[,c(4, 5:ncol(Protein_DF))] 

# Check for duplicated rows 
# Identify duplicated values
Protein_DF_Abundance$duplicated_name <- duplicated(Protein_DF_Abundance$Accession)

# This will return a logical vector where TRUE indicates the position of duplicates in the column.
# To see only rows with duplicated values, you can subset the dataframe like this:
duplicated_rows <- Protein_DF_Abundance[Protein_DF_Abundance$duplicated_name == TRUE, ]
print(duplicated_rows)

# We have 3 rows with duplicates, two of which have NA values. We will remove them now since we will go ahead 
# and remove the duplicated rows later on anyways. 
Protein_DF_Abundance <- Protein_DF_Abundance[- c(61, 276, 997), ] 

# Make rownames of the data frame accession IDs
rownames(Protein_DF_Abundance) <- Protein_DF_Abundance$Accession

# Change colnames 
colnames(Protein_DF_Abundance)
Protein_DF_Abundance <- Protein_DF_Abundance[, -c(1, 12)]

# Assuming column names of Protein_DF match with the rows in Meta
rownames(Meta) <- Meta$Samples

colnames(Protein_DF_Abundance) <- Meta$Samples
```


# NA removal and imputing with knn
```{r knn impute NA}
Protein_DF_Abundance_imp <- remove_rows_with_nas(Protein_DF_Abundance)
Protein_DF_Abundance_imp %>% dim()

Protein_DF_Abundance_imp_2 <- impute.knn(as.matrix(Protein_DF_Abundance_imp), k = 15, rowmax = 0.4)$data
Protein_DF_Abundance_imp_2 %>% dim()
```


# Log2 transform
```{r Log2}
log2_norm_counts <- log2(Protein_DF_Abundance_imp_2)
```


# Quantile Normalization 
```{r Quantile Normalization}
normalizedData <- limma::normalizeBetweenArrays(log2_norm_counts, method = "quantile")
```


# Prepare Data Object for RUVs 
```{r Prepare Data Object for RUVs}
#  counts need to be integer values and in a numeric matrix 
counts <- as.matrix(normalizedData) 

# Create a DataFrame for the phenoData
phenoData <- DataFrame(Meta)

# Now create the RangedSummarizedExperiment necessary for RUVs input 
set <- SummarizedExperiment(assays =  normalizedData, metadata =phenoData)
```


# RUVs Matrix 
```{r RUVs}
# Generate a background matrix where each set of replicates are in a row
# and null spaces where there are replicate mismatches get the value -1. 
# This will be used in the RUVs function, which is the typeII method to
# remove unwanted variation in the RUVs package. This will be used for all 
# RUVs permutations where the number of variation factors will be changed. 
scIdx <- matrix(-1, nrow = 6, ncol = 3)
scIdx[1, 1:3] <- c(which(colnames(counts) %in% c("S6", "S8", "S10"))) # Control group- Technical reps Ind. 48-1
scIdx[2, 1:3] <- c(which(colnames(counts) %in% c("S5", "S7", "S9"))) # Dox group- Technical reps Ind. 48-1
scIdx[3, 1] <- c(which(colnames(counts) %in% c("S2"))) # Control group- Bio reps Ind. 77-1
scIdx[4, 1] <- c(which(colnames(counts) %in% c("S1"))) # Dox group- 77-1
scIdx[5, 1] <- c(which(colnames(counts) %in% c("S4"))) # Control group- Bio reps Ind. 87-1
scIdx[6, 1] <- c(which(colnames(counts) %in% c("S3"))) # Dox group- 87-1
scIdx
```


# Linear Modelling 
```{r Linear Modelling}
# Apply RUVs function from RUVSeq and add to set object
set <- RUVSeq::RUVs(x = normalizedData, k = 1, scIdx = scIdx, isLog = TRUE)
RUV_1 <- set$W[,1]

set$W
phenoData$RUV_1 <- RUV_1


# Create Design Matrix 
# phenoData$Cond <- factor(phenoData$Cond , levels = c("Control", "Dox"))
design <- model.matrix(~0 + Cond + RUV_1, phenoData)
design

# rename columns 
colnames(design) <- c('Control', "Dox", "RUV_1")


# Fit model
fit <- lmFit(set$normalizedCounts, design)
fit2 <- eBayes(fit)


# Make contrasts
cm <- makeContrasts(
  DoxvNorm = Dox - Control,
  levels = design)


# Model with contrasts
fit2 <- contrasts.fit(fit, cm)
fit2 <- eBayes(fit2, robust = TRUE, trend = TRUE)


# Summarize
results_summary <- decideTests(fit2, adjust.method = "none", p.value = 0.05)
summary(results_summary)
```
 

# Organize toptable 
```{r Organize toptable}
# Toptable summary organized to contain results for all tested proteins   
toptable_summary <- topTable(fit2, coef = "DoxvNorm",number = (nrow(set$normalizedCounts )), p.value = 1, adjust.method = "none")
toptable_summary$Protein <- rownames(toptable_summary)
```


# Histograms of Abundance and P-values 
```{r Histograms}
# log2 transformed abundance values per sample 
long_df <- pivot_longer( as.data.frame(log2_norm_counts), cols = everything(), names_to = "Sample", values_to = "Abundance")

ggplot(long_df, aes(x = Abundance, y = Sample, fill = Sample)) +
  geom_density_ridges(scale = 0.9) +
  labs(x = "Abundance", y = "Sample", title = "Log2 Abundance distribution") +
  theme_ridges() +
  scale_fill_viridis_d()




# log2-quantile normalized-RUVs- abundance values per sample 
quantnormcountmatrix <- as.data.frame(set$normalizedCounts)

long_df <- pivot_longer(quantnormcountmatrix, cols = everything(), names_to = "Sample", values_to = "Abundance")

ggplot(long_df, aes(x = Abundance, y = Sample, fill = Sample)) +
  geom_density_ridges(scale = 0.9) +
  labs(x = " Abundance", y = "Sample", title = "Log2-Quantile Norm.- RUVs Abundance distribution") +
  theme_ridges() +
  scale_fill_viridis_d()



# Average expression of log2 quantile normalized values
toptable_summary$AveExpr %>% hist(breaks = 100)


# Nominal Pvalue distribution 
toptable_summary$P.Value %>% hist(breaks = 100)
```


# Volcano plots 
```{r Volcano plots}
# 1. Create a column to threshold P-values 
toptable_summary <- toptable_summary %>%  mutate(threshold_P = P.Value < 0.05)

# 2. Plot 
ggplot(toptable_summary)+
  geom_point(mapping = aes(x = logFC, y = -log10(P.Value), color = threshold_P))+
  xlab("log2FC")+
  ylab("-log10 nominal p-value")+
  ylim(0, 10)+
  xlim(-7, 7)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()
```


# Boxplots for top 3 most differentially abundant proteins
```{r Boxplots}
# View most signifigantly differentially abundant proteins in toptable_summary
toptable_summary[1:3, ]


# 1. Plot the first most signifigant diff. abundant protein 
quantnormcountmatrix <- as.matrix(quantnormcountmatrix)
boxplot(quantnormcountmatrix["Q15327",] ~ Meta$Cond, data=Meta, main="Q15327",
        ylab="Log2 Abundance", xlab="", col = c("skyblue2","red")) 


# 2. Plot the second most signifigant diff. abundant protein 
quantnormcountmatrix <- as.matrix(quantnormcountmatrix)
boxplot(quantnormcountmatrix["O76021",] ~ Meta$Cond, data=Meta, main="O76021",
        ylab="Log2 Abundance", xlab="", col = c("skyblue2","red")) 


# 3. Plot the third most signifigant diff. abundant protein 
quantnormcountmatrix <- as.matrix(quantnormcountmatrix)
boxplot(quantnormcountmatrix["Q969Q1",] ~ Meta$Cond, data=Meta, main="Q969Q1",
        ylab="Log2 Abundance", xlab="", col = c("skyblue2","red")) 

```

# PCA before processing
```{r PCA before}
# PCA of log2-quantile normalized-RUVs values:
prcomp_res <- prcomp(t(log2_norm_counts %>% as.matrix()), center = TRUE)

ggplot2::autoplot(prcomp_res, data = Meta, colour = "Cond", shape = "Ind", size =4)+
  theme_bw()
```



# PCA after processing
```{r PCA After}
# PCA of log2-quantile normalized-RUVs values:
prcomp_res <- prcomp(t(set$normalizedCounts %>% as.matrix()), center = TRUE)

ggplot2::autoplot(prcomp_res, data = Meta, colour = "Cond", shape = "Ind", size =4)+
  theme_bw()
```



# Heatmaps before processing 
```{r Heatmaps before}
phenoData

pheatmap::pheatmap(log2_norm_counts %>% as.matrix(),
                   cluster_rows = TRUE, 
                   cluster_cols = TRUE,
                   show_rownames = FALSE,
                   show_colnames = TRUE
)


cor(log2_norm_counts %>% as.matrix()) %>% pheatmap(
  cluster_rows = TRUE, 
  cluster_cols = TRUE,
  show_rownames = TRUE,
  show_colnames = TRUE)

```


# Heatmaps after processing 
```{r Heatmaps after}
phenoData

pheatmap::pheatmap(set$normalizedCounts %>% as.matrix(),
                   cluster_rows = TRUE, 
                   cluster_cols = TRUE,
                   show_rownames = FALSE,
                   show_colnames = TRUE
)


cor(set$normalizedCounts %>% as.matrix()) %>% pheatmap(
  cluster_rows = TRUE, 
  cluster_cols = TRUE,
  show_rownames = TRUE,
  show_colnames = TRUE)

```
