---
title: "Diff_abundance_231207"
output: html_document
date: "2023-12-08"
---

# Load Libraries 
```{r Libraries, include=FALSE}
library(EDASeq)
library(RUVSeq)
library(RColorBrewer)
library(edgeR)
library(limma)
library(Biobase)
library(SummarizedExperiment)
library(tidyverse) 
library(ggfortify)
library(cluster)
library(edgeR)
library(limma)
library(Homo.sapiens)
library(BiocParallel)
library(qvalue)
library(pheatmap)
library(clusterProfiler)
library(AnnotationDbi)
library(org.Hs.eg.db)
library(RColorBrewer)
library(variancePartition)
library(DOSE)
library(UpSetR)
library(ggvenn)
library(biomaRt)
library(ggridges)
library(reshape2)
library(BioNERO)
library(WGCNA)
library(impute)
```


# Added funtions 
```{r Added functions}
# 1
remove_rows_with_nas <- function(data_frame) {
  data_frame[rowSums(is.na(data_frame)) < 5, ]
}
# 2
remove_rows_with_nas_var <- function(data_frame, NA_remove) {
  data_frame[rowSums(is.na(data_frame)) < NA_remove, ]
}
# 3
plot_nrow_vs_naremove <- function(data_frame) {
  results <- data.frame(NA_remove = integer(), Rows_Remaining = integer())

  for (i in 1:ncol(data_frame)) {
    filtered_df <- remove_rows_with_nas_var(data_frame, NA_remove = i)
    results <- rbind(results, data.frame(NA_remove = i, Rows_Remaining = nrow(filtered_df)))
  }

  ggplot(results, aes(x = NA_remove, y = Rows_Remaining)) +
    geom_point() +
    geom_line() +
    xlab("Na tolerance threshold") +
    ylab("Number of proteins remaining") +
    theme_minimal()
}



```


# Read in Data 
```{r Read in Data 1}

# Load your data
Protein_DF <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/Abundance.csv", header = TRUE)

# Include metadata about samples 
Meta <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/Meta.csv", header = TRUE)
```


# Wrangle Data Frame 
```{r Wrangle Data Frame 1}
# Save the original 
Full_DF <- Protein_DF 


# Subset the columns referring to abundance
Protein_DF_Abundance <- Protein_DF[,c(4, 5:ncol(Protein_DF))] 

# Check for duplicated rows 
# Identify duplicated values
Protein_DF_Abundance$duplicated_name <- duplicated(Protein_DF_Abundance$Accession)

# This will return a logical vector where TRUE indicates the position of duplicates in the column.
# To see only rows with duplicated values, you can subset the dataframe like this:
duplicated_rows <- Protein_DF_Abundance[Protein_DF_Abundance$duplicated_name == TRUE, ]
print(duplicated_rows)

# We have 3 rows with duplicates, two of which have NA values. We will remove them now since we will go ahead 
# and remove the duplicated rows later on anyways. 
Protein_DF_Abundance <- Protein_DF_Abundance[- c(61, 276, 997), ] 

# Make rownames of the data frame accession IDs
rownames(Protein_DF_Abundance) <- Protein_DF_Abundance$Accession

# Change colnames 
colnames(Protein_DF_Abundance)
Protein_DF_Abundance <- Protein_DF_Abundance[, -c(1, 12)]

# Assuming column names of Protein_DF match with the rows in Meta
rownames(Meta) <- Meta$Samples

colnames(Protein_DF_Abundance) <- Meta$Samples
```


# Remove NA
```{r Wrangle Data Frame 234}
#1.  Find rows with any NA values
rows_with_na <- apply(Protein_DF_Abundance, 1, function(x) any(is.na(x))) %>% which()
 

rows_with_na <- as.numeric(rows_with_na)


# 2. Remove rows with NA values 
Protein_DF_Abundance <- Protein_DF_Abundance[-rows_with_na, ]

# 3. Sanity check 
Protein_DF_Abundance %>% dim()
```


# Log2 transform 
```{r Wrangle Data Frame 90}
log2_norm_counts <- log2(Protein_DF_Abundance)
log2_norm_counts %>% rowMeans() %>% hist(breaks = 100)
```


# Quantile Normalization 
```{r Wrangle Data Frame 55}
normalizedData <- limma::normalizeBetweenArrays(log2_norm_counts[, c(1,2,4,6,7,9)], method = "quantile")
normalizedData %>% rowMeans() %>% hist(breaks = 100)
```


# Linear model - RUVs 
```{r upcor on 6 samples 2}
#  counts need to be integer values and in a numeric matrix 
counts <- as.matrix(normalizedData) 
counts %>% dim()
# Create a DataFrame for the phenoData
phenoData <- DataFrame(Meta)
phenoData_sub <- phenoData[c(1,2,4,6,7,9), ]


# Create Design Matrix 
# phenoData$Cond <- factor(phenoData$Cond , levels = c("Control", "Dox"))
design <- model.matrix(~ 0 + Cond , phenoData_sub)
design

# rename columns 
colnames(design) <- c('Control', "Dox")


# Fit model
dupcor <- duplicateCorrelation(counts , design, block = phenoData_sub$Ind)
fit <- lmFit(object = counts, design = design, block = phenoData_sub$Ind, correlation = dupcor$consensus)
fit2 <- eBayes(fit)


# Make contrasts
cm <- makeContrasts(
  DoxvNorm = Dox - Control,
  levels = design)


# Model with contrasts
fit2 <- contrasts.fit(fit, cm)
fit2 <- eBayes(fit2 )


# Summarize
results_summary <- decideTests(fit2, adjust.method = "none", p.value = 0.05)
summary(results_summary)






# Toptable summary organized to contain results for all tested proteins   
toptable_summary <- topTable(fit2, coef = "DoxvNorm",number = (nrow(normalizedData)), p.value = 1, adjust.method = "none")
toptable_summary$Protein <- rownames(toptable_summary)
toptable_summary$P.Value %>% hist(breaks = 100)



# PCA of log2-quantile normalized-RUVs values:
prcomp_res <- prcomp(t(normalizedData %>% as.matrix()), center = TRUE)

ggplot2::autoplot(prcomp_res, data = as.data.frame(phenoData_sub), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()


# Volcano plots 
# 1. Create a column to threshold P-values 
toptable_summary <- toptable_summary %>%  mutate(threshold_P = P.Value < 0.05)

# 2. Plot 
ggplot(toptable_summary)+
  geom_point(mapping = aes(x = logFC, y = -log10(P.Value), color = threshold_P))+
  xlab("log2FC")+
  ylab("-log10 nominal p-value")+
  ylim(0, 10)+
  xlim(-7, 7)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()


# Other fits 
fit3 <- eBayes(fit2, robust = TRUE, trend = TRUE)


# Summarize
results_summary <- decideTests(fit3, adjust.method = "none", p.value = 0.05)
summary(results_summary)


# Toptable summary organized to contain results for all tested proteins   
toptable_summary <- topTable(fit3, coef = "DoxvNorm",number = (nrow(normalizedData)), p.value = 1, adjust.method = "none")
toptable_summary$Protein <- rownames(toptable_summary)
toptable_summary$P.Value %>% hist(breaks = 100)


# PCA of log2-quantile normalized-RUVs values:
prcomp_res <- prcomp(t(normalizedData %>% as.matrix()), center = TRUE)


ggplot2::autoplot(prcomp_res, data = as.data.frame(phenoData_sub), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()


# Volcano plots 
# 1. Create a column to threshold P-values 
toptable_summary <- toptable_summary %>%  mutate(threshold_P = P.Value < 0.05)


# 2. Plot 
ggplot(toptable_summary)+
  geom_point(mapping = aes(x = logFC, y = -log10(P.Value), color = threshold_P))+
  xlab("log2FC")+
  ylab("-log10 nominal p-value")+
  ylim(0, 10)+
  xlim(-7, 7)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()
```


# Linear model + RUVs 
```{r MW suggested workflow }
# 1. Get non log abundance values 
Protein_DF_Abundance %>% head()
Protein_DF_Abundance %>% dim()



# 2. Generate RUVs related objects (differences_all and set_all)
Meta
genes_all <- rownames(Protein_DF_Abundance)
x_all <- c(1,2,3,3,3,4,5,6,6,6)
differences_all <- makeGroups(x_all)


set_all <- newSeqExpressionSet(as.matrix(Protein_DF_Abundance),phenoData = data.frame(x_all, row.names=colnames(Protein_DF_Abundance)))




# 3. Get RUV weights using all 10 samples and view for different values of "k"
# K =1 
set_all_RUV <- RUVSeq::RUVs(set_all, genes_all, k=1, differences_all, isLog = FALSE)
prcomp_res <- prcomp(t(as.matrix(assayData(set_all_RUV)$normalizedCounts)))
ggplot2::autoplot(prcomp_res, data = as.data.frame(Meta), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()

# K =2 
set_all_RUV <- RUVSeq::RUVs(set_all, genes_all, k=2, differences_all, isLog = FALSE)
prcomp_res <- prcomp(t(as.matrix(assayData(set_all_RUV)$normalizedCounts)))
ggplot2::autoplot(prcomp_res, data = as.data.frame(Meta), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()

# K =3 
set_all_RUV <- RUVSeq::RUVs(set_all, genes_all, k=3, differences_all, isLog = FALSE)
prcomp_res <- prcomp(t(as.matrix(assayData(set_all_RUV)$normalizedCounts)))
ggplot2::autoplot(prcomp_res, data = as.data.frame(Meta), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()

# Proceed with K =1 
set_all_RUV <- RUVSeq::RUVs(set_all, genes_all, k=1, differences_all, isLog = FALSE)


# 4. Subset counts by the 6 columns of interest, Metadata by 6 rows of interest, RUV weights vector to the 6 values of interest
#  counts need to be integer values and in a numeric matrix 
counts_RUVs <- as.matrix(Protein_DF_Abundance) 

# Create a DataFrame for the phenoData
phenoData_RUVs <- DataFrame(Meta)
phenoData_RUVs <- phenoData_RUVs[c(1,2,4,6,7,9), ]

counts_RUVs <- counts_RUVs[,c(1,2,4,6,7,9)]

counts_RUVs %>% dim()
phenoData_RUVs %>% dim()


RUV_1 <- set_all_RUV$W_1
phenoData_RUVs$RUV_1 <- RUV_1[c(1,2,4,6,7,9)]


# View changes 
phenoData_RUVs %>% head()
counts_RUVs %>% head()




# 5. Take the info from 4 and assign it to a new object
counts_RUV_nolog <- assayData(set_all_RUV)$counts
counts_RUV_nolog %>% head()
counts_RUV_nolog %>% dim()
counts_RUV_nolog[,1] %>% hist(breaks = 100)
counts_RUV_nolog[,2] %>% hist(breaks = 100)
counts_RUV_nolog[,3] %>% hist(breaks = 100)
counts_RUV_nolog[,4] %>% hist(breaks = 100)
counts_RUV_nolog[,5] %>% hist(breaks = 100)
counts_RUV_nolog[,6] %>% hist(breaks = 100)
counts_RUV_nolog[,7] %>% hist(breaks = 100)
counts_RUV_nolog[,8] %>% hist(breaks = 100)
counts_RUV_nolog[,9] %>% hist(breaks = 100)
counts_RUV_nolog[,10] %>% hist(breaks = 100)





counts_RUV_normalized <- assayData(set_all_RUV)$normalizedCounts
counts_RUV_normalized %>% head()
counts_RUV_normalized %>% dim()
counts_RUV_normalized[,1] %>% hist(breaks = 100)
counts_RUV_normalized[,2] %>% hist(breaks = 100)
counts_RUV_normalized[,3] %>% hist(breaks = 100)
counts_RUV_normalized[,4] %>% hist(breaks = 100)
counts_RUV_normalized[,5] %>% hist(breaks = 100)
counts_RUV_normalized[,6] %>% hist(breaks = 100)
counts_RUV_normalized[,7] %>% hist(breaks = 100)
counts_RUV_normalized[,8] %>% hist(breaks = 100)
counts_RUV_normalized[,9] %>% hist(breaks = 100)
counts_RUV_normalized[,10] %>% hist(breaks = 100)






counts_RUV_log2 <- assayData(set_all_RUV)$normalizedCounts %>% log2()
counts_RUV_log2 %>% head()
counts_RUV_log2 %>% dim()
counts_RUV_log2[,1] %>% hist(breaks = 100)
counts_RUV_log2[,2] %>% hist(breaks = 100)
counts_RUV_log2[,3] %>% hist(breaks = 100)
counts_RUV_log2[,4] %>% hist(breaks = 100)
counts_RUV_log2[,5] %>% hist(breaks = 100)
counts_RUV_log2[,6] %>% hist(breaks = 100)
counts_RUV_log2[,7] %>% hist(breaks = 100)
counts_RUV_log2[,8] %>% hist(breaks = 100)
counts_RUV_log2[,9] %>% hist(breaks = 100)
counts_RUV_log2[,10] %>% hist(breaks = 100)


counts_RUV_log2_sub <- counts_RUV_log2[,c(1,2,4,6,7,9)]
counts_RUV_log2_sub %>% head()
counts_RUV_log2_sub %>% dim()
counts_RUV_log2_sub[,1] %>% hist(breaks = 100)
counts_RUV_log2_sub[,2] %>% hist(breaks = 100)
counts_RUV_log2_sub[,3] %>% hist(breaks = 100)
counts_RUV_log2_sub[,4] %>% hist(breaks = 100)
counts_RUV_log2_sub[,5] %>% hist(breaks = 100)
counts_RUV_log2_sub[,6] %>% hist(breaks = 100)




counts_RUV_log2_sub_quantnorm <- limma::normalizeBetweenArrays(counts_RUV_log2_sub, method = "quantile")
counts_RUV_log2_sub_quantnorm %>% head()
counts_RUV_log2_sub_quantnorm %>% dim()
counts_RUV_log2_sub_quantnorm[,1] %>% hist(breaks = 100)
counts_RUV_log2_sub_quantnorm[,2] %>% hist(breaks = 100)
counts_RUV_log2_sub_quantnorm[,3] %>% hist(breaks = 100)
counts_RUV_log2_sub_quantnorm[,4] %>% hist(breaks = 100)
counts_RUV_log2_sub_quantnorm[,5] %>% hist(breaks = 100)
counts_RUV_log2_sub_quantnorm[,6] %>% hist(breaks = 100)




# Create Design Matrix 
# phenoData$Cond <- factor(phenoData$Cond , levels = c("Control", "Dox"))
design <- model.matrix(~ 0 + Cond + RUV_1, data = phenoData_RUVs)
design


# rename columns 
colnames(design) <- c('Control', "Dox", "RUV_1")


# Get model counts 
Model_counts <- counts_RUV_log2_sub_quantnorm


# Fit model
dupcor <- duplicateCorrelation(as.matrix(Model_counts), design, block = phenoData_RUVs$Ind)
fit <- lmFit(object = as.matrix(Model_counts), design = design, block = phenoData_RUVs$Ind, correlation = dupcor$consensus)
fit2 <- eBayes(fit)


# Make contrasts
cm <- makeContrasts(
  DoxvNorm = Dox - Control,
  levels = design)


# Model with contrasts
fit2 <- contrasts.fit(fit, cm)
fit2 <- eBayes(fit2)


# Summarize
results_summary <- decideTests(fit2, adjust.method = "none", p.value = 0.05)
summary(results_summary)


# Toptable summary organized to contain results for all tested proteins   
toptable_summary <- topTable(fit2, coef = "DoxvNorm",number = (nrow(Model_counts)), p.value = 1, adjust.method = "none")
toptable_summary$Protein <- rownames(toptable_summary)
toptable_summary$P.Value %>% hist(breaks = 100)




# PCA of log2-quantile normalized-RUVs values:
Model_counts_PCA <- na.omit(Model_counts)
sum(is.na(Model_counts_PCA))

Model_counts_PCA %>% dim()
prcomp_res <- prcomp(t(as.matrix(Model_counts_PCA)))
ggplot2::autoplot(prcomp_res, data = as.data.frame(phenoData_RUVs), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()




# Volcano plots 
# 1. Create a column to threshold P-values 
toptable_summary <- toptable_summary %>%  mutate(threshold_P = P.Value < 0.05)


# 2. Plot 
ggplot(toptable_summary)+
  geom_point(mapping = aes(x = logFC, y = -log10(P.Value), color = threshold_P))+
  xlab("log2FC")+
  ylab("-log10 nominal p-value")+
  ylim(0, 6)+
  xlim(-7, 7)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()
```


# Wrangle Data Frame for imputed data
```{r Wrangle Data Frame impute}
# Save the original 
Full_DF <- Protein_DF 


# Subset the columns referring to abundance
Protein_DF_Abundance <- Protein_DF[,c(4, 5:ncol(Protein_DF))] 

# Check for duplicated rows 
# Identify duplicated values
Protein_DF_Abundance$duplicated_name <- duplicated(Protein_DF_Abundance$Accession)

# This will return a logical vector where TRUE indicates the position of duplicates in the column.
# To see only rows with duplicated values, you can subset the dataframe like this:
duplicated_rows <- Protein_DF_Abundance[Protein_DF_Abundance$duplicated_name == TRUE, ]
print(duplicated_rows)

# We have 3 rows with duplicates, two of which have NA values. We will remove them now since we will go ahead 
# and remove the duplicated rows later on anyways. 
Protein_DF_Abundance <- Protein_DF_Abundance[- c(61, 276, 997), ] 

# Make rownames of the data frame accession IDs
rownames(Protein_DF_Abundance) <- Protein_DF_Abundance$Accession

# Change colnames 
colnames(Protein_DF_Abundance)
Protein_DF_Abundance <- Protein_DF_Abundance[, -c(1, 12)]

# Assuming column names of Protein_DF match with the rows in Meta
rownames(Meta) <- Meta$Samples

colnames(Protein_DF_Abundance) <- Meta$Samples
```


# Viewing how NA threshold vs remaining proteins  
```{r viewing NA and imp}

# View how NA thresholds affect the amount of proteins remaining to model
# All proteins 
Protein_DF_Abundance %>% nrow()

# Removing proteins with 1 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 1 ) %>% nrow()

# Removing proteins with 2 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 2 ) %>% nrow()

# Removing proteins with 3 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 3 ) %>% nrow()

# Removing proteins with 4 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 4 ) %>% nrow()

# Removing proteins with 5 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 5 ) %>% nrow()

# Removing proteins with 6 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 6 ) %>% nrow()

# Removing proteins with 7 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 7 ) %>% nrow()

# Removing proteins with 8 or more NA
remove_rows_with_nas_var(data_frame = Protein_DF_Abundance , NA_remove = 8 ) %>% nrow()

# View in graph 
plot_nrow_vs_naremove(Protein_DF_Abundance)
```


# NA removal and imputing with knn
```{r knn impute NA}
# View original abundances 
Protein_DF_Abundance %>% head()
Protein_DF_Abundance[,1] %>% hist(breaks = 100)
Protein_DF_Abundance[,2] %>% hist(breaks = 100)
Protein_DF_Abundance[,3] %>% hist(breaks = 100)
Protein_DF_Abundance[,4] %>% hist(breaks = 100)
Protein_DF_Abundance[,5] %>% hist(breaks = 100)
Protein_DF_Abundance[,6] %>% hist(breaks = 100)
Protein_DF_Abundance[,7] %>% hist(breaks = 100)
Protein_DF_Abundance[,8] %>% hist(breaks = 100)
Protein_DF_Abundance[,9] %>% hist(breaks = 100)
Protein_DF_Abundance[,10] %>% hist(breaks = 100)

# View abundances after removing proteins with 5 or more (50%) NA 
Protein_DF_Abundance_imp <- remove_rows_with_nas(Protein_DF_Abundance)
Protein_DF_Abundance_imp %>% dim()
Protein_DF_Abundance_imp[,1] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,2] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,3] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,4] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,5] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,6] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,7] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,8] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,9] %>% hist(breaks = 100)
Protein_DF_Abundance_imp[,10] %>% hist(breaks = 100)


Protein_DF_Abundance_imp_2 <- impute.knn(as.matrix(Protein_DF_Abundance_imp), k = 10, rowmax = 0.4)$data
Protein_DF_Abundance_imp_2 %>% dim()
Protein_DF_Abundance_imp_2[,1] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,2] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,3] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,4] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,5] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,6] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,7] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,8] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,9] %>% hist(breaks = 100)
Protein_DF_Abundance_imp_2[,10] %>% hist(breaks = 100)

```


# Log2 transform for imputed data
```{r Wrangle Data Frame 3}
log2_norm_counts <- log2(Protein_DF_Abundance_imp_2)
log2_norm_counts %>% rowMeans() %>% hist(breaks = 100)
log2_norm_counts[,1] %>% hist(breaks = 100) 
log2_norm_counts[,2] %>% hist(breaks = 100)
log2_norm_counts[,3] %>% hist(breaks = 100)
log2_norm_counts[,4] %>% hist(breaks = 100)
log2_norm_counts[,5] %>% hist(breaks = 100)
log2_norm_counts[,6] %>% hist(breaks = 100)
log2_norm_counts[,7] %>% hist(breaks = 100)
log2_norm_counts[,8] %>% hist(breaks = 100)
log2_norm_counts[,9] %>% hist(breaks = 100)
log2_norm_counts[,10] %>% hist(breaks = 100)
```


# Quantile Normalization for imputed data
```{r Wrangle Data Frame 4}
normalizedData <- limma::normalizeBetweenArrays(log2_norm_counts[, c(1,2,4,6,7,9)], method = "quantile")
normalizedData %>% rowMeans() %>% hist(breaks = 100)
normalizedData[,1] %>% hist(breaks = 100) 
normalizedData[,2] %>% hist(breaks = 100)
normalizedData[,3] %>% hist(breaks = 100)
normalizedData[,4] %>% hist(breaks = 100)
normalizedData[,5] %>% hist(breaks = 100)
normalizedData[,6] %>% hist(breaks = 100)
```


# View distribution of imputed NA values for all samples  
```{r  Imputed value distribution}
na_positions <- is.na(Protein_DF_Abundance_imp)

imputed_dataframe <- normalizedData

imputed_values <- imputed_dataframe[na_positions]

hist(imputed_values, main = "Histogram of Imputed Values", xlab = "Value")

# Histogram of original data (with NA values removed)
hist(log2(Protein_DF_Abundance_imp) %>% rowMeans(), xlim = range(log2(Protein_DF_Abundance_imp) %>% rowMeans(), na.rm = TRUE), main = "Histogram with Imputed & Non-imputed Values", xlab = "Value")

# Histogram of imputed values
hist(imputed_values, add = TRUE, col = rgb(1, 0, 0, 0.5))
```


# Linear model - RUVs + Imputation 
```{r upcor on 6 samples 22}
#  counts need to be integer values and in a numeric matrix 
counts <- as.matrix(normalizedData) 
counts %>% dim()
# Create a DataFrame for the phenoData
phenoData <- DataFrame(Meta)
phenoData_sub <- phenoData[c(1,2,4,6,7,9), ]


# Create Design Matrix 
# phenoData$Cond <- factor(phenoData$Cond , levels = c("Control", "Dox"))
design <- model.matrix(~ 0 + Cond , phenoData_sub)
design

# rename columns 
colnames(design) <- c('Control', "Dox")


# Fit model
dupcor <- duplicateCorrelation(counts , design, block = phenoData_sub$Ind)
fit <- lmFit(object = counts, design = design, block = phenoData_sub$Ind, correlation = dupcor$consensus)
fit2 <- eBayes(fit)


# Make contrasts
cm <- makeContrasts(
  DoxvNorm = Dox - Control,
  levels = design)


# Model with contrasts
fit2 <- contrasts.fit(fit, cm)
fit2 <- eBayes(fit2 )


# Summarize
results_summary <- decideTests(fit2, adjust.method = "none", p.value = 0.05)
summary(results_summary)






# Toptable summary organized to contain results for all tested proteins   
toptable_summary <- topTable(fit2, coef = "DoxvNorm",number = (nrow(normalizedData)), p.value = 1, adjust.method = "none")
toptable_summary$Protein <- rownames(toptable_summary)
toptable_summary$P.Value %>% hist(breaks = 100)



# PCA of log2-quantile normalized-RUVs values:
prcomp_res <- prcomp(t(normalizedData %>% as.matrix()), center = TRUE)

ggplot2::autoplot(prcomp_res, data = as.data.frame(phenoData_sub), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()


# Volcano plots 
# 1. Create a column to threshold P-values 
toptable_summary <- toptable_summary %>%  mutate(threshold_P = P.Value < 0.05)

# 2. Plot 
ggplot(toptable_summary)+
  geom_point(mapping = aes(x = logFC, y = -log10(P.Value), color = threshold_P))+
  xlab("log2FC")+
  ylab("-log10 nominal p-value")+
  ylim(0, 10)+
  xlim(-7, 7)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()


# Other fits 
fit3 <- eBayes(fit2, robust = TRUE, trend = TRUE)


# Summarize
results_summary <- decideTests(fit3, adjust.method = "none", p.value = 0.05)
summary(results_summary)


# Toptable summary organized to contain results for all tested proteins   
toptable_summary <- topTable(fit3, coef = "DoxvNorm",number = (nrow(normalizedData)), p.value = 1, adjust.method = "none")
toptable_summary$Protein <- rownames(toptable_summary)
toptable_summary$P.Value %>% hist(breaks = 100)


# PCA of log2-quantile normalized-RUVs values:
prcomp_res <- prcomp(t(normalizedData %>% as.matrix()), center = TRUE)


ggplot2::autoplot(prcomp_res, data = as.data.frame(phenoData_sub), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()


# Volcano plots 
# 1. Create a column to threshold P-values 
toptable_summary <- toptable_summary %>%  mutate(threshold_P = P.Value < 0.05)


# 2. Plot 
ggplot(toptable_summary)+
  geom_point(mapping = aes(x = logFC, y = -log10(P.Value), color = threshold_P))+
  xlab("log2FC")+
  ylab("-log10 nominal p-value")+
  ylim(0, 10)+
  xlim(-7, 7)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()
```


# Linear model + RUVs + Imputation 
```{r MW suggested workflow 22}
# 1. Get non log abundance values 
Protein_DF_Abundance_imp_2 %>% head()




# 2. Generate RUVs related objects (differences_all and set_all)
Meta
genes_all <- rownames(Protein_DF_Abundance_imp_2)
x_all <- c(1,2,3,3,3,4,5,6,6,6)
differences_all <- makeGroups(x_all)


set_all <- newSeqExpressionSet(as.matrix(round(Protein_DF_Abundance_imp_2)),phenoData = data.frame(x_all, row.names=colnames(Protein_DF_Abundance_imp_2)))




# 3. Get RUV weights using all 10 samples
# K=1
set_all_RUV <- RUVSeq::RUVs(set_all, genes_all, k=1, differences_all, isLog = FALSE)
prcomp_res <- prcomp(t(as.matrix(assayData(set_all_RUV)$normalizedCounts)))
ggplot2::autoplot(prcomp_res, data = as.data.frame(Meta), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()

# K =2 
set_all_RUV <- RUVSeq::RUVs(set_all, genes_all, k=2, differences_all, isLog = FALSE)
prcomp_res <- prcomp(t(as.matrix(assayData(set_all_RUV)$normalizedCounts)))
ggplot2::autoplot(prcomp_res, data = as.data.frame(Meta), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()

# K =3 
set_all_RUV <- RUVSeq::RUVs(set_all, genes_all, k=3, differences_all, isLog = FALSE)
prcomp_res <- prcomp(t(as.matrix(assayData(set_all_RUV)$normalizedCounts)))
ggplot2::autoplot(prcomp_res, data = as.data.frame(Meta), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()

# Proceed with K=1
set_all_RUV <- RUVSeq::RUVs(set_all, genes_all, k=1, differences_all, isLog = FALSE)



# 4. Subset counts by the 6 columns of interest, Metadata by 6 rows of interest, RUV weights vector to the 6 values of interest
#  counts need to be integer values and in a numeric matrix 
counts_RUVs <- as.matrix(round(Protein_DF_Abundance_imp_2)) 
counts_RUVs %>% dim()
# Create a DataFrame for the phenoData
phenoData_RUVs <- DataFrame(Meta)
phenoData_RUVs <- phenoData_RUVs[c(1,2,4,6,7,9), ]

counts_RUVs <- counts_RUVs[,c(1,2,4,6,7,9)]

counts_RUVs %>% dim()
phenoData_RUVs %>% dim()


RUV_1 <- set_all_RUV$W_1
phenoData_RUVs$RUV_1 <- RUV_1[c(1,2,4,6,7,9)]


# View changes 
phenoData_RUVs %>% head()
counts_RUVs %>% head()

prcomp_res <- prcomp(t(as.matrix(counts_RUVs)))
ggplot2::autoplot(prcomp_res, data = as.data.frame(phenoData_RUVs), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()


# 5. Take the info from 4 and assign it to a new object
# Counts going into RUVs 
counts_RUV_nolog <- assayData(set_all_RUV)$counts 
counts_RUV_nolog %>% head()
counts_RUV_nolog %>% dim()
counts_RUV_nolog[,1] %>% hist(breaks = 100)
counts_RUV_nolog[,2] %>% hist(breaks = 100)
counts_RUV_nolog[,3] %>% hist(breaks = 100)
counts_RUV_nolog[,4] %>% hist(breaks = 100)
counts_RUV_nolog[,5] %>% hist(breaks = 100)
counts_RUV_nolog[,6] %>% hist(breaks = 100)
counts_RUV_nolog[,7] %>% hist(breaks = 100)
counts_RUV_nolog[,8] %>% hist(breaks = 100)
counts_RUV_nolog[,9] %>% hist(breaks = 100)
counts_RUV_nolog[,10] %>% hist(breaks = 100)




# Counts normalized 
counts_RUV_normalized <- assayData(set_all_RUV)$normalizedCounts
counts_RUV_normalized %>% head()
counts_RUV_normalized %>% dim()
counts_RUV_normalized[,1] %>% hist(breaks = 100)
counts_RUV_normalized[,2] %>% hist(breaks = 100)
counts_RUV_normalized[,3] %>% hist(breaks = 100)
counts_RUV_normalized[,4] %>% hist(breaks = 100)
counts_RUV_normalized[,5] %>% hist(breaks = 100)
counts_RUV_normalized[,6] %>% hist(breaks = 100)
counts_RUV_normalized[,7] %>% hist(breaks = 100)
counts_RUV_normalized[,8] %>% hist(breaks = 100)
counts_RUV_normalized[,9] %>% hist(breaks = 100)
counts_RUV_normalized[,10] %>% hist(breaks = 100)





# Counts normalized from RUVs and log2 transformed
counts_RUV_log2 <- assayData(set_all_RUV)$normalizedCounts %>% log2()
counts_RUV_log2 %>% head()
counts_RUV_log2 %>% dim()
counts_RUV_log2[,1] %>% hist(breaks = 100)
counts_RUV_log2[,2] %>% hist(breaks = 100)
counts_RUV_log2[,3] %>% hist(breaks = 100)
counts_RUV_log2[,4] %>% hist(breaks = 100)
counts_RUV_log2[,5] %>% hist(breaks = 100)
counts_RUV_log2[,6] %>% hist(breaks = 100)
counts_RUV_log2[,7] %>% hist(breaks = 100)
counts_RUV_log2[,8] %>% hist(breaks = 100)
counts_RUV_log2[,9] %>% hist(breaks = 100)
counts_RUV_log2[,10] %>% hist(breaks = 100)


# Counts normalized from RUVs and log2 transformed looking at the subsetted samples for linear modelling 
counts_RUV_log2_sub <- counts_RUV_log2[,c(1,2,4,6,7,9)]
counts_RUV_log2_sub %>% head()
counts_RUV_log2_sub %>% dim()
counts_RUV_log2_sub[,1] %>% hist(breaks = 100)
counts_RUV_log2_sub[,2] %>% hist(breaks = 100)
counts_RUV_log2_sub[,3] %>% hist(breaks = 100)
counts_RUV_log2_sub[,4] %>% hist(breaks = 100)
counts_RUV_log2_sub[,5] %>% hist(breaks = 100)
counts_RUV_log2_sub[,6] %>% hist(breaks = 100)



# Quantile normalization on the samples being used for linear modelling 
counts_RUV_log2_sub_quantnorm <- limma::normalizeBetweenArrays(counts_RUV_log2_sub, method = "quantile")
counts_RUV_log2_sub_quantnorm %>% head()
counts_RUV_log2_sub_quantnorm %>% dim()
counts_RUV_log2_sub_quantnorm[,1] %>% hist(breaks = 100)
counts_RUV_log2_sub_quantnorm[,2] %>% hist(breaks = 100)
counts_RUV_log2_sub_quantnorm[,3] %>% hist(breaks = 100)
counts_RUV_log2_sub_quantnorm[,4] %>% hist(breaks = 100)
counts_RUV_log2_sub_quantnorm[,5] %>% hist(breaks = 100)
counts_RUV_log2_sub_quantnorm[,6] %>% hist(breaks = 100)




# Create Design Matrix 
# phenoData$Cond <- factor(phenoData$Cond , levels = c("Control", "Dox"))
design <- model.matrix(~ 0 + Cond + RUV_1, data = phenoData_RUVs)
design


# rename columns 
colnames(design) <- c('Control', "Dox", "RUV_1")


# Get model counts 
Model_counts <- counts_RUV_log2_sub_quantnorm


# Fit model
dupcor <- duplicateCorrelation(as.matrix(Model_counts), design, block = phenoData_RUVs$Ind)
fit <- lmFit(object = as.matrix(Model_counts), design = design, block = phenoData_RUVs$Ind, correlation = dupcor$consensus)
fit2 <- eBayes(fit)


# Make contrasts
cm <- makeContrasts(
  DoxvNorm = Dox - Control,
  levels = design)


# Model with contrasts
fit2 <- contrasts.fit(fit, cm)
fit2 <- eBayes(fit2)


# Summarize
results_summary <- decideTests(fit2, adjust.method = "none", p.value = 0.05)
summary(results_summary)


# Toptable summary organized to contain results for all tested proteins   
toptable_summary <- topTable(fit2, coef = "DoxvNorm",number = (nrow(Model_counts)), p.value = 1, adjust.method = "none")
toptable_summary$Protein <- rownames(toptable_summary)
toptable_summary$P.Value %>% hist(breaks = 100)




# Volcano plots 
# 1. Create a column to threshold P-values 
toptable_summary <- toptable_summary %>%  mutate(threshold_P = P.Value < 0.05)


# 2. Plot 
ggplot(toptable_summary)+
  geom_point(mapping = aes(x = logFC, y = -log10(P.Value), color = threshold_P))+
  xlab("log2FC")+
  ylab("-log10 nominal p-value")+
  ylim(0, 6)+
  xlim(-7, 7)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()



# Other fits 
fit3 <- eBayes(fit2, robust = TRUE) # Trend = TRUE does not work 


# Summarize
results_summary <- decideTests(fit3, adjust.method = "none", p.value = 0.05)
summary(results_summary)


# Toptable summary organized to contain results for all tested proteins   
toptable_summary <- topTable(fit3, coef = "DoxvNorm",number = (nrow(normalizedData)), p.value = 1, adjust.method = "none")
toptable_summary$Protein <- rownames(toptable_summary)
toptable_summary$P.Value %>% hist(breaks = 100)


# PCA of log2-quantile normalized-RUVs values:
prcomp_res <- prcomp(t(normalizedData %>% as.matrix()), center = TRUE)


ggplot2::autoplot(prcomp_res, data = as.data.frame(phenoData_sub), colour = "Cond", shape = "Ind", size =4)+
  theme_bw()


# Volcano plots 
# 1. Create a column to threshold P-values 
toptable_summary <- toptable_summary %>%  mutate(threshold_P = P.Value < 0.05)


# 2. Plot 
ggplot(toptable_summary)+
  geom_point(mapping = aes(x = logFC, y = -log10(P.Value), color = threshold_P))+
  xlab("log2FC")+
  ylab("-log10 nominal p-value")+
  ylim(0, 6)+
  xlim(-7, 7)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()
```

