#### Title #### 

# Proteomic wrangle 
#### REQUIRED Libraries ####
```{r}
library(EDASeq)
library(RUVSeq)
library(RColorBrewer)
library(edgeR)
library(limma)
library(Biobase)
library(SummarizedExperiment)
library(tidyverse) 
library(ggfortify)
library(cluster)
library(edgeR)
library(limma)
library(biomaRt)
library(Homo.sapiens)
library(BiocParallel)
library(qvalue)
library(pheatmap)
library(clusterProfiler)
library(AnnotationDbi)
library(org.Hs.eg.db)
library(RColorBrewer)
library(DOSE)
library(UpSetR)
library(ggvenn)
```
#### Read in Data #### 
# Load your data
```{r}
Protein_DF <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/Abundance.csv", header = TRUE)

Meta <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/Meta.csv", header = TRUE)
```
#### Wrangle Data Frame #### 
# Save the original 
```{r}
Full_DF <- Protein_DF 
```
# Subset the columns referring to abundance
```{r}
Protein_DF_Abundance <- Protein_DF[,c(4, 5:ncol(Protein_DF))] 
```
# Check for duplicated rows 
# Identify duplicated values
```{r}
Protein_DF_Abundance$duplicated_name <- duplicated(Protein_DF_Abundance$Accession)
```
# This will return a logical vector where TRUE indicates the position of duplicates in the column.
# To see only rows with duplicated values, you can subset the dataframe like this:
```{r}
duplicated_rows <- Protein_DF_Abundance[Protein_DF_Abundance$duplicated_name == TRUE, ]
print(duplicated_rows)
```
# We have 3 rows with duplicates, two of which have NA values. We will remove them now since we will go ahead 
# and remove the duplicated rows later on anyways. 
```{r}
Protein_DF_Abundance <- Protein_DF_Abundance[- c(61, 276, 997), ] 
```
# Make rownames of the data frame accession IDs
```{r}
rownames(Protein_DF_Abundance) <- Protein_DF_Abundance$Accession

# Change colnames 
colnames(Protein_DF_Abundance)
Protein_DF_Abundance <- Protein_DF_Abundance[, -c(1, 12)]

# Assuming column names of Protein_DF match with the rows in Meta
rownames(Meta) <- Meta$Samples

colnames(Protein_DF_Abundance) <- Meta$Samples
```

#### Remove rows with at least one NA ####
```{r}
#1.  Find rows with any NA values
rows_with_na <- apply(Protein_DF_Abundance, 1, function(x) any(is.na(x))) %>% which()
rows_with_na 

rows_with_na <- as.numeric(rows_with_na)
rows_with_na

# 2. Remove rows with NA values 
Protein_DF_Abundance <- Protein_DF_Abundance[-rows_with_na, ]

# 3. Sanity check 
Protein_DF_Abundance %>% dim()
```


#### TMM Normalization #### 
```{r}
library(edgeR)

# Create a DGEList from your count data
y <- DGEList(counts = Protein_DF_Abundance)
y$samples

# Assign group to DGEList object
y$samples$group <- Meta$Cond

# Calculate normalization factors using TMM method
y <- calcNormFactors(y, method = "TMM")

# Now the object 'y' has the normalization factors calculated
# If you want to proceed with RUVSeq, you need to use these normalization factors
# when creating the counts matrix that will be input to RUVSeq

norm_counts <- t( t(y$counts) / y$samples$norm.factors )

log2_norm_counts <- log2(norm_counts)
```


#### Prepare Data Object for RUVs #### 
#  counts need to be integer values and in a numeric matrix 
```{r}
counts <- as.matrix(log2_norm_counts) 

# Create a DataFrame for the phenoData
phenoData <- DataFrame(Meta)

# Now create the RangedSummarizedExperiment necessary for RUVs input 
set <- SummarizedExperiment(assays =  counts, metadata =phenoData)
```



#### REQUIRED RUVs Matrix #### 
```{r}
# Generate a background matrix where each set of replicates are in a row
# and null spaces where there are replicate mismatches get the value -1. 
# This will be used in the RUVs function, which is the typeII method to
# remove unwanted variation in the RUVs package. This will be used for all 
# RUVs permutations where the number of variation factors will be changed. 
scIdx <- matrix(-1, nrow = 6, ncol = 3)
scIdx[1, 1:3] <- c(which(colnames(counts) %in% c("S6", "S8", "S10")))
scIdx[2, 1:3] <- c(which(colnames(counts) %in% c("S5", "S7", "S9")))
scIdx[3, 1] <- c(which(colnames(counts) %in% c("S2")))
scIdx[4, 1] <- c(which(colnames(counts) %in% c("S1")))
scIdx[5, 1] <- c(which(colnames(counts) %in% c("S4")))
scIdx[6, 1] <- c(which(colnames(counts) %in% c("S3")))
scIdx
```



#### Dupcor + RUVs K = 1 ####
# Apply RUVs function from RUVSeq 
```{r}
set <- RUVSeq::RUVs(x = counts, k =1, scIdx = scIdx, isLog = TRUE)
RUV_1 <- set$W[,1]



set$W
phenoData$RUV_1 <- RUV_1


# apply duplicateCorrelation is two rounds
design <- model.matrix(~ Cond + RUV_1, phenoData)

vobj_tmp = voom(counts, design, plot = TRUE)
dupcor <- duplicateCorrelation(counts , design, block = Meta$Ind)


# run voom considering the duplicateCorrelation results
# in order to compute more accurate precision weights
# Otherwise, use the results from the first voom run
vobj = voom( counts = counts, design = design, plot=TRUE, block=Meta$Ind, correlation=dupcor$consensus)

# Estimate linear mixed model with a single variance component
# Fit the model for each gene, 
dupcor <- duplicateCorrelation(vobj, design, block=Meta$Ind)

# But this step uses only the genome-wide average for the random effect
fitDupCor <- lmFit(counts, design, block=Meta$Ind, correlation=dupcor$consensus)

# Fit Empirical Bayes for moderated t-statistics
fitDupCor_2 <- eBayes( fitDupCor )


# Summarize
results_Dupcor <- decideTests(fitDupCor_2)
summary(results_Dupcor)

# Toptable summary for more comprehensive results  
toptable_Dupcor <- topTable(fitDupCor_2, coef = "CondDox", number = nrow(Protein_DF_Abundance), p.value = 1)
toptable_Dupcor$Protein <- rownames(toptable_Dupcor)
toptable_Dupcor
```

#### Q-Values #### 
```{r}
qobj <- qvalue(toptable_Dupcor$P.Value)
adj_q_values <- qobj$qvalues

toptable_Dupcor$adj_q_values <- adj_q_values
toptable_Dupcor

sum(toptable_Dupcor$adj_q_values < 0.05 & toptable_Dupcor$logFC > 0 )
sum(toptable_Dupcor$adj_q_values < 0.05 & toptable_Dupcor$logFC < 0 )

toptable_Dupcor %>% head()
```
#### PCA #### 
```{r}
vobj$weights 

bleh <- (vobj$E* sqrt(vobj$weights)) %>% sqrt()

Meta

# Before correction: 
prcomp_res <- prcomp(t(vobj$E), scale. = TRUE, center = TRUE, )

ggplot2::autoplot(prcomp_res, data = Meta, colour = "Cond", shape = "Ind", size =4)+
  theme_bw()


# After correction: 
prcomp_res <- prcomp(t(bleh), scale. = TRUE, center = TRUE)

ggplot2::autoplot(prcomp_res, data = Meta, colour = "Cond", shape = "Ind", size =4)+
  theme_bw()
```


#### Heatmaps #### 
# Before correction with weights 
```{r}
hypothetical_1 <- vobj$E
colnames(hypothetical_1) <- Meta$Cond_Ind


# Use paste to combine the vectors
colnames(hypothetical_1) <- Meta$Cond_Ind
pheatmap::pheatmap(hypothetical_1,
                   cluster_rows = TRUE, 
                   cluster_cols = TRUE,
                   show_rownames = FALSE,
                   show_colnames = TRUE
)


cor(hypothetical_1) %>% pheatmap(
  cluster_rows = TRUE, 
  cluster_cols = TRUE,
  show_rownames = TRUE,
  show_colnames = TRUE)


# After correction with weights 
hypothetical_2 <- bleh

# Use paste to combine the vectors
colnames(hypothetical_2) <- Meta$Cond_Ind


pheatmap::pheatmap(hypothetical_2,
                   cluster_rows = TRUE, 
                   cluster_cols = TRUE,
                   show_rownames = FALSE,
                   show_colnames = TRUE
)


cor(hypothetical_2) %>% pheatmap(
  cluster_rows = TRUE, 
  cluster_cols = TRUE,
  show_rownames = TRUE,
  show_colnames = TRUE)
```

#### Volcano with adj. P #### 
```{r}
# 1. Create a column to threshold adjusted P-values/q-values 
toptable_Threshold_0.05 <- toptable_Dupcor %>%  mutate(threshold_P = adj.P.Val < 0.05)
toptable_Threshold_0.05

# 2. Do the volcano plot 
ggplot(toptable_Threshold_0.05)+
  geom_point(mapping = aes(x = logFC, y = -log10(adj.P.Val), color = threshold_P))+
  xlab("log2FC")+
  ylab("-log10 adjusted p-value")+
  ylim(0, 5)+
  xlim(-5, 5)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()
```


#### Volcano with adj. Q #### 
```{r}
# 1. Create a column to threshold adjusted P-values/q-values 
toptable_Threshold_0.05 <- toptable_Dupcor %>%  mutate(threshold_Q = adj_q_values < 0.05)
toptable_Threshold_0.05

# 2. Do the volcano plot 
ggplot(toptable_Threshold_0.05)+
  geom_point(mapping = aes(x = logFC, y = -log10(adj_q_values), color = threshold_Q))+
  xlab("log2FC")+
  ylab("-log10 adjusted q-value")+
  ylim(0, 5)+
  xlim(-5, 5)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()
```

#### Histogram #### 
```{r}
hist(toptable_Dupcor$adj.P.Val, breaks = 10)

hist(toptable_Dupcor$adj_q_values, breaks = 10)
```



#### Enrichment Test Wrangle P-adj values #### 
```{r}
# 1. Read in the comprehensive DF that contains all sample info
Full_DF %>% head()



# 2.
# Get set of DE proteins as per BH adjusted P-value 
DE_proteins_Padj <- toptable_Threshold_0.05 %>%
  filter(adj.P.Val < 0.05) %>% rownames()

# Get SYMBOL ID for the proteins in DE_proteins_Padj
# Find the rows where 'var' is in 'values'
rows <- which(Full_DF$Accession %in% DE_proteins_Padj)

# Subset the data frame
subset_Full_data <- Full_DF[rows, ]

# Here are the SYMBOL IDs for the DE proteins as per BH adj P value < 0.05
DE_SYMBOL_Padj <- subset_Full_data$Gene.Symbol %>% unique() %>% na.omit()

DE_SYMBOL_Padj



# Get background Symbol IDs 
All_proteins_tested <- toptable_Threshold_0.05 %>%
  filter(adj.P.Val < 1) %>% rownames()

# Get SYMBOL ID for the proteins in DE_proteins_Padj
# Find the rows where 'var' is in 'values'
rows <- which(Full_DF$Accession %in% All_proteins_tested)

# Subset the data frame
subset_back_data <- Full_DF[rows, ]
Background_SYMBOL <- subset_back_data$Gene.Symbol %>% unique() %>% na.omit() 
Background_SYMBOL
```




#### Enrichment Test Wrangle qvalues #### 
```{r}
# 1. Read in the comprehensive DF that contains all sample info
Full_DF %>% head()



# 2.
# Get set of DE proteins as per BH adjusted P-value 
DE_proteins_qval <- toptable_Threshold_0.05 %>%
  filter(adj_q_values < 0.05) %>% rownames()

# Get SYMBOL ID for the proteins in DE_proteins_Padj
# Find the rows where 'var' is in 'values'
rows <- which(Full_DF$Accession %in% DE_proteins_qval)

# Subset the data frame
subset_Full_data <- Full_DF[rows, ]

# Here are the SYMBOL IDs for the DE proteins as per BH adj P value < 0.05
DE_SYMBOL_qval <- subset_Full_data$Gene.Symbol %>% unique() %>% na.omit()

DE_SYMBOL_qval



# Get background Symbol IDs 
All_proteins_tested <- toptable_Threshold_0.05 %>%
  filter(adj_q_values < 1) %>% rownames()

# Get SYMBOL ID for the proteins in DE_proteins_Padj
# Find the rows where 'var' is in 'values'
rows <- which(Full_DF$Accession %in% All_proteins_tested)

# Subset the data frame
subset_back_data <- Full_DF[rows, ]
Background_SYMBOL <- subset_back_data$Gene.Symbol %>% unique() %>% na.omit() 
Background_SYMBOL
```




#### GO Enrichment BP - DE_Pval #### 
```{r}
# 1.
# Do enrichment analysis of ENTREZ IDs from Padjusted value 
# Perform GO enrichment analysis using the enrichGO function. We are using stringent cutoffs for Pvalue and q value in the testing! (this is good)
go_enrichment <- enrichGO(gene = DE_SYMBOL_Padj,
                          OrgDb = org.Hs.eg.db,
                          keyType = "SYMBOL",
                          universe = Background_SYMBOL,
                          ont = "BP",
                          pvalueCutoff = 0.05,
                          qvalueCutoff = 0.05)

go_enrichment

# Go plot 
goplot(x = go_enrichment, showCategory = 30)


# summary of the result that most people use 
plot(barplot(go_enrichment, showCategory = 20))


# View the top enriched GO terms as a tibble 
GO_Tibble <- go_enrichment %>% as_tibble()
GO_Tibble



# Arrange by adjusted p value 
GO_Tibble <- GO_Tibble %>%
  arrange(desc(p.adjust))

# Factor by P.adjusted value 
GO_Tibble$Description <- factor(GO_Tibble$Description, levels = GO_Tibble$Description[order(GO_Tibble$p.adjust)])

# Get P value for consistent gradient fill
Gradient_value <- GO_Tibble$qvalue %>% median()

# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biologcal Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,75))
```





```{r}
GO_Tibble$negplog <- -log(GO_Tibble$p.adjust) 
# Break up into high, medium and low siignfigance groups

# 1. High 
# Create a sample data frame
GO_Tibble_Upper <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 67
upper_percentile <- 100

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_Upper <- GO_Tibble_Upper[GO_Tibble_Upper$negplog >= lower_value & GO_Tibble_Upper$negplog <= upper_value, ]



# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_Upper, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biological Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0, 70))
```


# 2. Med 
```{r}
# Create a sample data frame
GO_Tibble_Mid <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 33
upper_percentile <- 67

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_Mid <- GO_Tibble_Mid[GO_Tibble_Mid$negplog >= lower_value & GO_Tibble_Mid$negplog <= upper_value, ]




# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_Mid, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biological Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,10))
```




# 3. Low 
```{r}
# Create a sample data frame
GO_Tibble_low <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 1
upper_percentile <- 33

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_low <- GO_Tibble_low[GO_Tibble_low$negplog >= lower_value & GO_Tibble_low$negplog <= upper_value, ]
GO_Tibble_low




# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_low, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biological Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,5))
```

```{r}
#* the input for these plots will be one of the following variables 
#* that we obtained in previous sections of the code, such as 1. go_enrichment, 
#* 2. EnrichPathobj, or 3. enrichdiseaseobj.  
#* 
cnetplot(x = go_enrichment, showCategory = 10, categorySize = "pvalue" )



# heatplot to see gene overlaps 
heatplot(go_enrichment, showCategory = 20)



# Enrichmap by emapplot

library(enrichplot)
edo <- pairwise_termsim(go_enrichment)
edo
p1 <- emapplot(edo, showCategory = 30, nCluster = 3)
p1

p2 <- emapplot(edo, cex_category=1.5)
p2

p3 <- emapplot(edo, layout="kk")
p3

p4 <- emapplot(edo, cex_category=1.5,layout="kk") 
p4
```



#### GO Enrichment MF - DE_Pval #### 
```{r}
go_enrichment <- enrichGO(gene = DE_SYMBOL_Padj,
                          OrgDb = org.Hs.eg.db,
                          keyType = "SYMBOL",
                          universe = Background_SYMBOL,
                          ont = "MF",
                          pvalueCutoff = 0.05,
                          qvalueCutoff = 0.05)

go_enrichment

goplot(go_enrichment, showCategory = 15)


# summary of the result that most people use 
plot(barplot(go_enrichment, showCategory = 30 ))

# View the top enriched GO terms as a tibble 
GO_Tibble <- go_enrichment %>% as_tibble()
GO_Tibble



# Arrange by adjusted p value 
GO_Tibble <- GO_Tibble %>%
  arrange(desc(p.adjust))

# Factor by P.adjusted value 
GO_Tibble$Description <- factor(GO_Tibble$Description, levels = GO_Tibble$Description[order(GO_Tibble$p.adjust)])

# Get P value for consistent gradient fill
Gradient_value <- GO_Tibble$qvalue %>% median()

# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Molecular Functions",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,60))






#* the input for these plots will be one of the following variables 
#* that we obtained in previous sections of the code, such as 1. go_enrichment, 
#* 2. EnrichPathobj, or 3. enrichdiseaseobj.  
#* 
cnetplot(x = go_enrichment, showCategory = 5, categorySize = "pvalue" )



# heatplot to see gene overlaps 
heatplot(go_enrichment, showCategory = 20)



# Enrichmap by emapplot

library(enrichplot)
edo <- pairwise_termsim(go_enrichment)
edo
p1 <- emapplot(edo, showCategory = 15, nCluster = 3)
p1

p2 <- emapplot(edo, cex_category=1.5)
p2

p3 <- emapplot(edo, layout="kk")
p3

p4 <- emapplot(edo, cex_category=1.5,layout="kk") 
p4
```



#### GO Enrichment CC - DE_Pval #### 
```{r}
go_enrichment <- enrichGO(gene = DE_SYMBOL_Padj,
                          OrgDb = org.Hs.eg.db,
                          keyType = "SYMBOL",
                          universe = Background_SYMBOL,
                          ont = "CC",
                          pvalueCutoff = 0.05,
                          qvalueCutoff = 0.05)

go_enrichment



# Go plot 
goplot(go_enrichment, showCategory = 25)

# summary of the result that most people use 
plot(barplot(go_enrichment, showCategory = 25))

# View the top enriched GO terms as a tibble 
GO_Tibble <- go_enrichment %>% as_tibble()
GO_Tibble



# Arrange by adjusted p value 
GO_Tibble <- GO_Tibble %>%
  arrange(desc(p.adjust))

# Factor by P.adjusted value 
GO_Tibble$Description <- factor(GO_Tibble$Description, levels = GO_Tibble$Description[order(GO_Tibble$p.adjust)])

# Get P value for consistent gradient fill
Gradient_value <- GO_Tibble$qvalue %>% median()

# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Molecular Functions",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,90))




#* the input for these plots will be one of the following variables 
#* that we obtained in previous sections of the code, such as 1. go_enrichment, 
#* 2. EnrichPathobj, or 3. enrichdiseaseobj.  
#* 
cnetplot(x = go_enrichment, showCategory = 5, categorySize = "pvalue" )



# heatplot to see gene overlaps 
heatplot(go_enrichment, showCategory = 20)



# Enrichmap by emapplot

library(enrichplot)
edo <- pairwise_termsim(go_enrichment)
edo
p1 <- emapplot(edo, showCategory = 15, nCluster = 3)
p1

p2 <- emapplot(edo, cex_category=1.5)
p2

p3 <- emapplot(edo, layout="kk")
p3

p4 <- emapplot(edo, cex_category=1.5,layout="kk") 
p4
```



#### Enrichment Test Wrangle Downregulated DE genes ####
```{r}
# 1. Read in the comprehensive DF that contains all sample info
Full_DF %>% head()

toptable_Threshold_0.05$logFC

# 2.
# Get set of DE proteins as per BH adjusted P-value 
DE_proteins_Padj <- toptable_Threshold_0.05 %>%
  filter((logFC < 0) & (adj.P.Val < 0.05)) %>% rownames()

# Get SYMBOL ID for the proteins in DE_proteins_Padj
# Find the rows where 'var' is in 'values'
rows <- which(Full_DF$Accession %in% DE_proteins_Padj)

# Subset the data frame
subset_Full_data <- Full_DF[rows, ]

# Here are the SYMBOL IDs for the DE proteins as per BH adj P value < 0.05
DE_SYMBOL_Padj <- subset_Full_data$Gene.Symbol %>% unique() %>% na.omit()




# Get background Symbol IDs 
All_proteins_tested <- toptable_Threshold_0.05 %>%
  filter(adj.P.Val < 1) %>% rownames()

# Get SYMBOL ID for the proteins in DE_proteins_Padj
# Find the rows where 'var' is in 'values'
rows <- which(Full_DF$Accession %in% All_proteins_tested)

# Subset the data frame
subset_back_data <- Full_DF[rows, ]
Background_SYMBOL <- subset_back_data$Gene.Symbol %>% unique() %>% na.omit() 
```

#### GO Enrichment BP - Downregulated Genes #### 
```{r}
# 1.
# Do enrichment analysis of ENTREZ IDs from Padjusted value 
# Perform GO enrichment analysis using the enrichGO function. We are using stringent cutoffs for Pvalue and q value in the testing! (this is good)
go_enrichment <- enrichGO(gene = DE_SYMBOL_Padj,
                          OrgDb = org.Hs.eg.db,
                          keyType = "SYMBOL",
                          universe = Background_SYMBOL,
                          ont = "BP",
                          pvalueCutoff = 0.05,
                          qvalueCutoff = 0.05)

go_enrichment


# Go plot 
goplot(x = go_enrichment, showCategory = 20)


# summary of the result that most people use 
plot(barplot(go_enrichment, showCategory = 20))


# View the top enriched GO terms as a tibble 
GO_Tibble <- go_enrichment %>% as_tibble()
GO_Tibble



# Arrange by adjusted p value 
GO_Tibble <- GO_Tibble %>%
  arrange(desc(p.adjust))

# Factor by P.adjusted value 
GO_Tibble$Description <- factor(GO_Tibble$Description, levels = GO_Tibble$Description[order(GO_Tibble$p.adjust)])

# Get P value for consistent gradient fill
Gradient_value <- GO_Tibble$qvalue %>% median()

# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biologcal Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,100))
```



```{r}
GO_Tibble$negplog <- -log(GO_Tibble$p.adjust) 
# Break up into high, medium and low siignfigance groups

# 1. High 
# Create a sample data frame
GO_Tibble_Upper <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 67
upper_percentile <- 100

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_Upper <- GO_Tibble_Upper[GO_Tibble_Upper$negplog >= lower_value & GO_Tibble_Upper$negplog <= upper_value, ]



# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_Upper, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biological Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0, 90))



# 2. Med 
# Create a sample data frame
GO_Tibble_Mid <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 33
upper_percentile <- 67

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_Mid <- GO_Tibble_Mid[GO_Tibble_Mid$negplog >= lower_value & GO_Tibble_Mid$negplog <= upper_value, ]




# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_Mid, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biological Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,10))





# 3. Low 
# Create a sample data frame
GO_Tibble_low <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 1
upper_percentile <- 33

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_low <- GO_Tibble_low[GO_Tibble_low$negplog >= lower_value & GO_Tibble_low$negplog <= upper_value, ]
GO_Tibble_low




# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_low, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biological Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,5))



#* the input for these plots will be one of the following variables 
#* that we obtained in previous sections of the code, such as 1. go_enrichment, 
#* 2. EnrichPathobj, or 3. enrichdiseaseobj.  
#* 
cnetplot(x = go_enrichment, showCategory = 5, categorySize = "pvalue" )



# heatplot to see gene overlaps 
heatplot(go_enrichment, showCategory = 20)



# Enrichmap by emapplot

library(enrichplot)
edo <- pairwise_termsim(go_enrichment)
edo

p1 <- emapplot(edo, showCategory = 20, nCluster = 5)
p1

p2 <- emapplot(edo, cex_category=1.5)
p2

p3 <- emapplot(edo, layout="kk")
p3

p4 <- emapplot(edo, cex_category=1.5,layout="kk") 
p4

```


#### GO CC Downregulated proteins #### 
```{r}
# 1.
# Do enrichment analysis of ENTREZ IDs from Padjusted value 
# Perform GO enrichment analysis using the enrichGO function. We are using stringent cutoffs for Pvalue and q value in the testing! (this is good)
go_enrichment <- enrichGO(gene = DE_SYMBOL_Padj,
                          OrgDb = org.Hs.eg.db,
                          keyType = "SYMBOL",
                          universe = Background_SYMBOL,
                          ont = "CC",
                          pvalueCutoff = 0.05,
                          qvalueCutoff = 0.05)

go_enrichment


# Go plot 
goplot(x = go_enrichment, showCategory = 20)


# summary of the result that most people use 
plot(barplot(go_enrichment, showCategory = 20))


# View the top enriched GO terms as a tibble 
GO_Tibble <- go_enrichment %>% as_tibble()
GO_Tibble



# Arrange by adjusted p value 
GO_Tibble <- GO_Tibble %>%
  arrange(desc(p.adjust))

# Factor by P.adjusted value 
GO_Tibble$Description <- factor(GO_Tibble$Description, levels = GO_Tibble$Description[order(GO_Tibble$p.adjust)])

# Get P value for consistent gradient fill
Gradient_value <- GO_Tibble$qvalue %>% median()

# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biologcal Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,100))
```





```{r}
GO_Tibble$negplog <- -log(GO_Tibble$p.adjust) 
# Break up into high, medium and low siignfigance groups

# 1. High 
# Create a sample data frame
GO_Tibble_Upper <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 67
upper_percentile <- 100

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_Upper <- GO_Tibble_Upper[GO_Tibble_Upper$negplog >= lower_value & GO_Tibble_Upper$negplog <= upper_value, ]



# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_Upper, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biological Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0, 70))



# 2. Med 
# Create a sample data frame
GO_Tibble_Mid <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 33
upper_percentile <- 67

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_Mid <- GO_Tibble_Mid[GO_Tibble_Mid$negplog >= lower_value & GO_Tibble_Mid$negplog <= upper_value, ]




# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_Mid, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biological Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,10))





# 3. Low 
# Create a sample data frame
GO_Tibble_low <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 1
upper_percentile <- 33

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_low <- GO_Tibble_low[GO_Tibble_low$negplog >= lower_value & GO_Tibble_low$negplog <= upper_value, ]
GO_Tibble_low




# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_low, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biological Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,5))



#* the input for these plots will be one of the following variables 
#* that we obtained in previous sections of the code, such as 1. go_enrichment, 
#* 2. EnrichPathobj, or 3. enrichdiseaseobj.  
#* 
cnetplot(x = go_enrichment, showCategory = 5, categorySize = "pvalue" )



# heatplot to see gene overlaps 
heatplot(go_enrichment, showCategory = 20)



# Enrichmap by emapplot

library(enrichplot)
edo <- pairwise_termsim(go_enrichment)
edo
p1 <- emapplot(edo, showCategory = 20, nCluster = 3)
p1
p2 <- emapplot(edo, cex_category=1.5)
p2
p3 <- emapplot(edo, layout="kk")
p3
p4 <- emapplot(edo, cex_category=1.5,layout="kk") 
p4
cowplot::plot_grid(p1, p2, p3, p4, ncol=2, labels=LETTERS[1:4])
```



#### GO Enrichment MF - Downregulated Genes #### 
```{r}
# 1.
# Do enrichment analysis of ENTREZ IDs from Padjusted value 
# Perform GO enrichment analysis using the enrichGO function. We are using stringent cutoffs for Pvalue and q value in the testing! (this is good)
go_enrichment <- enrichGO(gene = DE_SYMBOL_Padj,
                          OrgDb = org.Hs.eg.db,
                          keyType = "SYMBOL",
                          universe = Background_SYMBOL,
                          ont = "MF",
                          pvalueCutoff = 0.05,
                          qvalueCutoff = 0.05)

go_enrichment


# Go plot 
goplot(x = go_enrichment, showCategory = 20)


# summary of the result that most people use 
plot(barplot(go_enrichment, showCategory = 20))


# View the top enriched GO terms as a tibble 
GO_Tibble <- go_enrichment %>% as_tibble()
GO_Tibble



# Arrange by adjusted p value 
GO_Tibble <- GO_Tibble %>%
  arrange(desc(p.adjust))

# Factor by P.adjusted value 
GO_Tibble$Description <- factor(GO_Tibble$Description, levels = GO_Tibble$Description[order(GO_Tibble$p.adjust)])

# Get P value for consistent gradient fill
Gradient_value <- GO_Tibble$qvalue %>% median()

# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biologcal Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,75))
```





```{r}
GO_Tibble$negplog <- -log(GO_Tibble$p.adjust) 
# Break up into high, medium and low siignfigance groups

# 1. High 
# Create a sample data frame
GO_Tibble_Upper <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 67
upper_percentile <- 100

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_Upper <- GO_Tibble_Upper[GO_Tibble_Upper$negplog >= lower_value & GO_Tibble_Upper$negplog <= upper_value, ]



# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_Upper, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biological Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0, 70))



# 2. Med 
# Create a sample data frame
GO_Tibble_Mid <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 33
upper_percentile <- 67

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_Mid <- GO_Tibble_Mid[GO_Tibble_Mid$negplog >= lower_value & GO_Tibble_Mid$negplog <= upper_value, ]




# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_Mid, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biological Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,10))





# 3. Low 
# Create a sample data frame
GO_Tibble_low <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 1
upper_percentile <- 33

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_low <- GO_Tibble_low[GO_Tibble_low$negplog >= lower_value & GO_Tibble_low$negplog <= upper_value, ]
GO_Tibble_low




# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_low, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Biological Processes",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,5))



#* the input for these plots will be one of the following variables 
#* that we obtained in previous sections of the code, such as 1. go_enrichment, 
#* 2. EnrichPathobj, or 3. enrichdiseaseobj.  
#* 
cnetplot(x = go_enrichment, showCategory = 5, categorySize = "pvalue" )



# heatplot to see gene overlaps 
heatplot(go_enrichment, showCategory = 20)



# Enrichmap by emapplot

library(enrichplot)
edo <- pairwise_termsim(go_enrichment)
edo

p1 <- emapplot(edo, showCategory = 20, nCluster = 3)
p1
p2 <- emapplot(edo, cex_category=1.5)
p2
p3 <- emapplot(edo, layout="kk")
p3
p4 <- emapplot(edo, cex_category=1.5,layout="kk") 
p4
cowplot::plot_grid(p1, p2, p3, p4, ncol=2, labels=LETTERS[1:4])
```

#### Enrich Pathway through reactome ENTREZ - DE_Pval #### 
```{r}
# Wrangle ENTREZ IDs for Pval 
# 1. Read in the comprehensive DF that contains all sample info
Full_DF %>% head()



# 2.
# Get set of DE proteins as per BH adjusted P-value 
DE_ENTREZ_Padj <- toptable_Threshold_0.05 %>%
  filter(adj.P.Val < 0.05) %>% rownames()

# Get SYMBOL ID for the proteins in DE_proteins_Padj
# Find the rows where 'var' is in 'values'
rows <- which(Full_DF$Accession %in% DE_ENTREZ_Padj)


# Subset the data frame
subset_Full_data <- Full_DF[rows, ]

# Here are the SYMBOL IDs for the DE proteins as per BH adj P value < 0.05
DE_ENTREZ_Padj <- subset_Full_data$Entrez.Gene.ID %>% unique() %>% na.omit()

DE_ENTREZ_Padj



# Get background Symbol IDs 
All_proteins_tested <- toptable_Threshold_0.05 %>%
  filter(adj.P.Val < 1) %>% rownames()

# Get SYMBOL ID for the proteins in DE_proteins_Padj
# Find the rows where 'var' is in 'values'
rows <- which(Full_DF$Accession %in% All_proteins_tested)

# Subset the data frame
subset_back_data <- Full_DF[rows, ]
Background_ENTREZ <- subset_back_data$Entrez.Gene.ID %>% unique() %>% na.omit() 
Background_ENTREZ




# Fusion proteins in ENTREZ ids. Therefore, need to split them up 
# vector to split 
my_vector_test <- DE_ENTREZ_Padj


# Split the elements of the vector on semicolons
split_vector <- strsplit(my_vector_test, split = ";")

# Unlist the split vector
new_vector_ENTREZ <- unlist(split_vector)





# Do the same for background 
back_vector_test <- Background_ENTREZ

# Split the elements of the vector on semicolons
split_vector <- strsplit(back_vector_test, split = ";")

# Unlist the split vector
back_new_vector_ENTREZ <- unlist(split_vector)





EnrichPathobj <- ReactomePA::enrichPathway(
  new_vector_ENTREZ,
  organism = "human",
  pvalueCutoff = 0.05,
  pAdjustMethod = "BH",
  qvalueCutoff = 0.05,
  universe = back_new_vector_ENTREZ,
  minGSSize = 2,
  maxGSSize = 500,
  readable = FALSE
)


EnrichPathobj

# summary of the result that most people use 
plot(barplot(EnrichPathobj, showCategory = 15 ))

# View the top enriched GO terms as a tibble 
GO_Tibble <- EnrichPathobj %>% as_tibble()
GO_Tibble

write_csv(x = GO_Tibble, file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/Important_DF_Final/Reactome_Tibble.csv")

# Arrange by adjusted p value 
GO_Tibble <- GO_Tibble %>%
  arrange(desc(p.adjust))

# Factor by P.adjusted value 
GO_Tibble$Description <- factor(GO_Tibble$Description, levels = GO_Tibble$Description[order(GO_Tibble$p.adjust)])

# Get P value for consistent gradient fill
Gradient_value <- GO_Tibble$qvalue %>% median()

# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Molecular Functions",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,105))
```



```{r}
GO_Tibble$negplog <- -log(GO_Tibble$p.adjust) 
# Break up into high, medium and low siignfigance groups

# 1. High 
# Create a sample data frame
GO_Tibble_Upper <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 67
upper_percentile <- 100

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_Upper <- GO_Tibble_Upper[GO_Tibble_Upper$negplog >= lower_value & GO_Tibble_Upper$negplog <= upper_value, ]



# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_Upper, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Molecular Functions",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,130))



# 2. Med 
# Create a sample data frame
GO_Tibble_Mid <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 33
upper_percentile <- 67

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_Mid <- GO_Tibble_Mid[GO_Tibble_Mid$negplog >= lower_value & GO_Tibble_Mid$negplog <= upper_value, ]




# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_Mid, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Molecular Functions",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,100))





# 3. Low 
# Create a sample data frame
GO_Tibble_low <- GO_Tibble

# Define the lower and upper percentile values
lower_percentile <- 1
upper_percentile <- 33

# Calculate the percentile values for the 'Value' column
lower_value <- quantile(GO_Tibble$negplog, probs = lower_percentile / 100)
upper_value <- quantile(GO_Tibble$negplog, probs = upper_percentile / 100)

# Subset the data frame based on the percentile range
GO_Tibble_low <- GO_Tibble_low[GO_Tibble_low$negplog >= lower_value & GO_Tibble_low$negplog <= upper_value, ]
GO_Tibble_low




# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble_low, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Molecular Functions",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,35))






#* the input for these plots will be one of the following variables 
#* that we obtained in previous sections of the code, such as 1. go_enrichment, 
#* 2. EnrichPathobj, or 3. enrichdiseaseobj.  
#* 
cnetplot(x = EnrichPathobj, showCategory = 5, categorySize = "pvalue" )



# heatplot to see gene overlaps 
heatplot(EnrichPathobj, showCategory = 20)



# Enrichmap by emapplot

library(enrichplot)
edo <- pairwise_termsim(EnrichPathobj)
edo
p1 <- emapplot(edo, showCategory = 15, nCluster = 3)
p1
p2 <- emapplot(edo, cex_category=1.5)
p2
p3 <- emapplot(edo, layout="kk")
p3
p4 <- emapplot(edo, cex_category=1.5,layout="kk") 
p4
cowplot::plot_grid(p1, p2, p3, p4, ncol=2, labels=LETTERS[1:4])
```






#### Enrich Pathway through reactome downregulated DE ENTREZ - DE_Pval #### 
```{r}
# Wrangle ENTREZ IDs for Pval 
# 1. Read in the comprehensive DF that contains all sample info
Full_DF %>% head()


# 2.
# Get set of DE proteins as per BH adjusted P-value 
DE_ENTREZ_Padj <- toptable_Threshold_0.05 %>%
  filter((logFC < 0 )&(adj.P.Val < 0.05)) %>% rownames()

# Get SYMBOL ID for the proteins in DE_proteins_Padj
# Find the rows where 'var' is in 'values'
rows <- which(Full_DF$Accession %in% DE_ENTREZ_Padj)


# Subset the data frame
subset_Full_data <- Full_DF[rows, ]

# Here are the SYMBOL IDs for the DE proteins as per BH adj P value < 0.05
DE_ENTREZ_Padj <- subset_Full_data$Entrez.Gene.ID %>% unique() %>% na.omit()

DE_ENTREZ_Padj



# Get background Symbol IDs 
All_proteins_tested <- toptable_Threshold_0.05 %>%
  filter(adj.P.Val < 1) %>% rownames()

# Get SYMBOL ID for the proteins in DE_proteins_Padj
# Find the rows where 'var' is in 'values'
rows <- which(Full_DF$Accession %in% All_proteins_tested)

# Subset the data frame
subset_back_data <- Full_DF[rows, ]
Background_ENTREZ <- subset_back_data$Entrez.Gene.ID %>% unique() %>% na.omit() 
Background_ENTREZ




# Fusion proteins in ENTREZ ids. Therefore, need to split them up 
# vector to split 
my_vector_test <- DE_ENTREZ_Padj


# Split the elements of the vector on semicolons
split_vector <- strsplit(my_vector_test, split = ";")

# Unlist the split vector
new_vector_ENTREZ <- unlist(split_vector)





# Do the same for background 
back_vector_test <- Background_ENTREZ

# Split the elements of the vector on semicolons
split_vector <- strsplit(back_vector_test, split = ";")

# Unlist the split vector
back_new_vector_ENTREZ <- unlist(split_vector)

new_vector_ENTREZ %>% length()



EnrichPathobj <- ReactomePA::enrichPathway(
  new_vector_ENTREZ,
  organism = "human",
  pvalueCutoff = 0.05,
  pAdjustMethod = "BH",
  qvalueCutoff = 0.05,
  universe = back_new_vector_ENTREZ,
  minGSSize = 2,
  maxGSSize = 500,
  readable = FALSE
)


EnrichPathobj

# summary of the result that most people use 
plot(barplot(EnrichPathobj, showCategory = 20))

# View the top enriched GO terms as a tibble 
GO_Tibble <- EnrichPathobj %>% as_tibble()
GO_Tibble


# Arrange by adjusted p value 
GO_Tibble <- GO_Tibble %>%
  arrange(desc(p.adjust))

# Factor by P.adjusted value 
GO_Tibble$Description <- factor(GO_Tibble$Description, levels = GO_Tibble$Description[order(GO_Tibble$p.adjust)])

# Get P value for consistent gradient fill
Gradient_value <- GO_Tibble$qvalue %>% median()

# Visualize the total enriched GO terms using a vertical bar plot 
ggplot(data = GO_Tibble, aes(x = -log(p.adjust), y = reorder(Description, -log(p.adjust)))) +
  geom_bar(stat = "identity") + 
  geom_bar(stat = "identity", fill = "#4B9CD3")+
  labs(x = "-log(p-adj)",
       y = "Molecular Functions",
       fill = "P.adjusted",
       title = "GO enrichment analysis") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlim(c(0,120))
```
####* - Read in and wrangle RNA-Seq data ####
```{r}
#### RNA-Seq Wrangling ####
# Get data 
RNA_Seq_Top_Table <- read_csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/RNA_Seq/Doxtoplist.csv", col_names = TRUE, row.names(1))
RNA_Seq_Top_Table %>% dim()
# Group the 24hr data together 
RNA_Seq_Top_Table_24hr <- RNA_Seq_Top_Table %>% dplyr::filter(time == "24_hours")
RNA_Seq_Top_Table_24hr 



# Generate q values for the 24hr Dox toptable 
qobj <- qvalue(RNA_Seq_Top_Table_24hr$P.Value)
adj_q_values <- qobj$qvalues

RNA_Seq_Top_Table_24hr$adj_q_values <- adj_q_values
RNA_Seq_Top_Table_24hr

sum(RNA_Seq_Top_Table_24hr$adj_q_values < 0.05 & RNA_Seq_Top_Table_24hr$logFC > 0 )
sum(RNA_Seq_Top_Table_24hr$adj_q_values < 0.05 & RNA_Seq_Top_Table_24hr$logFC < 0 )


# Group the 3hr data together 
RNA_Seq_Top_Table_3hr <- RNA_Seq_Top_Table %>% dplyr::filter(time == "3_hours" )
```


#### 24 hr Plots ####
```{r}
# Basic workflow for visualizing. and interpreting genes for 24 hr timepoint 
RNA_Seq_Top_Table_24hr

# 1. Create a column to threshold adjusted P-values/q-values 
RNA_24hr_Dox_toptable_Threshold_0.05 <- RNA_Seq_Top_Table_24hr %>%  mutate(threshold_P = adj.P.Val < 0.05)


# 2. Do the volcano plot 
ggplot(RNA_24hr_Dox_toptable_Threshold_0.05)+
  geom_point(mapping = aes(x = logFC, y = -log10(adj.P.Val), color = threshold_P ))+
  xlab("log2FC")+
  ylab("-log10 adjusted p-value")+
  ylim(0, 25)+
  xlim(-8, 8)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()
```
#### Volcano plot with labels  #### 
```{r}
ggplot(RNA_24hr_Dox_toptable_Threshold_0.05)+
  geom_point(mapping = aes(x = logFC, y = -log10(adj.P.Val), color = threshold_P))+
  geom_text(mapping = aes(x = logFC, y = -log10(adj.P.Val), label = SYMBOL), 
            hjust = -0.1, vjust = -0.1, check_overlap = TRUE, size = 3)+
  xlab("log2FC")+
  ylab("-log10 adjusted p-value")+
  ylim(0, 30)+
  xlim(-10, 10)+
  theme(legend.position = "none", 
        plot.title = element_text(size = rel(1.5), hjust = 0.5),
        axis.title = element_text(size = rel(1.25)))+
  theme_bw()
```
#### RNA-Seq + proteomic sign test Next to do ####
```{r}
# Use the ensembl dataset
mart <- useMart("ensembl", dataset = "hsapiens_gene_ensembl")

# vector of Uniprot IDs
uniprot_ids <- toptable_Dupcor %>% rownames()

uniprot_ids %>% length()


# Get the corresponding ENTREZ IDs
results_Pro <- getBM(filters = "uniprotswissprot", 
                     attributes = c("uniprotswissprot", "hgnc_symbol"), 
                     values = uniprot_ids, 
                     mart = mart)


# Get the corresponding SYMBOLs
results_RNA <- getBM(filters = "hgnc_symbol", 
                     attributes = c("entrezgene_id","uniprotswissprot", "hgnc_symbol"), 
                     values = RNA_24hr_Dox_toptable_Threshold_0.05$SYMBOL, 
                     mart = mart)




# Simplify Proteomic DF 
Pro_DF <- data.frame( uniprotswissprot = rownames(toptable_Dupcor), Pro_LogFC = toptable_Dupcor$logFC, Pro_Pval = toptable_Dupcor$adj.P.Val )


Joined_ProDF_results_Pro <- full_join(Pro_DF, results_Pro, by = "uniprotswissprot")
Joined_ProDF_results_Pro <- Joined_ProDF_results_Pro %>% na.omit()



# Simplify RNA DF 
RNA_DF <- data.frame( hgnc_symbol = RNA_24hr_Dox_toptable_Threshold_0.05$SYMBOL, RNA_LogFC = RNA_24hr_Dox_toptable_Threshold_0.05$logFC, RNA_Pval = RNA_24hr_Dox_toptable_Threshold_0.05$adj.P.Val )
RNA_DF %>% head()

Joined_ProDF_results_Pro_RNA_DF <- full_join(Joined_ProDF_results_Pro, RNA_DF, by = "hgnc_symbol")
Joined_ProDF_results_Pro_RNA_DF_NAomit <- Joined_ProDF_results_Pro_RNA_DF %>% na.omit() 


Results_RNA_DF_Pro_DF_Merged_NAomit <- data.frame(uniprotswissprot = Joined_ProDF_results_Pro_RNA_DF_NAomit$uniprotswissprot, 
                                                  hgnc_symbol =Joined_ProDF_results_Pro_RNA_DF_NAomit$hgnc_symbol , 
                                                  RNA_LogFC = Joined_ProDF_results_Pro_RNA_DF_NAomit$RNA_LogFC, 
                                                  RNA_Pval = Joined_ProDF_results_Pro_RNA_DF_NAomit$RNA_Pval, 
                                                  Pro_LogFC = Joined_ProDF_results_Pro_RNA_DF_NAomit$Pro_LogFC, 
                                                  Pro_Pval =  Joined_ProDF_results_Pro_RNA_DF_NAomit$Pro_Pval)

Results_RNA_DF_Pro_DF_Merged_NAomit %>% head()
```


#### Sign Testing #### 
```{r}
# Add a new column to the data frame indicating whether the signs of Pro_LogFC and RNA_LogFC match
Results_RNA_DF_Pro_DF_Merged_NAomit$sign_match <- sign(Results_RNA_DF_Pro_DF_Merged_NAomit$RNA_LogFC) == sign(Results_RNA_DF_Pro_DF_Merged_NAomit$Pro_LogFC)
Results_RNA_DF_Pro_DF_Merged_NAomit$sign_match
```


```{r}
# Calculate the proportion of matches
proportion_sign_matches <- mean(Results_RNA_DF_Pro_DF_Merged_NAomit$sign_match)
print(proportion_sign_matches)
```


```{r}
# Fit linear model
model_LogFC <- lm(RNA_LogFC ~ Pro_LogFC, data = Results_RNA_DF_Pro_DF_Merged_NAomit)



# Get R-squared
r2 <- summary(model_LogFC)$r.squared
r2



#------ Plot for both same sign and not same sign
ggplot(Results_RNA_DF_Pro_DF_Merged_NAomit, aes(x = Pro_LogFC, y = RNA_LogFC, color = sign_match)) +
  geom_point(size = 2, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black", linetype = "dashed") +
  annotate("text", x = Inf, y = Inf, vjust = 2, hjust = 2,
           label = paste("R^2 = ", round(r2, digits = 2), sep = ""),
           color = "black") +
  scale_color_manual(values = c("red", "blue")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  theme_bw()






#------ Plot for same sign 
SAME_SIGN <- Results_RNA_DF_Pro_DF_Merged_NAomit[Results_RNA_DF_Pro_DF_Merged_NAomit$sign_match == TRUE, ]

# Fit linear model
model_LogFC <- lm(RNA_LogFC ~ Pro_LogFC, data = SAME_SIGN)

nrow(SAME_SIGN)/nrow(Results_RNA_DF_Pro_DF_Merged_NAomit)

# Get R-squared
r2 <- summary(model_LogFC)$r.squared
r2

ggplot(SAME_SIGN, aes(x = Pro_LogFC, y = RNA_LogFC, color = sign_match)) +
  geom_point(size = 2, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black", linetype = "dashed") +
  annotate("text", x = Inf, y = Inf, vjust = 2, hjust = 2,
           label = paste("R^2 = ", round(r2, digits = 2), sep = ""),
           color = "black") +
  scale_color_manual(values = c("red", "blue")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  theme_bw()
```



```{r}
#------ Plot for opposite signs
OPPOSITE_SIGN <- Results_RNA_DF_Pro_DF_Merged_NAomit[Results_RNA_DF_Pro_DF_Merged_NAomit$sign_match == FALSE, ]

# Fit linear model
model_LogFC <- lm(RNA_LogFC ~ Pro_LogFC, data = OPPOSITE_SIGN)



# Get R-squared
r2 <- summary(model_LogFC)$r.squared
r2

ggplot(OPPOSITE_SIGN, aes(x = Pro_LogFC, y = RNA_LogFC, color = sign_match)) +
  geom_point(size = 2, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black", linetype = "dashed") +
  annotate("text", x = Inf, y = Inf, vjust = 2, hjust = 2,
           label = paste("R^2 = ", round(r2, digits = 2), sep = ""),
           color = "black") +
  scale_color_manual(values = c("red", "blue")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  theme_bw()
```



```{r}
# Plot for Same sign & DE in both cases 
SAME_Sign_DE <- Results_RNA_DF_Pro_DF_Merged_NAomit[(Results_RNA_DF_Pro_DF_Merged_NAomit$sign_match == TRUE),  ]

SAME_Sign_DE_2 <- SAME_Sign_DE[ (SAME_Sign_DE$RNA_Pval < 0.05) & (SAME_Sign_DE$Pro_Pval < 0.05),  ]

# Fit linear model
model_LogFC <- lm(RNA_LogFC ~ Pro_LogFC, data = SAME_Sign_DE_2)



# Get R-squared
r2 <- summary(model_LogFC)$r.squared
r2

ggplot(SAME_Sign_DE_2, aes(x = Pro_LogFC, y = RNA_LogFC, color = sign_match)) +
  geom_point(size = 2, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black", linetype = "dashed") +
  annotate("text", x = Inf, y = Inf, vjust = 2, hjust = 2,
           label = paste("R^2 = ", round(r2, digits = 2), sep = ""),
           color = "black") +
  scale_color_manual(values = c("red", "blue")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  theme_bw()
```



```{r}
# Plot for opposite sign & DE 
SAME_Sign_DE <- Results_RNA_DF_Pro_DF_Merged_NAomit[(Results_RNA_DF_Pro_DF_Merged_NAomit$sign_match == FALSE),  ]

SAME_Sign_DE_2 <- SAME_Sign_DE[ (SAME_Sign_DE$RNA_Pval < 0.05) & (SAME_Sign_DE$Pro_Pval < 0.05),  ]

SAME_Sign_DE_2 %>% dim()
# Fit linear model
model_LogFC <- lm(RNA_LogFC ~ Pro_LogFC, data = SAME_Sign_DE_2)



# Get R-squared
r2 <- summary(model_LogFC)$r.squared
r2

ggplot(SAME_Sign_DE_2, aes(x = Pro_LogFC, y = RNA_LogFC, color = sign_match)) +
  geom_point(size = 2, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black", linetype = "dashed") +
  annotate("text", x = Inf, y = Inf, vjust = 2, hjust = 2,
           label = paste("R^2 = ", round(r2, digits = 2), sep = ""),
           color = "black") +
  scale_color_manual(values = c("red", "blue")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  theme_bw()
```



```{r}
#---------- Plot for DE 
RNA_Pro_DE <- Results_RNA_DF_Pro_DF_Merged_NAomit[(Results_RNA_DF_Pro_DF_Merged_NAomit$RNA_Pval < 0.05) & (Results_RNA_DF_Pro_DF_Merged_NAomit$Pro_Pval < 0.05),  ]




# Fit linear model
model_LogFC <- lm(RNA_LogFC ~ Pro_LogFC, data = RNA_Pro_DE)



# Get R-squared
r2 <- summary(model_LogFC)$r.squared
r2

ggplot(RNA_Pro_DE, aes(x = Pro_LogFC, y = RNA_LogFC, color = sign_match)) +
  geom_point(size = 2, alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black", linetype = "dashed") +
  annotate("text", x = Inf, y = Inf, vjust = 2, hjust = 2,
           label = paste("R^2 = ", round(r2, digits = 2), sep = ""),
           color = "black") +
  scale_color_manual(values = c("red", "blue")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  theme_bw()
```



#### GWAS Enrichment Tests #### 
```{r}
HF_GWAS <- readRDS(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Data_sets/GWAS/HF_geneset.RDS")
CAD_GWAS <- readRDS(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Data_sets/GWAS/CAD_geneset.RDS")
ARR_GWAS <- readRDS(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Data_sets/GWAS/Arr_geneset.RDS")


# Combine data frames into a whole CVD GWAS data set 
CVD_GWAS <- rbind(HF_GWAS, CAD_GWAS, ARR_GWAS)


# Get the unique genes from the CVD_GWAS data set 
CVD_GWAS_Unique <- CVD_GWAS$hgnc_symbol %>% unique() 
```


```{r}
# Prepare:
# A = number of DE things that are in the GWAS list
# B = number of DE things that are not in the GWAS list
# C = number of expressed things that are in the GWAS list but are not DE
# D = number of expressed things that are not in the GWAS list and are not DE
Expressed_protein <- Results_RNA_DF_Pro_DF_Merged_NAomit$hgnc_symbol




CAD_GWAS_Expressed <- intersect(CAD_GWAS$hgnc_symbol, Expressed_protein)
intersect(Expressed_protein,CAD_GWAS_Expressed )
CAD_GWAS_Expressed

ARR_GWAS_Expressed <- intersect(ARR_GWAS$hgnc_symbol,Expressed_protein)
intersect(Expressed_protein,ARR_GWAS_Expressed )

HF_GWAS_Expressed <- intersect(HF_GWAS$hgnc_symbol, Expressed_protein)
intersect(Expressed_protein,HF_GWAS_Expressed )
HF_GWAS_Expressed
```


#### Enrichment Testing #### 
```{r}
####* --- DE protein ####
# Protein coding universe GWAS 
SAME_Sign_DE <- Results_RNA_DF_Pro_DF_Merged_NAomit[(Results_RNA_DF_Pro_DF_Merged_NAomit$Pro_Pval <0.05 ),  ]
SAME_Sign_DE$hgnc_symbol 
HF_GWAS$ensembl_gene_id %>% length()

# HF
#**************************
GWAS_Exp <- intersect(Expressed_protein, HF_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(SAME_Sign_DE$hgnc_symbol, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(SAME_Sign_DE$hgnc_symbol) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(SAME_Sign_DE$hgnc_symbol)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)

# Record the gene list
GWAS_List_3 <- intersect(SAME_Sign_DE$hgnc_symbol, GWAS_Exp)

GWAS_List_3

colnames(mat) <- c("DE", "~DE")
rownames(mat) <- c("GWAS", "~GWAS")
mat


table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("GWAS", "Non-GWAS"),
                                         Protein = c("DE", "Non-DE"))))

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + GWAS", "DE ~ GWAS", "~ DE + GWAS", "~ DE ~ GWAS")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("Contingency Table Stacked Bar Chart") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")

table
```


```{r}
# CAD
#**************************
CAD_GWAS$hgnc_symbol %>% length()
CAD_GWAS_Expressed %>% length()
GWAS_Exp <- intersect(Expressed_protein, CAD_GWAS_Expressed)
intersect(SAME_Sign_DE$hgnc_symbol, GWAS_Exp) %>% length()

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(SAME_Sign_DE$hgnc_symbol, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(SAME_Sign_DE$hgnc_symbol) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(SAME_Sign_DE$hgnc_symbol)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
```


```{r}
# ARR
#**************************
GWAS_Exp <- intersect(Expressed_protein, ARR_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(SAME_Sign_DE$hgnc_symbol, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(SAME_Sign_DE$hgnc_symbol) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(SAME_Sign_DE$hgnc_symbol)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)
```





####* --- DE RNA ####
```{r}
Results_RNA_DF_Pro_DF_Merged_NAomit %>% dim()
# Protein coding universe GWAS 
SAME_Sign_DE <- Results_RNA_DF_Pro_DF_Merged_NAomit[(Results_RNA_DF_Pro_DF_Merged_NAomit$RNA_Pval < 0.05 ),  ]
SAME_Sign_DE$hgnc_symbol
SAME_Sign_DE %>% dim()

# HF
#**************************
GWAS_Exp <- intersect(Expressed_protein, HF_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(SAME_Sign_DE$hgnc_symbol, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(SAME_Sign_DE$hgnc_symbol) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(SAME_Sign_DE$hgnc_symbol)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)
```


```{r}
# CAD
#**************************
GWAS_Exp <- intersect(Expressed_protein, CAD_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(SAME_Sign_DE$hgnc_symbol, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(SAME_Sign_DE$hgnc_symbol) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(SAME_Sign_DE$hgnc_symbol)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)
```


```{r}
# ARR --- Restricted to most DE genes that are protein coding ( Pval < 0.01)
#**************************
GWAS_Exp <- intersect(Expressed_protein, ARR_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(SAME_Sign_DE$hgnc_symbol, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(SAME_Sign_DE$hgnc_symbol) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(SAME_Sign_DE$hgnc_symbol)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)

# Collect enriched genes 
GWAS_List_1 <- intersect(SAME_Sign_DE$hgnc_symbol, GWAS_Exp)
GWAS_List_1



# Plot result 
colnames(mat) <- c("DE", "~DE")
rownames(mat) <- c("GWAS", "~GWAS")
mat


table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("GWAS", "Non-GWAS"),
                                         Protein = c("DE", "Non-DE"))))
table
# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + GWAS", "DE ~ GWAS", "~ DE + GWAS", "~ DE ~ GWAS")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("Contingency Table Stacked Bar Chart") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


####* --- DE-Same-Sign ####
```{r}
# Protein coding universe GWAS 
SAME_Sign_DE <- Results_RNA_DF_Pro_DF_Merged_NAomit[(Results_RNA_DF_Pro_DF_Merged_NAomit$sign_match == TRUE),  ]

SAME_Sign_DE_2 <- SAME_Sign_DE[ (SAME_Sign_DE$RNA_Pval < 0.05) & (SAME_Sign_DE$Pro_Pval < 0.05),  ]


# HF
#**************************
GWAS_Exp <- intersect(Expressed_protein, HF_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(SAME_Sign_DE_2$hgnc_symbol, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(SAME_Sign_DE_2$hgnc_symbol) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(SAME_Sign_DE_2$hgnc_symbol)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)

```


```{r}
# CAD
#**************************
GWAS_Exp <- intersect(Expressed_protein, CAD_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(SAME_Sign_DE_2$hgnc_symbol, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(SAME_Sign_DE_2$hgnc_symbol) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(SAME_Sign_DE_2$hgnc_symbol)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)
```


```{r}
# ARR --- Restricted to most DE genes that are protein coding ( Pval < 0.01)
#**************************
GWAS_Exp <- intersect(Expressed_protein, ARR_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(SAME_Sign_DE_2$hgnc_symbol, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(SAME_Sign_DE_2$hgnc_symbol) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(SAME_Sign_DE_2$hgnc_symbol)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)
```




####* --- DE-Opposite-Sign ####
```{r}
# Protein coding universe GWAS 
SAME_Sign_DE <- Results_RNA_DF_Pro_DF_Merged_NAomit[(Results_RNA_DF_Pro_DF_Merged_NAomit$sign_match == FALSE),  ]

SAME_Sign_DE_2 <- SAME_Sign_DE[ (SAME_Sign_DE$RNA_Pval < 0.05) & (SAME_Sign_DE$Pro_Pval < 0.05),  ]


# HF
#**************************
GWAS_Exp <- intersect(Expressed_protein, HF_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(SAME_Sign_DE_2$hgnc_symbol, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(SAME_Sign_DE_2$hgnc_symbol) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(SAME_Sign_DE_2$hgnc_symbol)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)
```


```{r}
# CAD
#**************************
GWAS_Exp <- intersect(Expressed_protein, CAD_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(SAME_Sign_DE_2$hgnc_symbol, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(SAME_Sign_DE_2$hgnc_symbol) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(SAME_Sign_DE_2$hgnc_symbol)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)
```


```{r}
# ARR --- Restricted to most DE genes that are protein coding ( Pval < 0.05)
#**************************
GWAS_Exp <- intersect(Expressed_protein, ARR_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(SAME_Sign_DE_2$hgnc_symbol, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(SAME_Sign_DE_2$hgnc_symbol) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(SAME_Sign_DE_2$hgnc_symbol)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



# Record the genes in this set
GWAS_List_2 <- intersect(SAME_Sign_DE_2$hgnc_symbol, GWAS_Exp)
GWAS_List_2


# Plot result 
colnames(mat) <- c("DE", "~DE")
rownames(mat) <- c("GWAS", "~GWAS")
mat


table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("GWAS", "Non-GWAS"),
                                         Protein = c("DE", "Non-DE"))))
table
# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + GWAS", "DE ~ GWAS", "~ DE + GWAS", "~ DE ~ GWAS")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("Contingency Table Stacked Bar Chart") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


####* --- Divergent sets ####

```{r}
# Calculate the deltaLogFC and plot dstribution and define quantile sets 
New_RNA_PRO_DF <- Results_RNA_DF_Pro_DF_Merged_NAomit %>% mutate(delta_logFC = abs(RNA_LogFC - Pro_LogFC))
New_RNA_PRO_DF$delta_logFC %>% hist()
New_RNA_PRO_DF$delta_logFC 

quantile(x = New_RNA_PRO_DF$delta_logFC , 0.95) 
hist(New_RNA_PRO_DF$delta_logFC, breaks = 20)

New_RNA_PRO_DF <- New_RNA_PRO_DF %>% mutate(Upper_quant = New_RNA_PRO_DF$delta_logFC > quantile(x = New_RNA_PRO_DF$delta_logFC , 0.95))
New_RNA_PRO_DF

New_RNA_PRO_DF <- New_RNA_PRO_DF %>% mutate(Lower_quant = New_RNA_PRO_DF$delta_logFC < quantile(x = New_RNA_PRO_DF$delta_logFC , 0.05))
New_RNA_PRO_DF


write_csv(x = New_RNA_PRO_DF, "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/Important_DF_Final/Pro_RNA_Sign_Divergent.csv")

New_RNA_PRO_DF %>% head()
# High Divergent Gene-Proteins HF 
Non_DE_Divergent <- New_RNA_PRO_DF[New_RNA_PRO_DF$Upper_quant == TRUE, ]$hgnc_symbol
Non_DE_Divergent
GWAS_Exp <- intersect(Expressed_protein, HF_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(Non_DE_Divergent, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(Non_DE_Divergent) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(Non_DE_Divergent)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
```


```{r}
# Low Divergent Gene-Proteins HF 
Non_DE_Divergent <- New_RNA_PRO_DF[New_RNA_PRO_DF$Lower_quant == TRUE, ]$hgnc_symbol
Non_DE_Divergent


# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(Non_DE_Divergent, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(Non_DE_Divergent) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(Non_DE_Divergent)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
```





```{r}
# High Divergent Gene-Proteins CAD Upper .95, 0.9
Non_DE_Divergent <- New_RNA_PRO_DF[New_RNA_PRO_DF$Upper_quant == TRUE, ]$hgnc_symbol
Non_DE_Divergent
GWAS_Exp <- intersect(Expressed_protein, CAD_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(Non_DE_Divergent, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(Non_DE_Divergent) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(Non_DE_Divergent)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
```



```{r}
# Low Divergent Gene-Proteins CAD
Non_DE_Divergent <- New_RNA_PRO_DF[New_RNA_PRO_DF$Lower_quant == TRUE, ]$hgnc_symbol
Non_DE_Divergent
GWAS_Exp <- intersect(Expressed_protein, CAD_GWAS_Expressed)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(Non_DE_Divergent, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(Non_DE_Divergent) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(Non_DE_Divergent)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
```






```{r}
# High Divergent Gene-Proteins ARR 
Non_DE_Divergent <- New_RNA_PRO_DF[New_RNA_PRO_DF$Upper_quant == TRUE, ]$hgnc_symbol
Non_DE_Divergent
GWAS_Exp <- intersect(Results_RNA_DF_Pro_DF_Merged_NAomit$hgnc_symbol, ARR_GWAS$hgnc_symbol)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(Non_DE_Divergent, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(Non_DE_Divergent) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(Non_DE_Divergent)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)


GWAS_List_4 <- intersect(Non_DE_Divergent, GWAS_Exp)
GWAS_List_4

# Plot result 
colnames(mat) <- c("DE", "~DE")
rownames(mat) <- c("GWAS", "~GWAS")
mat


table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("GWAS", "Non-GWAS"),
                                         Protein = c("DE", "Non-DE"))))
table
# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("Divergent + GWAS", "Divergent ~ GWAS", "~ Divergent + GWAS", "~ Divergent ~ GWAS")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("Contingency Table Stacked Bar Chart") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```



```{r}
# Low Divergent Gene-Proteins ARR
Non_DE_Divergent <- New_RNA_PRO_DF[New_RNA_PRO_DF$Lower_quant == TRUE, ]$hgnc_symbol
Non_DE_Divergent
GWAS_Exp <- intersect(Results_RNA_DF_Pro_DF_Merged_NAomit$hgnc_symbol, ARR_GWAS$hgnc_symbol)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(Non_DE_Divergent, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(Non_DE_Divergent) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(Non_DE_Divergent)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
```





```{r}
# High Divergent Gene-Proteins ARR DE 
Non_DE_Divergent <- New_RNA_PRO_DF[New_RNA_PRO_DF$Upper_quant == TRUE, ]$hgnc_symbol


GWAS_Exp <- intersect(Results_RNA_DF_Pro_DF_Merged_NAomit$hgnc_symbol, ARR_GWAS$hgnc_symbol)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(Non_DE_Divergent, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(Non_DE_Divergent) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(Non_DE_Divergent)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
```



```{r}
# High Divergent Proteins ARR DE 
Non_DE_Divergent <- New_RNA_PRO_DF[New_RNA_PRO_DF$Upper_quant == TRUE, ]
DE_Divergent <- Non_DE_Divergent[Non_DE_Divergent$Pro_Pval < 0.05, ]$hgnc_symbol

GWAS_Exp <- intersect(Results_RNA_DF_Pro_DF_Merged_NAomit$hgnc_symbol, ARR_GWAS$hgnc_symbol)
GWAS_Exp

# A = number of DE gene/proteins that are in the GWAS list
A <- intersect(DE_Divergent, GWAS_Exp) %>% length()
A

# B = number of DE gene/proteins that are not in the GWAS list
B <- length(DE_Divergent) - A
B
# C = number of expressed gene/proteins that are in the GWAS list but are not DE
C <- length(GWAS_Exp) - A
C
# D = number of expressed gene/proteins that are not in the GWAS list and are not DE
D <- (nrow(Results_RNA_DF_Pro_DF_Merged_NAomit) - length(DE_Divergent)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)

# Record gene set, differentially expressed and divergent. 
GWAS_List_5 <- intersect(DE_Divergent, GWAS_Exp)
GWAS_List_5



# Plot result 
colnames(mat) <- c("DE", "~DE")
rownames(mat) <- c("GWAS", "~GWAS")
mat


table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("GWAS", "Non-GWAS"),
                                         Protein = c("DE", "Non-DE"))))
table
# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("In GWAS", "Not in GWAS", "In GWAS", "Not in GWAS")
df_mat$Group <- c("Divergent", "Divergent", "~ Divergent", "~ Divergent")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("Contingency Table Stacked Bar Chart") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
GWAS_List_1
GWAS_List_2
GWAS_List_3
GWAS_List_4
GWAS_List_5
```

#### Mammalian Stress Granule (MSG) Gene-Protein Sets #### 
```{r}
# Read in data frame curated from (https://msgp.pt/)
MSG <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Data_sets/SG_RBP_AUtoph/MSG.csv", header = TRUE)



# 1. Generate lists of gene-protein pairs with interesting functional genomic properties
#*DE proteins
MSG_DE <- New_RNA_PRO_DF[New_RNA_PRO_DF$Pro_Pval < 0.05, ]

#*DE proteins same sign 
MSG_DE_SAME <- New_RNA_PRO_DF[(New_RNA_PRO_DF$sign_match == TRUE) & (New_RNA_PRO_DF$Pro_Pval < 0.05), ]

#*DE proteins opposite sign 
MSG_DE_OPPOSITE <- New_RNA_PRO_DF[(New_RNA_PRO_DF$sign_match == FALSE) & (New_RNA_PRO_DF$Pro_Pval < 0.05), ]

#*Divergent proteins 
MSG_DIVERGENT <- New_RNA_PRO_DF[ New_RNA_PRO_DF$Upper_quant == TRUE, ]

#*Conserved proteins 
MSG_CONSERVED <- New_RNA_PRO_DF[ New_RNA_PRO_DF$Lower_quant == TRUE, ]

#*DE Divergent
MSG_DE_DIVERGENT <- New_RNA_PRO_DF[(New_RNA_PRO_DF$Upper_quant == TRUE) & (New_RNA_PRO_DF$Pro_Pval < 0.05), ]

#*DE Conserved 
MSG_DE_Conserved <- New_RNA_PRO_DF[(New_RNA_PRO_DF$Lower_quant == TRUE) & (New_RNA_PRO_DF$Pro_Pval < 0.05), ]

#*DE Protein Expressing RNA 
MSG_DE_RNAasprotein <- New_RNA_PRO_DF[(New_RNA_PRO_DF$RNA_Pval < 0.05), ]

#* RNA as 
MSG_DE_RNA <- RNA_Seq_Top_Table_24hr[RNA_Seq_Top_Table_24hr$adj.P.Val < 0.05, ]





# 2. Generate sets from MSG data frame 
#* MSG (All)
MSG

#* RPB
MSG_RPB <- MSG[MSG$RPB == TRUE, ]

#* Autophagy
MSG_Auto <- MSG[MSG$Autophagy == TRUE, ]

#* Heat shock 
MSG_HSP <- MSG[MSG$Heat_shock == TRUE, ]

#* RPB-Autophagy
MSG_RPB_Auto <- MSG[(MSG$RPB == TRUE) & (MSG$Autophagy == TRUE), ]

#* RPB-Heat shock
MSG_RPB_HSP <- MSG[(MSG$RPB == TRUE) & (MSG$Heat_shock == TRUE), ]

#* Autophagy Heat_shock 
MSG_Auto_HSP <- MSG[(MSG$Autophagy == TRUE) & (MSG$Heat_shock == TRUE), ]
```


#### Testing MSG Enrichment ####
####* --------- DE Proteins ####
```{r}
SAME_Sign_DE <- MSG_DE
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot


# 1. MSG (All)
#**************************
MSG_Exp <- intersect(Expressed_protein, MSG$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A

# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("MSG", "Non-MSG"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + MSG", "DE ~ MSG", "~ DE + MSG", "~ DE ~ MSG")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("Contingency Table Stacked Bar Chart") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 2. RNA Binding Proteins RPBs 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_RPB$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("RPB", "Non-RPB"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + RPB", "DE ~ RPB", "~ DE + RPB", "~ DE ~ RPB")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 3. Autophagy proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_Auto$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("Autophagy", "Non-Autophagy"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + Autophagy", "DE ~ Autophagy", "~ DE + Autophagy", "~ DE ~ Autophagy")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 4. Heat Shock Proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_HSP$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("HSP", "Non-HSP"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + HSP", "DE ~ HSP", "~ DE + HSP", "~ DE ~ HSP")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```






####* --------- DE_SAME Proteins ####
```{r}
SAME_Sign_DE <- MSG_DE_SAME
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot


# 1. MSG (All)
#**************************
MSG_Exp <- intersect(Expressed_protein, MSG$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A

# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("MSG", "Non-MSG"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + MSG", "DE ~ MSG", "~ DE + MSG", "~ DE ~ MSG")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("Contingency Table Stacked Bar Chart") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 2. RNA Binding Proteins RPBs 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE_SAME

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_RPB$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("RPB", "Non-RPB"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + RPB", "DE ~ RPB", "~ DE + RPB", "~ DE ~ RPB")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 3. Autophagy proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE_SAME

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_Auto$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("Autophagy", "Non-Autophagy"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + Autophagy", "DE ~ Autophagy", "~ DE + Autophagy", "~ DE ~ Autophagy")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 4. Heat Shock Proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE_SAME

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_HSP$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("HSP", "Non-HSP"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + HSP", "DE ~ HSP", "~ DE + HSP", "~ DE ~ HSP")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


####* --------- DE_OPPOSSITE Proteins ####
```{r}
SAME_Sign_DE <- MSG_DE_OPPOSITE
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot


# 1. MSG (All)
#**************************
MSG_Exp <- intersect(Expressed_protein, MSG$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A

# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("MSG", "Non-MSG"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + MSG", "DE ~ MSG", "~ DE + MSG", "~ DE ~ MSG")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("Contingency Table Stacked Bar Chart") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 2. RNA Binding Proteins RPBs 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE_OPPOSITE

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_RPB$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("RPB", "Non-RPB"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + RPB", "DE ~ RPB", "~ DE + RPB", "~ DE ~ RPB")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 3. Autophagy proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE_OPPOSITE

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_Auto$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("Autophagy", "Non-Autophagy"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + Autophagy", "DE ~ Autophagy", "~ DE + Autophagy", "~ DE ~ Autophagy")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")

```


```{r}
# 4. Heat Shock Proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE_OPPOSITE

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_HSP$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("HSP", "Non-HSP"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + HSP", "DE ~ HSP", "~ DE + HSP", "~ DE ~ HSP")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```



####* --------- Divergent Proteins ####
```{r}
SAME_Sign_DE <- MSG_DIVERGENT
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot


# 1. MSG (All)
#**************************
MSG_Exp <- intersect(Expressed_protein, MSG$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A

# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("MSG", "Non-MSG"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + MSG", "DE ~ MSG", "~ DE + MSG", "~ DE ~ MSG")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("Contingency Table Stacked Bar Chart") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")

```


```{r}
# 2. RNA Binding Proteins RPBs 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DIVERGENT

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_RPB$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("RPB", "Non-RPB"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + RPB", "DE ~ RPB", "~ DE + RPB", "~ DE ~ RPB")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 3. Autophagy proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DIVERGENT

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_Auto$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("Autophagy", "Non-Autophagy"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + Autophagy", "DE ~ Autophagy", "~ DE + Autophagy", "~ DE ~ Autophagy")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 4. Heat Shock Proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DIVERGENT

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_HSP$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("HSP", "Non-HSP"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + HSP", "DE ~ HSP", "~ DE + HSP", "~ DE ~ HSP")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


####* --------- Conserved Proteins ####
```{r}
SAME_Sign_DE <- MSG_CONSERVED
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot


# 1. MSG (All)
#**************************
MSG_Exp <- intersect(Expressed_protein, MSG$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A

# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("MSG", "Non-MSG"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + MSG", "DE ~ MSG", "~ DE + MSG", "~ DE ~ MSG")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("Contingency Table Stacked Bar Chart") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 2. RNA Binding Proteins RPBs 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_CONSERVED

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_RPB$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("RPB", "Non-RPB"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + RPB", "DE ~ RPB", "~ DE + RPB", "~ DE ~ RPB")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 3. Autophagy proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_CONSERVED

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_Auto$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("Autophagy", "Non-Autophagy"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + Autophagy", "DE ~ Autophagy", "~ DE + Autophagy", "~ DE ~ Autophagy")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 4. Heat Shock Proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_CONSERVED

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_HSP$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("HSP", "Non-HSP"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + HSP", "DE ~ HSP", "~ DE + HSP", "~ DE ~ HSP")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


####* --------- DE_Divergent Proteins ####
```{r}
SAME_Sign_DE <- MSG_DE_DIVERGENT
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot


# 1. MSG (All)
#**************************
MSG_Exp <- intersect(Expressed_protein, MSG$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A

# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("MSG", "Non-MSG"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + MSG", "DE ~ MSG", "~ DE + MSG", "~ DE ~ MSG")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("Contingency Table Stacked Bar Chart") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 2. RNA Binding Proteins RPBs 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE_DIVERGENT

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_RPB$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("RPB", "Non-RPB"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + RPB", "DE ~ RPB", "~ DE + RPB", "~ DE ~ RPB")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 3. Autophagy proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE_DIVERGENT

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_Auto$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("Autophagy", "Non-Autophagy"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + Autophagy", "DE ~ Autophagy", "~ DE + Autophagy", "~ DE ~ Autophagy")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 4. Heat Shock Proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE_DIVERGENT

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_HSP$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("HSP", "Non-HSP"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + HSP", "DE ~ HSP", "~ DE + HSP", "~ DE ~ HSP")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```



####* --------- DE_Conserved Proteins ####
```{r}
SAME_Sign_DE <- MSG_CONSERVED[MSG_CONSERVED$Pro_Pval < 0.05, ]
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot


# 1. MSG (All)
#**************************
MSG_Exp <- intersect(Expressed_protein, MSG$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A

# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("MSG", "Non-MSG"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + MSG", "DE ~ MSG", "~ DE + MSG", "~ DE ~ MSG")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("Contingency Table Stacked Bar Chart") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 2. RNA Binding Proteins RPBs 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_CONSERVED[MSG_CONSERVED$Pro_Pval < 0.05, ]

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_RPB$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("RPB", "Non-RPB"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + RPB", "DE ~ RPB", "~ DE + RPB", "~ DE ~ RPB")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 3. Autophagy proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_CONSERVED[MSG_CONSERVED$Pro_Pval < 0.05, ]

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_Auto$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("Autophagy", "Non-Autophagy"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + Autophagy", "DE ~ Autophagy", "~ DE + Autophagy", "~ DE ~ Autophagy")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 4. Heat Shock Proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_CONSERVED[MSG_CONSERVED$Pro_Pval < 0.05, ]

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_HSP$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("HSP", "Non-HSP"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + HSP", "DE ~ HSP", "~ DE + HSP", "~ DE ~ HSP")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


####* --------- DE_RNA In Expressed Protein Set ####
```{r}
SAME_Sign_DE <- MSG_DE_RNAasprotein

Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot


# 1. MSG (All)
#**************************
MSG_Exp <- intersect(Expressed_protein, MSG$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A

# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("MSG", "Non-MSG"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + MSG", "DE ~ MSG", "~ DE + MSG", "~ DE ~ MSG")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("Contingency Table Stacked Bar Chart") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 2. RNA Binding Proteins RPBs 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE_RNAasprotein

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_RPB$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("RPB", "Non-RPB"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + RPB", "DE ~ RPB", "~ DE + RPB", "~ DE ~ RPB")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 3. Autophagy proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE_RNAasprotein

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_Auto$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("Autophagy", "Non-Autophagy"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + Autophagy", "DE ~ Autophagy", "~ DE + Autophagy", "~ DE ~ Autophagy")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


```{r}
# 4. Heat Shock Proteins 
#**************************
# All expressed proteins 
Expressed_protein <- New_RNA_PRO_DF$uniprotswissprot

# Set I am testing 
SAME_Sign_DE <- MSG_DE_RNAasprotein

# Intersection between MSG proteins and my expressed/detected proteins 
MSG_Exp <- intersect(Expressed_protein, MSG_HSP$Uniprot)
MSG_Exp

# A = number of Test Set proteins that are in the MSG_Exp list
A <- intersect(SAME_Sign_DE$uniprotswissprot, MSG_Exp) %>% length()
A
# B = number of Test Set proteins that are not in the MSG_Exp list
B <- length(SAME_Sign_DE$uniprotswissprot) - A
B
# C = number of expressed proteins that are in the MSG_Exp list but are not in Test Set proteins
C <- length(MSG_Exp) - A
C
# D = number of expressed proteins that are not in the MSG_Exp list and are not in Test Set proteins
D <- (nrow(New_RNA_PRO_DF) - length(SAME_Sign_DE$uniprotswissprot)) - C
D

# Chi-Squared Test
mat <- matrix(c(A, B, C, D), nrow = 2)
chisq.test(mat)
fisher.test(mat)



table <- as.table(matrix(c(A, B, C, D), nrow = 2,
                         dimnames = list(Gene = c("HSP", "Non-HSP"),
                                         Protein = c("DE", "Non-DE"))))
table

# Convert the table to a data frame
df_mat <- tidyr::gather(as.data.frame.matrix(table))
df_mat$key <- c("DE + HSP", "DE ~ HSP", "~ DE + HSP", "~ DE ~ HSP")
df_mat$Group <- c("DE", "DE", "~DE", "~DE")



# Create stacked bar chart
ggplot(df_mat, aes(x=Group, y=value, fill=key)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  ylab("Frequency") +
  xlab("Category") +
  ggtitle("") +
  scale_fill_discrete(name="Key") +
  theme(legend.position="bottom")
```


#### Subcellular Compartments ####
```{r}
# Read in compartment data frames 
Comp_Cytoplasm <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Compartment_Summaries/New_Pro_RNA_DF_Compartments/ID_Cytoplasm.csv", header = TRUE)
Comp_Cytosol <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Compartment_Summaries/New_Pro_RNA_DF_Compartments/ID_Cytosol.csv", header = TRUE)
Comp_ER <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Compartment_Summaries/New_Pro_RNA_DF_Compartments/ID_Endoplasmic_Reticulum.csv", header = TRUE)
Comp_Endosome <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Compartment_Summaries/New_Pro_RNA_DF_Compartments/ID_Endosome.csv", header = TRUE)
Comp_Golgi <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Compartment_Summaries/New_Pro_RNA_DF_Compartments/ID_Golgi_apparatus.csv", header = TRUE)
Comp_Lysosome <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Compartment_Summaries/New_Pro_RNA_DF_Compartments/ID_Lysosome.csv", header = TRUE)
Comp_membrane <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Compartment_Summaries/New_Pro_RNA_DF_Compartments/ID_Membrane.csv", header = TRUE)
Comp_mitochondrion <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Compartment_Summaries/New_Pro_RNA_DF_Compartments/ID_Mitochondrion.csv", header = TRUE)
Comp_Nucleus <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Compartment_Summaries/New_Pro_RNA_DF_Compartments/ID_Nucleus.csv", header = TRUE)
Comp_Pbody <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Compartment_Summaries/New_Pro_RNA_DF_Compartments/ID_Pbody.csv", header = TRUE)
Comp_Peroxisome <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Compartment_Summaries/New_Pro_RNA_DF_Compartments/ID_Peroxisome.csv", header = TRUE)
Comp_Secreted <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Proteomics/Compartment_Summaries/New_Pro_RNA_DF_Compartments/ID_Secreted.csv", header = TRUE)
```

####*--------All Protein Sets ####
```{r}
list_input <- list(
  Cytoplasm = Comp_Cytoplasm$Entry, 
  Cytosol = Comp_Cytosol$Entry, 
  ER = Comp_ER$Entry,
  Endosome = Comp_Endosome$Entry,
  Golgi = Comp_Golgi$Entry,
  Lysosome = Comp_Lysosome$Entry,
  Membrane = Comp_membrane$Entry,
  Mitochondrion = Comp_mitochondrion$Entry,
  Nucleus = Comp_Nucleus$Entry,
  Pbody = Comp_Pbody$Entry,
  Peroxisome = Comp_Peroxisome$Entry, 
  Secreted = Comp_Secreted$Entry
)
```


```{r}
# Upset Plots
upset(
  fromList(list_input), 
  sets = names(list_input), # show all sets in the plot
  order.by = "freq",
  
  sets.bar.color = "#56B4E9",
  matrix.color = "black",
  main.bar.color = "#D55E00",
)



# Convert to incidence matrix
matrix_input <- fromList(list_input)
matrix_input
# common item row numbers across sets. Example: Cytoplasm and Cytosol (Code here is variable to interests)
common_items <- rownames(matrix_input)[matrix_input[,"Cytoplasm"] == 1 & matrix_input[,"Cytosol"] == 1]

# Unlist the lisst input
all_entries <- unlist(list_input)

# Get Uniprot IDs 
common_items_names <- all_entries[as.numeric(common_items)]
common_items_names[length(common_items_names)]

# Venn
ggvenn(list_input)
```

```{r}
intersect(MSG_DE$uniprotswissprot, Comp_Cytoplasm$Entry)
####*--------DE proteins Upset ####
list_input <- list(
  Cytoplasm = intersect(Comp_Cytoplasm$Entry, MSG_DE$uniprotswissprot) , 
  Cytosol = intersect(Comp_Cytosol$Entry, MSG_DE$uniprotswissprot) , 
  ER = intersect(Comp_ER$Entry, MSG_DE$uniprotswissprot) ,
  Endosome = intersect(Comp_Endosome$Entry, MSG_DE$uniprotswissprot) ,
  Golgi = intersect(Comp_Golgi$Entry , MSG_DE$uniprotswissprot) ,
  Lysosome = intersect(Comp_Lysosome$Entry, MSG_DE$uniprotswissprot) ,
  Membrane = intersect(Comp_membrane$Entry, MSG_DE$uniprotswissprot) ,
  Mitochondrion = intersect(Comp_mitochondrion$Entry, MSG_DE$uniprotswissprot) ,
  Nucleus = intersect(Comp_Nucleus$Entry, MSG_DE$uniprotswissprot) ,
  Pbody = intersect(Comp_Pbody$Entry, MSG_DE$uniprotswissprot) ,
  Peroxisome = intersect(Comp_Peroxisome$Entry, MSG_DE$uniprotswissprot) , 
  Secreted = intersect(Comp_Secreted$Entry, MSG_DE$uniprotswissprot) 
)


# Upset Plots
upset(
  fromList(list_input), 
  sets = names(list_input), # show all sets in the plot
  order.by = "freq",
  
  sets.bar.color = "#56B4E9",
  matrix.color = "black",
  main.bar.color = "#D55E00",
)
```

####*--------Divergent proteins Upset ####
```{r}
list_input <- list(
  Cytoplasm = intersect(Comp_Cytoplasm$Entry, MSG_DIVERGENT$uniprotswissprot) , 
  Cytosol = intersect(Comp_Cytosol$Entry, MSG_DIVERGENT$uniprotswissprot) , 
  ER = intersect(Comp_ER$Entry, MSG_DIVERGENT$uniprotswissprot) ,
  Endosome = intersect(Comp_Endosome$Entry, MSG_DIVERGENT$uniprotswissprot) ,
  Golgi = intersect(Comp_Golgi$Entry , MSG_DIVERGENT$uniprotswissprot) ,
  Lysosome = intersect(Comp_Lysosome$Entry, MSG_DIVERGENT$uniprotswissprot) ,
  Membrane = intersect(Comp_membrane$Entry, MSG_DIVERGENT$uniprotswissprot) ,
  Mitochondrion = intersect(Comp_mitochondrion$Entry, MSG_DIVERGENT$uniprotswissprot) ,
  Nucleus = intersect(Comp_Nucleus$Entry, MSG_DIVERGENT$uniprotswissprot) ,
  Pbody = intersect(Comp_Pbody$Entry, MSG_DIVERGENT$uniprotswissprot) ,
  Peroxisome = intersect(Comp_Peroxisome$Entry, MSG_DIVERGENT$uniprotswissprot) , 
  Secreted = intersect(Comp_Secreted$Entry, MSG_DIVERGENT$uniprotswissprot) 
)


# Upset all members 
upset(
  fromList(list_input), 
  sets = names(list_input), # show all sets in the plot
  order.by = "freq",
  
  sets.bar.color = "#56B4E9",
  matrix.color = "black",
  main.bar.color = "#D55E00",
)
```



####*--------DE Divergent proteins Upset ####
```{r}
list_input <- list(
  Cytoplasm = intersect(Comp_Cytoplasm$Entry, MSG_DE_DIVERGENT$uniprotswissprot) , 
  Cytosol = intersect(Comp_Cytosol$Entry, MSG_DE_DIVERGENT$uniprotswissprot) , 
  ER = intersect(Comp_ER$Entry, MSG_DE_DIVERGENT$uniprotswissprot) ,
  Endosome = intersect(Comp_Endosome$Entry, MSG_DE_DIVERGENT$uniprotswissprot) ,
  Golgi = intersect(Comp_Golgi$Entry , MSG_DE_DIVERGENT$uniprotswissprot) ,
  Lysosome = intersect(Comp_Lysosome$Entry, MSG_DE_DIVERGENT$uniprotswissprot) ,
  Membrane = intersect(Comp_membrane$Entry, MSG_DE_DIVERGENT$uniprotswissprot) ,
  Mitochondrion = intersect(Comp_mitochondrion$Entry, MSG_DE_DIVERGENT$uniprotswissprot) ,
  Nucleus = intersect(Comp_Nucleus$Entry, MSG_DE_DIVERGENT$uniprotswissprot) ,
  Pbody = intersect(Comp_Pbody$Entry, MSG_DE_DIVERGENT$uniprotswissprot) ,
  Peroxisome = intersect(Comp_Peroxisome$Entry, MSG_DE_DIVERGENT$uniprotswissprot) , 
  Secreted = intersect(Comp_Secreted$Entry, MSG_DE_DIVERGENT$uniprotswissprot) 
)
```

# Upset all members 
```{r}
upset(
  fromList(list_input), 
  sets = names(list_input), # show all sets in the plot
  order.by = "freq",
  
  sets.bar.color = "#56B4E9",
  matrix.color = "black",
  main.bar.color = "#D55E00",
)
```


