---
title: "WPCNA_shallow_split_2"
output: html_document
date: "2023-12-06"
---

# Load Libraries 
```{r Libraries, include=FALSE}

library(EDASeq)
library(RUVSeq)
library(RColorBrewer)
library(edgeR)
library(limma)
library(Biobase)
library(SummarizedExperiment)
library(tidyverse) 
library(ggfortify)
library(cluster)
library(edgeR)
library(limma)
library(Homo.sapiens)
library(BiocParallel)
library(qvalue)
library(pheatmap)
library(clusterProfiler)
library(AnnotationDbi)
library(org.Hs.eg.db)
library(RColorBrewer)
library(variancePartition)
library(DOSE)
library(UpSetR)
library(ggvenn)
library(biomaRt)
library(ggridges)
library(reshape2)
library(BioNERO)
library(WGCNA)
library(impute)
library(dynamicTreeCut)
```

# Added funtions 
```{r Added functions}
remove_rows_with_nas <- function(data_frame) {
  data_frame[rowSums(is.na(data_frame)) < 5, ]
}
```
# Steps  
```{r Steps to take}
#* 1. Take Abundance values/counts 
#* 2. Remove NA values from Abundance values 
#* 3. Apply log2 transform to Abundance values 
#* 4. Quantile normalize abundance values 
#* 5. RUVs applied to account for technical variation 
#* 6. Use Limma to model differential protein abundaance 
```


# Read in Data 
```{r Read in Data}

# Load your data
Protein_DF <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/Abundance.csv", header = TRUE)

# Include metadata about samples 
Meta <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/Meta.csv", header = TRUE)
```


# Wrangle Data Frame 
```{r Wrangle Data Frame}
# Save the original 
Full_DF <- Protein_DF 


# Subset the columns referring to abundance
Protein_DF_Abundance <- Protein_DF[,c(4, 5:ncol(Protein_DF))] 

# Check for duplicated rows 
# Identify duplicated values
Protein_DF_Abundance$duplicated_name <- duplicated(Protein_DF_Abundance$Accession)

# This will return a logical vector where TRUE indicates the position of duplicates in the column.
# To see only rows with duplicated values, you can subset the dataframe like this:
duplicated_rows <- Protein_DF_Abundance[Protein_DF_Abundance$duplicated_name == TRUE, ]
print(duplicated_rows)

# We have 3 rows with duplicates, two of which have NA values. We will remove them now since we will go ahead 
# and remove the duplicated rows later on anyways. 
Protein_DF_Abundance <- Protein_DF_Abundance[- c(61, 276, 997), ] 

# Make rownames of the data frame accession IDs
rownames(Protein_DF_Abundance) <- Protein_DF_Abundance$Accession

# Change colnames 
colnames(Protein_DF_Abundance)
Protein_DF_Abundance <- Protein_DF_Abundance[, -c(1, 12)]

# Assuming column names of Protein_DF match with the rows in Meta
rownames(Meta) <- Meta$Samples

colnames(Protein_DF_Abundance) <- Meta$Samples
```

# Remove NA values 
```{r Remove NA values }
#1.  Find rows with any NA values
rows_with_na <- apply(Protein_DF_Abundance, 1, function(x) any(is.na(x))) %>% which()
 

rows_with_na <- as.numeric(rows_with_na)
Protein_DF_Abundance %>% dim()

# 2. Remove rows with NA values 
Protein_DF_Abundance <- Protein_DF_Abundance[-rows_with_na, ]

# 3. Sanity check 
Protein_DF_Abundance %>% dim()

```


# Log2 transform
```{r Log2 transform}
log2_norm_counts <- log2(Protein_DF_Abundance)
```

# Quantile Normalization 
```{r Quantile Normalization}
normalizedData <- limma::normalizeBetweenArrays(log2_norm_counts, method = "quantile")
```


# Prepare Data Object for RUVs 
```{r Prepare Data Object for RUVs}
#  counts need to be integer values and in a numeric matrix 
counts <- as.matrix(normalizedData) 

# Create a DataFrame for the phenoData
phenoData <- DataFrame(Meta)

# Now create the RangedSummarizedExperiment necessary for RUVs input 
set <- SummarizedExperiment(assays =  normalizedData, metadata =phenoData)
```


# RUVs Matrix 
```{r RUVs}
# Generate a background matrix where each set of replicates are in a row
# and null spaces where there are replicate mismatches get the value -1. 
# This will be used in the RUVs function, which is the typeII method to
# remove unwanted variation in the RUVs package. This will be used for all 
# RUVs permutations where the number of variation factors will be changed. 
scIdx <- matrix(-1, nrow = 6, ncol = 3)
scIdx[1, 1:3] <- c(which(colnames(counts) %in% c("S6", "S8", "S10"))) # Control group- Technical reps Ind. 48-1
scIdx[2, 1:3] <- c(which(colnames(counts) %in% c("S5", "S7", "S9"))) # Dox group- Technical reps Ind. 48-1
scIdx[3, 1] <- c(which(colnames(counts) %in% c("S2"))) # Control group- Bio reps Ind. 77-1
scIdx[4, 1] <- c(which(colnames(counts) %in% c("S1"))) # Dox group- 77-1
scIdx[5, 1] <- c(which(colnames(counts) %in% c("S4"))) # Control group- Bio reps Ind. 87-1
scIdx[6, 1] <- c(which(colnames(counts) %in% c("S3"))) # Dox group- 87-1
scIdx
```


# Linear Modelling 
```{r Linear Modelling}
# Apply RUVs function from RUVSeq and add to set object
set <- RUVSeq::RUVs(x = normalizedData, k = 1, scIdx = scIdx, isLog = TRUE)
RUV_1 <- set$W[,1]

set$W
phenoData$RUV_1 <- RUV_1


# Create Design Matrix 
# phenoData$Cond <- factor(phenoData$Cond , levels = c("Control", "Dox"))
design <- model.matrix(~0 + Cond + RUV_1, phenoData)
design

# rename columns 
colnames(design) <- c('Control', "Dox", "RUV_1")


# Fit model
fit <- lmFit(set$normalizedCounts, design)
fit2 <- eBayes(fit)


# Make contrasts
cm <- makeContrasts(
  DoxvNorm = Dox - Control,
  levels = design)


# Model with contrasts
fit2 <- contrasts.fit(fit, cm)
fit2 <- eBayes(fit2, robust = TRUE, trend = TRUE)


# Summarize
results_summary <- decideTests(fit2, adjust.method = "none", p.value = 0.05)
summary(results_summary)

# Toptable summary organized to contain results for all tested proteins   
toptable_summary <- topTable(fit2, coef = "DoxvNorm",number = (nrow(set$normalizedCounts )), p.value = 1, adjust.method = "none")
toptable_summary$Protein <- rownames(toptable_summary)
```
 

# WPCNA- shallow cuts 
```{r Create summarized experiment object}
# Create summarized experiment object 
WGCNA_DF <- SummarizedExperiment(assays = set$normalizedCounts)
exp_filt <- filter_by_variance(WGCNA_DF, n = 3384)

```

# SFT power threshold  
```{r SFT power threshold  }
# Determine the soft power threshold to get scale free shape
sft <- SFT_fit(exp_filt, net_type = "signed", rsquared = 0.8,  cor_method = "pearson")
sft$power

power <- sft$power
sft$plot 
power
```


# Modify workflow to have a simpler network  
```{r  Modify workflow to have a simpler network}
exp2gcn2_EDIT <- function (exp, net_type = "signed", module_merging_threshold = 0.8, 
          SFTpower = NULL, cor_method = "spearman", verbose = FALSE) 
{
  params <- list(net_type = net_type, module_merging_threshold = module_merging_threshold, 
                 SFTpower = SFTpower, cor_method = cor_method)
  norm.exp <- BioNERO:::handleSE(exp)
  if (is.null(SFTpower)) {
    stop("Please, specify the SFT power.")
  }
  if (verbose) {
    message("Calculating adjacency matrix...")
  }
  cor_matrix <- BioNERO:::calculate_cor_adj(cor_method, norm.exp, SFTpower, 
                                  net_type)$cor
  adj_matrix <- BioNERO:::calculate_cor_adj(cor_method, norm.exp, SFTpower, 
                                  net_type)$adj
  gene_ids <- rownames(adj_matrix)
  adj_matrix <- matrix(adj_matrix, nrow = nrow(adj_matrix))
  rownames(adj_matrix) <- gene_ids
  colnames(adj_matrix) <- gene_ids
  if (verbose) {
    message("Calculating topological overlap matrix (TOM)...")
  }
  tomtype <- BioNERO:::get_TOMtype(net_type)
  TOM <- WGCNA::TOMsimilarity(adj_matrix, TOMType = tomtype)
  dissTOM <- 1 - TOM
  geneTree <- hclust(as.dist(dissTOM), method = "average")
  if (verbose) {
    message("Detecting coexpression modules...")
  }
  old.module_labels <- dynamicTreeCut::cutreeDynamicTree(dendro = geneTree, maxTreeHeight = 4 , 
                                                         minModuleSize = 30, deepSplit = FALSE)
  nmod <- length(unique(old.module_labels))
  palette <- rev(WGCNA::standardColors(nmod))
  old.module_colors <- WGCNA::labels2colors(old.module_labels, 
                                            colorSeq = palette)
  if (verbose) {
    message("Calculating module eigengenes (MEs)...")
  }
  old.MElist <- WGCNA::moduleEigengenes(t(norm.exp), colors = old.module_colors, 
                                        softPower = SFTpower)
  old.MEs <- old.MElist$eigengenes
  MEDiss1 <- 1 - cor(old.MEs)
  old.METree <- hclust(as.dist(MEDiss1), method = "average")
  MEDissThreshold <- 1 - module_merging_threshold
  if (verbose) {
    message("Merging similar modules...")
  }
  if (cor_method == "pearson") {
    merge1 <- WGCNA::mergeCloseModules(t(norm.exp), old.module_colors, 
                                       cutHeight = MEDissThreshold, verbose = 0, colorSeq = palette)
  }
  else if (cor_method == "spearman") {
    merge1 <- WGCNA::mergeCloseModules(t(norm.exp), old.module_colors, 
                                       cutHeight = MEDissThreshold, verbose = 0, corOptions = list(use = "p", 
                                                                                                   method = "spearman"), colorSeq = palette)
  }
  else if (cor_method == "biweight") {
    merge1 <- WGCNA::mergeCloseModules(t(norm.exp), old.module_colors, 
                                       cutHeight = MEDissThreshold, verbose = 0, corFnc = bicor, 
                                       colorSeq = palette)
  }
  else {
    stop("Please, specify a correlation method. One of 'spearman', 'pearson' or 'biweight'.")
  }
  new.module_colors <- merge1$colors
  new.MEs <- merge1$newMEs
  new.METree <- hclust(as.dist(1 - cor(new.MEs)), method = "average")
  genes_and_modules <- as.data.frame(cbind(gene_ids, new.module_colors))
  colnames(genes_and_modules) <- c("Genes", "Modules")
  if (verbose) {
    message("Calculating intramodular connectivity...")
  }
  kwithin <- WGCNA::intramodularConnectivity(adj_matrix, new.module_colors)
  result.list <- list(adjacency_matrix = adj_matrix, MEs = new.MEs, 
                      genes_and_modules = genes_and_modules, kIN = kwithin, 
                      correlation_matrix = cor_matrix, params = params, dendro_plot_objects = list(tree = geneTree, 
                                                                                                   unmerged = old.module_colors))
  return(result.list)
}
```


# Generate network with max merge threshold 
```{r Generate network with max merge threshold }
net <- exp2gcn2_EDIT(
  exp_filt, net_type = "signed", module_merging_threshold = 0.99, SFTpower = power, 
  cor_method = "pearson")

# Dendogram
plot_dendro_and_colors(net )



# Eigengene networks
plot_eigengene_network(net)


# Genes per module 
plot_ngenes_per_module(net)
```


# Generate network with desired merge threshold 
```{r Generate network with desired merge threshold}
net <- exp2gcn2_EDIT(
  exp_filt, net_type = "signed", module_merging_threshold = 0.9, SFTpower = power, 
  cor_method = "pearson")

# Dendogram
plot_dendro_and_colors(net )



# Eigengene networks
plot_eigengene_network(net)


# Genes per module 
plot_ngenes_per_module(net)
```



# Define trat and get eigen proteins 
```{r Define trat and get eigen proteins }
WGCNA_DF$trait <- c(1,1,1,1,1,0,0,0,0,0)
names(WGCNA_DF$trait) <- c("S1", "S3", "S5", "S7", "S9", "S2", "S4", "S6", "S8", "S10")


eigenmatrix <- net$MEs %>% as.matrix()
eigenmatrix
```

# Trait-module correlation test 
```{r Trait-module correlation test}
correlationResults <- cor(eigenmatrix, WGCNA_DF$trait, method="pearson")

pvalues <- sapply(1:ncol(eigenmatrix), function(column) cor.test(eigenmatrix[,column], WGCNA_DF$trait)$p.value )

WGCNA_DF$trait <- as.matrix(WGCNA_DF$trait)

Modeigen <- as.matrix(net$MEs)


# Trait data frame
trait_data <- data.frame(
  ME = correlationResults %>% rownames(),
  Value = correlationResults[,1],
  PValue = pvalues
)
trait_data$neglogP <- -log(trait_data$PValue)
trait_data



# Plot correlation across modules
ggplot(trait_data, aes(x = ME, y = neglogP, color = Value)) + 
  geom_segment(aes(xend = ME, yend = 0), linetype = "solid") +
  geom_point(size = 10) + 
  scale_color_gradient(
    low = "red", 
    high = "blue", 
    name = "corr",
    limits = c(-1, 1),
    breaks = seq(-1, 1, by = 0.5)
  ) +
  labs(x = "Module", y = "-log(P-value)", title = "Module correlation with DOX treatment") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  geom_hline(yintercept = 2.995732, color = "black", linetype = "dashed") +
  geom_text(aes(x = 0, y = 3.5, label = "P-Val Threshold"), hjust = -0.1, vjust = 1.5)
```


# General wrangling 
```{r General wrangling }
# Get modules that significantly associate with DOX treatment 
Signifigant_modules <-  trait_data[trait_data$PValue < 0.05, ]$ME


# Get your genes/proteins and modules DF 
Gene_mod_DF <- net$genes_and_modules 



# Module data gets merged with toptable
toptable_summary %>% head()


Toptable_Modules <- merge(toptable_summary, 
                          Gene_mod_DF, by.x = "Protein", by.y = "Genes")





# Get the corresponding Gene name IDs
mart <- useMart("ensembl", dataset = "hsapiens_gene_ensembl")


results_Pro_names <- getBM(filters = "uniprotswissprot", 
                           attributes = c("uniprotswissprot", "hgnc_symbol"), 
                           values = toptable_summary$Protein, 
                           mart = mart)


merged_results_Pro_names_AND_Toptable_for_ENZYME <- merge(toptable_summary, results_Pro_names, by.x = "Protein", by.y = "uniprotswissprot")
ENZYME_DF_Toptable <- merged_results_Pro_names_AND_Toptable_for_ENZYME

DE_Enzymes <- ENZYME_DF_Toptable[(ENZYME_DF_Toptable$P.Value < 0.05) & (!is.na(ENZYME_DF_Toptable$ENZYME)), ]$hgnc_symbol

All_Proteins_ENZYMES <- ENZYME_DF_Toptable[(!is.na(ENZYME_DF_Toptable$ENZYME)), ]$hgnc_symbol





# Plotting LogFC in significant modules module 

Significant_modules_NoME <- stringr::str_replace(Signifigant_modules, "^ME", "")

Toptable_Modules_Sig <- Toptable_Modules[Toptable_Modules$Modules %in% Significant_modules_NoME, ]



# n-modules total 
Toptable_Modules$Modules %>% unique() %>% length()

# n-sig modules
Signifigant_modules %>% length()


# Percent sig modules 
(Signifigant_modules %>% length()) / (Toptable_Modules$Modules %>% unique() %>% length())



# Get modules that significantly associate with DOX treatment 
Signifigant_modules <-  trait_data[trait_data$PValue < 0.05, ]$ME


# Get your genes/proteins and modules DF 
Gene_mod_DF <- net$genes_and_modules 


# Subset genes/proteins and modules DF by the significantly correlated modules to DOX 
Sig_Gene_mod_DF <- Gene_mod_DF[Gene_mod_DF$Modules %in% Signifigant_modules, ]


# Module data gets merged with toptable
Toptable_Modules <- merge(toptable_summary, 
                          Gene_mod_DF, by.x = "Protein", by.y = "Genes")

Toptable_Modules %>% head()
Toptable_Modules %>% dim()
```


# Combining diff abundant test with modules 
```{r Riddge }
# LogFC Ridge plot 
ggplot(Toptable_Modules_Sig, aes(x = logFC, y = Modules, fill = Modules)) +
  ggridges::geom_density_ridges(alpha = 0.8) +
  labs(title = "Dox Associated Module LogFC distribution from DE test",
       x = "Log Fold Change",
       y = "Modules") +
  ggridges::theme_ridges() 



# LogFC Ridge plot 
ggplot(Toptable_Modules, aes(x = logFC, y = Modules, fill = Modules)) +
  ggridges::geom_density_ridges(alpha = 0.8) +
  labs(title = "Dox Associated Module LogFC distribution from DE test",
       x = "Log Fold Change",
       y = "Modules") +
  ggridges::theme_ridges() 



# Pval Ridge plot 
ggplot(Toptable_Modules_Sig, aes(x = P.Value, y = Modules, fill = Modules)) +
  ggridges::geom_density_ridges(alpha = 0.8) +
  labs(title = "Module pval distribution from DE test",
       x = "Pval",
       y = "") +
  ggridges::theme_ridges()+
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), limits = c(0, 1))


# Pval Ridge plot 
ggplot(Toptable_Modules, aes(x = P.Value, y = Modules, fill = Modules)) +
  ggridges::geom_density_ridges(alpha = 0.6) +
  labs(title = "Module pval distribution from DE test",
       x = "Pval",
       y = "Modules") +
  ggridges::theme_ridges()+
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), limits = c(0, 1))

```

```{r DE across modules}
# Plotting LogFC between DE and non DE proteins 
Toptable_Modules$DE_or_Not <- Toptable_Modules$P.Value < 0.05


# Calculate percentage of DE genes for each module
DE_Mod_result <- Toptable_Modules %>%
  group_by(Modules) %>%
  summarize(
    total_genes = n(),
    DE_genes = sum(P.Value < 0.05),
    percent_DE = (DE_genes / total_genes) * 100
  )

print(DE_Mod_result)


# Plot
ggplot(DE_Mod_result, aes(x = Modules, y = percent_DE, fill = Modules)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Module",
    y = "Percentage of DE genes",
    title = "Percentage of DE genes in each module",
    fill = "Module"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


# Compute complementary percentage for non-DE genes
DE_Mod_result$percent_nonDE <- 100 - DE_Mod_result$percent_DE

# Reshape data to long format
long_data <- DE_Mod_result %>% 
  pivot_longer(cols = c(percent_DE, percent_nonDE), 
               names_to = "type", 
               values_to = "percentage")


# Plot stacked bar chart
ggplot(long_data, aes(x = Modules, y = percentage, fill = type)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Module",
    y = "Percentage",
    title = "Percentage of DE and non-DE genes in each module",
    fill = "Type"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = rev(seq(0, 100, by = 10)))

Significant_modules_NoME



metatestDF <- phenoData$Cond %>% as.data.frame()


```


# GO enrichment acrross dox correlated modules 
```{r GO enrichment}
hubs <- get_hubs_gcn(WGCNA_DF, net)
ontology_categories <- c("ALL")


# Loop over each module and ontology category
for (module in Significant_modules_NoME) {
  # Extract hub genes for the current module
  module_hubs <- hubs[hubs$Module == module, ]$Gene
  
  # All module proteins
  module_proteins <- Toptable_Modules[(Toptable_Modules$Modules == module), ]$Protein
  
  # Get gene names for the proteins in the module
  module_genes <- ENZYME_DF_Toptable[ENZYME_DF_Toptable$Protein %in% module_proteins, ]$hgnc_symbol
  
  # Define background genes
  background_genes_mod <- ENZYME_DF_Toptable$hgnc_symbol
  
  for (ont in ontology_categories) {
    # GO Enrichment
    go_enrichment <- enrichGO(gene = module_genes,
                              OrgDb = org.Hs.eg.db,
                              keyType = "SYMBOL",
                              universe = background_genes_mod,
                              ont = ont,
                              pvalueCutoff = 1,
                              qvalueCutoff = 1)
    
    # Plotting the results
    # Plotting the results
    p <- barplot(go_enrichment, showCategory = 10) +
      ggtitle(paste("Module:", module, "- Ontology:", ont))
    
    print(p)   
    
  }
}
```


# Protein corrrelation plots within modules 
```{r Protein corrrelation plots}
# Remove edges based on optimal scale-free topology fit
edges_filtered <- get_edge_list(net, module = c("darkgreen", "pink", "lightyellow", "royalblue"), filter = TRUE)

## The correlation threshold that best fits the scale-free topology is 0.7
dim(edges_filtered)
## [1] 588   3

#### Network for all ####
# Remove edges based on minimum correlation
edges_filtered <- get_edge_list(
  net, module = c("darkgreen", "pink", "lightyellow", "royalblue"), 
  filter = TRUE, method = "min_cor", rcutoff = 0.93,
  check_SFT = TRUE
)

dim(edges_filtered)

plot_gcn(
  edgelist_gcn = edges_filtered, 
  net = net, 
  color_by = "module", 
  hubs = hubs,
  top_n_hubs = 30,
  show_labels = "tophubs"
)
```


#### Network darkgreen #### 
```{r Network darkgreen}
edges_filtered <- get_edge_list(
  net, module = c("darkgreen" ), 
  filter = TRUE, method = "min_cor", rcutoff = 0.9,
  check_SFT = TRUE
)

dim(edges_filtered)

plot_gcn(
  edgelist_gcn = edges_filtered, 
  net = net, 
  color_by = "module", 
  hubs = hubs,
  top_n_hubs = 30,
  show_labels = "tophubs"
)
```


#### Network pink #### 
```{r Network pink}
edges_filtered <- get_edge_list(
  net, module = c( "pink"), 
  filter = TRUE, method = "min_cor", rcutoff = 0.8,
  check_SFT = TRUE
)

dim(edges_filtered)

plot_gcn(
  edgelist_gcn = edges_filtered, 
  net = net, 
  color_by = "module", 
  hubs = hubs,
  top_n_hubs = 30,
  show_labels = "tophubs"
)
```


#### Network lightyellow #### 
```{r Network lightyellow}
edges_filtered <- get_edge_list(
  net, module = c("lightyellow" ), 
  filter = TRUE, method = "min_cor", rcutoff = 0.92,
  check_SFT = TRUE
)

dim(edges_filtered)

plot_gcn(
  edgelist_gcn = edges_filtered, 
  net = net, 
  color_by = "module", 
  hubs = hubs,
  top_n_hubs = 30,
  show_labels = "tophubs"
)
```


#### Network royalblue #### 
```{r Network royalblue}
edges_filtered <- get_edge_list(
  net, module = c("royalblue"), 
  filter = TRUE, method = "min_cor", rcutoff = 0.94,
  check_SFT = TRUE
)

dim(edges_filtered)

plot_gcn(
  edgelist_gcn = edges_filtered, 
  net = net, 
  color_by = "module", 
  hubs = hubs,
  top_n_hubs = 30,
  show_labels = "tophubs"
)
```

