---
title: "Dox_prot_WGCNA"
output: html_document
date: "2023-11-04"
---

# Libraries 
```{r libraries}
library(EDASeq)
library(RUVSeq)
library(RColorBrewer)
library(edgeR)
library(limma)
library(Biobase) 
library(SummarizedExperiment)
library(tidyverse) 
library(ggfortify)
library(cluster)
library(edgeR)
library(limma)
library(biomaRt)
library(Homo.sapiens)
library(BiocParallel)
library(qvalue)
library(pheatmap)
library(clusterProfiler)
library(AnnotationDbi)
library(org.Hs.eg.db)
library(RColorBrewer)
library(DOSE)
library(UpSetR)
library(ggvenn)
library(WGCNA)
library(BioNERO)
```

# Getting toptable data frame and gene names 
```{r df and names}
ENZYME_DF <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/Functional_Annotations_ENZYME.csv" , header = TRUE)
 
toptable_Dupcor <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/Important_DF_Final/toptable_Dupcor.csv" , header = TRUE)

Toptable_for_ENZYME <- toptable_Dupcor


# Get the corresponding Gene name IDs
mart <- useMart("ensembl", dataset = "hsapiens_gene_ensembl")


results_Pro_names <- getBM(filters = "hgnc_symbol", 
                           attributes = c("uniprotswissprot", "hgnc_symbol",""), 
                           values = ENZYME_DF$Gene.Symbol, 
                           mart = mart)


merged_results_Pro_names_AND_Toptable_for_ENZYME <- merge(Toptable_for_ENZYME, results_Pro_names, by.x = "Protein", by.y = "uniprotswissprot")

merged_results_Pro_names_AND_Toptable_for_ENZYME_AND_ENZYME_DF <- merge(merged_results_Pro_names_AND_Toptable_for_ENZYME, 
                                                                        ENZYME_DF, by.x = "hgnc_symbol", by.y = "Gene.Symbol")

ENZYME_DF_Toptable <- merged_results_Pro_names_AND_Toptable_for_ENZYME_AND_ENZYME_DF

DE_Enzymes <- ENZYME_DF_Toptable[(ENZYME_DF_Toptable$P.Value < 0.05) & (!is.na(ENZYME_DF_Toptable$ENZYME)), ]$hgnc_symbol

All_Proteins_ENZYMES <- ENZYME_DF_Toptable[(!is.na(ENZYME_DF_Toptable$ENZYME)), ]$hgnc_symbol
```

# Get protein abundance matrix 
```{r abundance df}

phenoData <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/WGCNA/phenoData.csv" , header = TRUE)

vobjE <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/WGCNA/vobjE.csv" , header = TRUE)

vobjdesign <- read.csv(file = "/Users/omarjohnson/Documents/Projects/Dox_Proteomics/Data/Data_Frames/WGCNA/vobjdesign.csv" , header = TRUE)

# WGCNA requires a summarized experiment object using vobj$E 
WGCNA_phenodata <- phenoData[ ,4:5] 

colnames(WGCNA_phenodata) <- c("trait", "individual_cond")

rownames(vobjE) <- vobjE$X
vobjE <- vobjE[,-c(1)]
vobjE %>% head()
```



# WGCNA Workflow
# Fit abundance matrix to scale free topology  
```{r connectivity}

# Create summarized experiiment object 
WGCNA_DF <- SummarizedExperiment(assays = vobjE)

# Determine the soft power threshold to get scale free shape
sft <- SFT_fit(vobjE, net_type = "signed", rsquared = 0.8,  cor_method = "pearson")
sft$power

power <- sft$power
sft$plot 

WGCNA_DF <- SummarizedExperiment(assays = vobjE)
```


# Modules unmerged
```{r net unmerged}
net <- exp2gcn(
  WGCNA_DF, net_type = "signed", module_merging_threshold = 0.9, SFTpower = power, 
  cor_method = "pearson"
)
```


# Modules unmerged summary plots 
```{r dend unmerged,  fig.width=10, fig.height=8 }
# Dendogram
plot_dendro_and_colors(gcn = net )


# Eigengene networks
plot_eigengene_network(net)


# Genes per module 
plot_ngenes_per_module(net)
```

# Merge modules 
```{r net merged}
net <- exp2gcn(
  WGCNA_DF, net_type = "signed", module_merging_threshold = 0.65, SFTpower = power, 
  cor_method = "pearson"
)
```

# Summary plots for merged modules
```{r Dend merged,  fig.width=10, fig.height=8 }
# Dendogram
plot_dendro_and_colors(gcn = net )


# Eigengene networks
plot_eigengene_network(net)


# Genes per module 
plot_ngenes_per_module(net)
```

# Module stability 
```{r Mod stability,  fig.width=13, fig.height=10 }
# Looking at module stability 
module_stability(WGCNA_DF, net, nRuns = 50)
```


# Correlate moules to DOX trait  
```{r connectivity 2}

# Ave K total
net$kIN$kTotal %>% mean()

# Ave KDiff
net$kIN$kWithin %>% hist()

# Median KDiff
net$kIN$kDiff %>% median()


# Calculate percentage of positive numbers in kDiff
percentage_positive <- sum(net$kIN$kDiff > 0) / length(net$kIN$kDiff) * 100
print(percentage_positive)


# Correlation test 
WGCNA_DF$trait <- c(1,1,1,1,1,0,0,0,0,0) 
names(WGCNA_DF$trait) <- c("S1", "S3", "S5", "S7", "S9", "S2", "S4", "S6", "S8", "S10")


eigenmatrix <- net$MEs %>% as.matrix()
correlationResults <- cor(eigenmatrix, WGCNA_DF$trait, method="pearson")

pvalues <- sapply(1:ncol(eigenmatrix), function(column) cor.test(eigenmatrix[,column], WGCNA_DF$trait)$p.value )

WGCNA_DF$trait <- as.matrix(WGCNA_DF$trait)

Modeigen <- as.matrix(net$MEs)


# Trait data frame
trait_data <- data.frame(
  ME = correlationResults %>% rownames(),
  Value = correlationResults[,1],
  PValue = pvalues
)
trait_data$neglogP <- -log(trait_data$PValue)
trait_data


# Plot correlation across modules
ggplot(trait_data, aes(x = ME, y = neglogP, color = Value)) + 
  geom_segment(aes(xend = ME, yend = 0), linetype = "solid") +
  geom_point(size = 10) + 
  scale_color_gradient(
    low = "red", 
    high = "blue", 
    name = "corr",
    limits = c(-1, 1),
    breaks = seq(-1, 1, by = 0.5)
  ) +
  labs(x = "Module", y = "-log(P-value)", title = "Module correlation with DOX treatment") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  geom_hline(yintercept = 2.995732, color = "black", linetype = "dashed") +
  geom_text(aes(x = 0, y = 3.5, label = "P-Val Threshold"), hjust = -0.1, vjust = 1.5)
```


# Subset DOX correlated modules 
```{r mods,  fig.width = 8, fig.height = 6}
# Get modules that significantly associate with DOX treatment 
Signifigant_modules <-  trait_data[trait_data$PValue < 0.05, ]$ME


# Get your genes/proteins and modules DF 
Gene_mod_DF <- net$genes_and_modules 
 


# Module data gets merged with toptable
toptable_Dupcor %>% head()

Toptable_Modules <- merge(toptable_Dupcor, 
                          Gene_mod_DF, by.x = "Protein", by.y = "Genes")

```

# Wrangling 
```{r modplot}


# Plotting LogFC in significant modules module 
Signifigant_modules 

Significant_modules_NoME <- stringr::str_replace(Signifigant_modules, "^ME", "")

Toptable_Modules_Sig <- Toptable_Modules[Toptable_Modules$Modules %in% Significant_modules_NoME, ]



# n-modules total 
Toptable_Modules$Modules %>% unique() %>% length()

# n-sig modules
Signifigant_modules %>% length()


# Percent sig modules 
(Signifigant_modules %>% length()) / (Toptable_Modules$Modules %>% unique() %>% length())



# Get modules that significantly associate with DOX treatment 
Signifigant_modules <-  trait_data[trait_data$PValue < 0.05, ]$ME


# Get your genes/proteins and modules DF 
Gene_mod_DF <- net$genes_and_modules 


# Subset genes/proteins and modules DF by the significantly correlated modules to DOX 
Sig_Gene_mod_DF <- Gene_mod_DF[Gene_mod_DF$Modules %in% Signifigant_modules, ]


# Module data gets merged with toptable
toptable_Dupcor %>% head()

Toptable_Modules <- merge(toptable_Dupcor, 
                          Gene_mod_DF, by.x = "Protein", by.y = "Genes")

Toptable_Modules %>% head()
Toptable_Modules %>% dim()
```


# Ridge plots 
```{r other mod plots}


# LogFC Ridge plot 
ggplot(Toptable_Modules_Sig, aes(x = logFC, y = Modules, fill = Modules)) +
  ggridges::geom_density_ridges(alpha = 0.8) +
  labs(title = "Dox Associated Module LogFC distribution from DE test",
       x = "Log Fold Change",
       y = "Modules") +
  ggridges::theme_ridges() 


# LogFC Ridge plot 
ggplot(Toptable_Modules, aes(x = logFC, y = Modules, fill = Modules)) +
  ggridges::geom_density_ridges(alpha = 0.8) +
  labs(title = "Dox Associated Module LogFC distribution from DE test",
       x = "Log Fold Change",
       y = "Modules") +
  ggridges::theme_ridges() 


# Pval Ridge plot 
ggplot(Toptable_Modules_Sig, aes(x = P.Value, y = Modules, fill = Modules)) +
  ggridges::geom_density_ridges(alpha = 0.8) +
  labs(title = "Module pval distribution from DE test",
       x = "Pval",
       y = "") +
  ggridges::theme_ridges()+
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), limits = c(0, 1))


# Pval Ridge plot 
ggplot(Toptable_Modules, aes(x = P.Value, y = Modules, fill = Modules)) +
  ggridges::geom_density_ridges(alpha = 0.6) +
  labs(title = "Module pval distribution from DE test",
       x = "Pval",
       y = "Modules") +
  ggridges::theme_ridges()+
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), limits = c(0, 1))



# Plotting LogFC between DE and non DE proteins 
Toptable_Modules$DE_or_Not <- Toptable_Modules$P.Value < 0.05
```


# DE protein content in modules 
```{r many mod plt}
# Calculate percentage of DE genes for each module
DE_Mod_result <- Toptable_Modules %>%
  group_by(Modules) %>%
  summarize(
    total_genes = n(),
    DE_genes = sum(P.Value < 0.05),
    percent_DE = (DE_genes / total_genes) * 100
  )

print(DE_Mod_result)


# Plot
ggplot(DE_Mod_result, aes(x = Modules, y = percent_DE, fill = Modules)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Module",
    y = "Percentage of DE genes",
    title = "Percentage of DE genes in each module",
    fill = "Module"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


# Compute complementary percentage for non-DE genes
DE_Mod_result$percent_nonDE <- 100 - DE_Mod_result$percent_DE

# Reshape data to long format
long_data <- DE_Mod_result %>% 
  pivot_longer(cols = c(percent_DE, percent_nonDE), 
               names_to = "type", 
               values_to = "percentage")


# Plot stacked bar chart
ggplot(long_data, aes(x = Modules, y = percentage, fill = type)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Module",
    y = "Percentage",
    title = "Percentage of DE and non-DE genes in each module",
    fill = "Type"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_y_continuous(breaks = rev(seq(0, 100, by = 10)))


```


# Wrangle 2 
```{r randoplots}
metatestDF <- phenoData$Cond %>% as.data.frame()



assay_data <- assay(WGCNA_DF)
row_data <- rowData(WGCNA_DF)
col_data <- colData(WGCNA_DF)

row_data[] <- lapply(row_data, as.character)
col_data[] <- lapply(col_data, as.character)

rowData(WGCNA_DF) <- row_data
colData(WGCNA_DF) <- col_data
```



# Module protein GO Enrichment 
```{r GO loop}
hubs <- get_hubs_gcn(WGCNA_DF, net)

Significant_modules_NoME 
ontology_categories <- c("BP","CC")

# Loop over each module and ontology category
for (module in Significant_modules_NoME) {
    # Extract hub genes for the current module
    module_hubs <- hubs[hubs$Module == module, ]$Gene

    # All module proteins
    module_proteins <- Toptable_Modules[(Toptable_Modules$Modules == module), ]$Protein

    # Get gene names for the proteins in the module
    module_genes <- ENZYME_DF_Toptable[ENZYME_DF_Toptable$Protein %in% module_proteins, ]$hgnc_symbol

    # Define background genes
    background_genes_mod <- ENZYME_DF_Toptable$hgnc_symbol

    for (ont in ontology_categories) {
        # GO Enrichment
        go_enrichment <- enrichGO(gene = module_genes,
                                  OrgDb = org.Hs.eg.db,
                                  keyType = "SYMBOL",
                                  universe = background_genes_mod,
                                  ont = ont,
                                  pvalueCutoff = 0.05,
                                  qvalueCutoff = 0.05)

        # Plotting the results
# Plotting the results
        p <- barplot(go_enrichment, showCategory = 20) +
            ggtitle(paste("Module:", module, "- Ontology:", ont))

        print(p)   
        
    }
}


```



# Abundance correlation network plot 
```{r network plots,  fig.width=13, fig.height=10}

# Remove edges based on p-value
edges_filtered <- get_edge_list(
  net, module = c("darkslateblue", "darkorange2", "brown","pink"),
  filter = TRUE, method = "pvalue", 
  pvalue_cutoff = 0.00008,
  nSamples = ncol(WGCNA_DF),
  check_SFT = TRUE
)

dim(edges_filtered)



# Plot filtered network 
plot_gcn(
  edgelist_gcn = edges_filtered, 
  net = net, 
  color_by = "module", 
  hubs = hubs,
  top_n_hubs = 10,
  show_labels = "allhubs"
)

edges_filtered %>% head()
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

